\tabulinesep = 5pt
\begin{longtabu} to \textwidth {
    |l|X[3l]|X[0.75l]|}
\caption{Attributes for CuttingTool and CuttingToolArchetype} \label{table:attributes-for-cuttingtool-and-cuttingtoolarchetype} \\

\hline
Attribute & Description & Occurrence \\
\hline
\endfirsthead

\hline
\multicolumn{3}{|c|}{Continuation of Table \ref{table:attributes-for-cuttingtool-and-cuttingtoolarchetype}}\\
\hline
Attribute & Description & Occurrence \\
\hline
\endhead

\gls{timestamp}
&
The time this \gls{mtconnect asset} was last modified. Always given in UTC. The \gls{timestamp} \MUST be provided in UTC (Universal Time Coordinate, also known as GMT). This is the time the \gls{asset} data was last modified.
\newline \gls{timestamp} is a required attribute.
&
1 \\
\hline
 
\gls{assetid}
&
The unique identifier of the instance of this tool. This will be the
same as the \gls{toolid} and \gls{serialnumber} in most cases. The \gls{assetid} \SHOULD be the combination of the \gls{toolid} and \gls{serialnumber} as in \gls{toolid}. \gls{serialnumber} or an equivalent implementation dependent identification scheme.
\newline \gls{assetid} is a required attribute.
\newline \gls{assetid} is a permanent identifier that will be associated with an \gls{mtconnect asset} for its entire life.
&
1 \\
\hline

\gls{serialnumber}
&
The unique identifier for this assembly. This is defined as an XML string type and is implementation dependent.
\newline \gls{serialnumber} is a required attribute.
&
1 \\
\hline

\gls{toolid}
&
The identifier for a class of Cutting Tools. This is defined as an XML string type and is implementation dependent.
\newline \gls{toolid} is a required attribute.
&
1 \\
\hline

\gls{deviceuuid}
&
\glsentrydesc{deviceuuid}
&
1 \\
\hline

\gls{manufacturers}
&
An optional attribute referring to the manufacturer(s) of this Cutting
Tool, for this element, this will reference the Tool Item and Adaptive
Items specifically. The Cutting Items manufacturers’ will be an
attribute of the \gls{cuttingitem} elements. The representation will be a
comma (,) delimited list of manufacturer names. This can be any
series of numbers and letters as defined by the XML type \cfont{string}.
&
0..1 \\
\hline

\gls{removed}
&
This is an indicator that the Cutting Tool has been removed from the piece of equipment.
\newline \gls{removed} is a required attribute.
\newline If the \gls{mtconnect asset} is marked as removed, it will not be visible to the client application unless the \cfont{includeRemoved=true} parameter is provided in the URL. If this attribute is not present it \MUST be assumed to be \cfont{false}. The value is an \cfont{xsi:boolean} type and \MUST be \cfont{true} or \cfont{false}.
&
0..1 \\
\hline


\end{longtabu}