\appendix
\section*{Appendices}
\addcontentsline{toc}{section}{Appendices}
\renewcommand{\thesubsection}{\Alph{subsection}}

\subsection{Bibliography}
\label{Bibliography}

Engineering Industries Association. \textit{EIA Standard - EIA-274-D}, Interchangeable Variable, Block Data Format for Positioning, Contouring, and Contouring/Positioning Numerically Controlled Machines. Washington, D.C. 1979.

ISO TC 184/SC4/WG3 N1089. \textit{ISO/DIS 10303-238:} Industrial automation systems and integration  Product data representation and exchange  Part 238: Application Protocols: Application interpreted model for computerized numerical controllers. Geneva, Switzerland, 2004.

International Organization for Standardization. \textit{ISO 14649:} Industrial automation systems and integration – Physical device control – Data model for computerized numerical controllers – Part 10: General process data. Geneva, Switzerland, 2004.

International Organization for Standardization. \textit{ISO 14649:} Industrial automation systems and integration – Physical device control – Data model for computerized numerical controllers – Part 11: Process data for milling. Geneva, Switzerland, 2000.

International Organization for Standardization. \textit{ISO 6983/1} – Numerical Control of machines – Program format and definition of address words – Part 1: Data format for positioning, line and contouring control systems. Geneva, Switzerland, 1982.

Electronic Industries Association. \textit{ANSI/EIA-494-B-1992}, 32 Bit Binary CL (BCL) and 7 Bit ASCII CL (ACL) Exchange Input Format for Numerically Controlled Machines. Washington, D.C. 1992.

National Aerospace Standard. \textit{Uniform Cutting Tests} - NAS Series: Metal Cutting Equipment Specifications. Washington, D.C. 1969.

International Organization for Standardization. \textit{ISO 10303-11:} 1994, Industrial automation systems and integration  Product data representation and exchange  Part 11: Description methods: The EXPRESS language reference manual. Geneva, Switzerland, 1994.

International Organization for Standardization. \textit{ISO 10303-21:} 1996, Industrial automation systems and integration -- Product data representation and exchange -- Part 21: Implementation methods: Clear text encoding of the exchange structure. Geneva, Switzerland, 1996.

H.L. Horton, F.D. Jones, and E. Oberg. \textit{Machinery's Handbook}. Industrial Press, Inc. New York, 1984.

International Organization for Standardization. \textit{ISO 841-2001:} Industrial automation systems and integration - Numerical control of machines - Coordinate systems and motion nomenclature. Geneva, Switzerland, 2001.

ASME B5.57: \textit{Methods for Performance Evaluation of Computer Numerically Controlled Lathes and Turning Centers}, 1998.

ASME/ANSI B5.54: \textit{Methods for Performance Evaluation of Computer Numerically Controlled Machining Centers}. 2005.

OPC Foundation. \textit{OPC Unified Architecture Specification, Part 1: Concepts Version 1.00}. July 28, 2006.

IEEE STD 1451.0-2007, \textit{Standard for a Smart Transducer Interface for Sensors and Actuators – Common Functions, Communication Protocols, and Transducer Electronic Data Sheet (TEDS) Formats, IEEE Instrumentation and Measurement Society, TC-9, The Institute of Electrical and Electronics Engineers, Inc., New York, N.Y. 10016, SH99684, October 5, 2007.}

IEEE STD 1451.4-1994, Standard for a Smart Transducer Interface for Sensors and Actuators – Mixed-Mode Communication Protocols and Transducer Electronic Data Sheet (TEDS) Formats, IEEE Instrumentation and Measurement Society, TC-9, The Institute of Electrical and Electronics Engineers, Inc., New York, N.Y. 10016, SH95225, December 15, 2004. 