
\newglossaryentry{Application Programming Interface}
{
    name={Application Programming Interface},
	description={
  A set of methods to provide communications between software applications.

  The API defined in the MTConnect Standard describes the methods for providing the \gls{Request/Response} Information Exchange between an \gls{Agent} and client software applications.
  
  Appears in the documents in the following forms: Application Programming Interface or API.
}
}

\newglossaryentry{Applications}
{
    name={Applications},
	description={}
}

\newglossaryentry{Adapter}
{
    name={Adapter},
	description={
  An optional piece of hardware or software that transforms information provided by a piece of equipment into a form that can be received by an \gls{Agent}.

  Appears in the documents in the following form: adapter.
}
}

\newglossaryentry{Agent}
{
    name={Agent},
	description={
  Refers to an MTConnect Agent. 
  
  Software that collects data published from one or more piece(s) of equipment, organizes that data in a structured manner, and responds to requests for data from client software systems by providing a structured response in the form of a \gls{Response Document} that is constructed using the \gls{semantic data model} defined in the Standard. 
  
  Appears in the documents in the following form: \gls{Agent}.
}
}

\newglossaryentry{MTConnect Agent}
{
    name={MTConnect Agent},
	description={
	See definition for \gls{Agent}.
}
}

\newglossaryentry{Client}
{
    name={Client},
	description={
  A process or set of processes that send \gls{Request} for information to an \gls{Agent}; e.g. software applications or a function that implements the \gls{Request} portion of an \gls{Interface} \gls{Interaction Model}.

  Appears in the documents in the following form: client.
}
}

\newglossaryentry{Archetype}
{
    name={Archetype},
	description={
  *ULHEADING:General Description of an \gls{MTConnect Asset}*:
  
  Archetype is a class of \gls{MTConnect Asset} that provides the requirements, constraints, and common properties for a type of \gls{MTConnect Asset}.

  Appears in the documents in the following form: Archetype.

  *ULHEADING:Used as an XML term describing an \gls{MTConnect Asset}*:
  
  In an XML representation of the \gls{Asset Information Model}, \block{Archetype} is an abstract element that is replaced by a specific type of \gls{Asset} Archetype.
  
  Appears in the documents in the following form: \block{Archetype}
}
}

\newglossaryentry{Attribute}
{
    name={Attribute},
	description={
  A term that is used to provide additional information or properties for an element.

  Appears in the documents in the following form: attribute.
}
}

\newglossaryentry{Base Functional Structure}
{
    name={Base Functional Structure},
	description={
  A consistent set of functionalities defined by the MTConnect Standard. This functionality includes the protocol(s) used to communicate data to a client software application, the \gls{semantic data model} defining how that data is organized into \gls{Response Document}, and the encoding of those \gls{Response Document}.

  Appears in the documents in the following form: \gls{Base Functional Structure}.
}
}

\newglossaryentry{CDATA}
{
    name={CDATA},
	description={
  **ULHEADING:General meaning**:

  An abbreviation for Character Data.

  \gls{CDATA} is used to describe a value (text or data) published as part of an XML element.

  For example, *CFONT:"This is some text"* is the \gls{CDATA} in the XML element:
  
  **TAB** *CFONT:<Message ...>This is some text</Message>*

  Appears in the documents in the following form: \gls{CDATA}
}
}

\newglossaryentry{Component}
{
    name={Component},
	description={
  **ULHEADING:General meaning**:

  A \gls{Structural Element} that represents a physical or logical part or subpart of a piece of equipment.

  Appears in the documents in the following form: \gls{Component}.

  *ULHEADING:Used in \gls{Information Models}*:

  A data modeling element used to organize the data being retrieved from a piece of equipment.
  
  **BEGIN:itemize**
      **ITEM** When used as an XML container to organize \gls{Lower Level} \block{Component} elements. 
      
      Appears in the documents in the following form: \block{Components}.
      
      **ITEM** When used as an abstract XML element. \block{Component} is replaced in a data model by a type of \gls{Component} element. \block{Component} is also an XML container used to organize \gls{Lower Level} \block{Component} elements, \gls{Data Entities}, or both.
      
      Appears in the documents in the following form: \block{Component}.
  **END:itemize**
}
}

\newglossaryentry{Composition}
{
    name={Composition},
	description={
  **ULHEADING:General meaning**:

  Data modeling elements that describe the lowest level basic structural or functional building blocks contained within a \block{Component} element.

  Appears in the documents in the following form: \gls{Composition}

  *ULHEADING:Used in \gls{Information Models}*:

  A data modeling element used to organize the data being retrieved from a piece of equipment.

  **BEGIN:itemize**
      **ITEM** When used as an XML container to organize \block{Composition} elements. 
      
      Appears in the documents in the following form: \block{Compositions}
      
      **ITEM** When used as an abstract XML element. \block{Composition} is replaced in a data model by a type of \gls{Composition} element. 
      
      Appears in the documents in the following form: \block{Composition}.
  **END:itemize**
}
}

\newglossaryentry{Controlled Vocabulary}
{
    name={Controlled Vocabulary},
	description={
	A restricted set of values that may be published as the \gls{Valid Data Value} for a \gls{Data Entity}.

	Appears in the documents in the following form: \gls{Controlled Vocabulary}.
}
}

\newglossaryentry{Data Model}
{
    name={Data Model},
	description={A \gls{semantic data model}.}
}

\newglossaryentry{Data Set}
{
    name={Data Set},
	description={A set of \gls{key-value pairs} where each entry is uniquely identified by the \gls{key}.}
}

\newglossaryentry{Data Source}
{
    name={Data Source},
	description={
	Any piece of equipment that can produce data that is published to an \gls{Agent}.

	Appears in the documents in the following form: data source.
}
}

\newglossaryentry{Deprecated}
{
    name={Deprecated},
	description={
	An indication that specific content in an \gls{MTConnect Document} is currently usable but is regarded as being obsolete or superseded. It is recommended that deprecated content should be avoided.

	Appears in the documents in the following form: **DEPRECATED**.
}
}

\newglossaryentry{Deprecation Warning}
{
    name={Deprecation Warning},
	description={
	An indicator that specific content in an \gls{MTConnect Document} may be changed to **DEPRECATED** in a future release of the standard.

	Appears in the documents in the following form: **DEPRECATIONWARNING**.
}
}

\newglossaryentry{Document}
{
    name={Document},
	description={
	**ULHEADING:General meaning**:

	A piece of written, printed, or electronic matter that provides information.

	*ULHEADING:Used to represent an \gls{MTConnect Document}*:

	Refers to printed or electronic document(s) that represent a \gls{Part}(s) of the MTConnect Standard.

	Appears in the documents in the following form: \gls{MTConnect Document}.

	*ULHEADING:Used to represent a specific representation of an \gls{MTConnect Document}*:

	Refers to electronic document(s) associated with an \gls{Agent} that are encoded using XML; \gls{Response Document} or \gls{Asset Document}.

	Appears in the documents in the following form: \gls{MTConnect XML Document}.

	*ULHEADING:Used to describe types of information stored in an \gls{Agent}*:

	In an implementation, the electronic documents that are published from a data source and stored by an \gls{Agent}.

	Appears in the documents in the following form: \gls{Asset Document}.

	*ULHEADING:Used to describe information published by an \gls{Agent}*:

	A document published by an \gls{Agent} based upon one of the \gls{semantic data model} defined in the MTConnect Standard in response to a request from a client.  

	Appears in the documents in the following form: \gls{Response Document}.
}
}

\newglossaryentry{MTConnect Document}
{
    name={MTConnect Document},
	description={See \gls{Document}.}
}

\newglossaryentry{Asset Document}
{
    name={Asset Document},
	description={
	An electronic document published by an \gls{Agent} in response to a \gls{Request} for information from a client software application relating to Assets.
}
}

\newglossaryentry{Document Body}
{
    name={Document Body},
	description={
	The portion of the content of an \gls{MTConnect Response Document} that is defined by the relative \gls{MTConnect Information Model}. The \gls{Document Body} contains the \gls{Structural Elements} and \gls{Data Entities} reported in a \gls{Response Document}.

	Appears in the documents in the following form: \gls{Document Body}.
}
}

\newglossaryentry{Document Header}
{
    name={Document Header},
	description={
	The portion of the content of an \gls{MTConnect Response Document} that provides information from an \gls{Agent} defining version information, storage capacity, protocol, and other information associated with the management of the data stored in or retrieved from the \gls{Agent}.
	
	Appears in the documents in the following form: \gls{Document Header}.
}
}

\newglossaryentry{Element}
{
    name={Element},
	description={
	Refers to an XML element.

	An XML element is a logical portion of an XML document or schema that begins with a **CFONT:start-tag** and ends with a corresponding **CFONT:end-tag**.  

	The information provided between the **CFONT:start-tag** and **CFONT:end-tag** may contain attributes, other elements (sub-elements), and/or CDATA.

    **BEGIN:note**
	Note:  Also, an XML element may consist of an **CFONT:empty-element tag**.  Refer to **APX:A** for more information on element tags.
    **END:note**
    
	Appears in the documents in the following form: element.
}
}

\newglossaryentry{Abstract Element}
{
    name={Abstract Element},
	description={
  An element that defines a set of common characteristics that are shared by a group of elements.
  
  An abstract element cannot appear in a document. In a specific implementation of a schema, an abstract element is replaced by a derived element that is itself not an abstract element. The characteristics for the derived element are inherited from the abstract element. 
  
  Appears in the documents in the following form: abstract.
}
}

\newglossaryentry{Child Element}
{
    name={Child Element},
	description={
  A portion of a data modeling structure that illustrates the relationship between an element and the higher-level \gls{Parent Element} within which it is contained.
  
  Appears in the documents in the following form: \gls{Child Element}.
}
}

\newglossaryentry{Lower Level}
{
    name={Lower Level},
	description={A nested element that is below a higher level element.}
}

\newglossaryentry{Parent Element}
{
    name={Parent Element},
	description={
	An XML element used to organize \gls{Lower Level} child elements that share a common relationship to the \gls{Parent Element}.

	Appears in the documents in the following form: \gls{Parent Element}.
}
}

\newglossaryentry{Higher Level}
{
    name={Higher Level},
	description={A nested element that is above a lower level element.}
}

\newglossaryentry{Root Element}
{
    name={Root Element},
	description={
	The first \gls{Structural Element} provided in a \gls{Response Document} encoded using XML.  The \gls{Root Element} is an XML container and is the \gls{Parent Element} for all other XML elements in the document.  The \gls{Root Element} appears immediately following the XML Declaration.

	Appears in the documents in the following form: \gls{Root Element}.
}
}

\newglossaryentry{Equipment}
{
    name={Equipment},
	description={
	Represents anything that can publish information and is used in the operations of a manufacturing facility shop floor.  Examples of equipment are machine tools, ovens, sensor units, workstations, software applications, and bar feeders.

	Appears in the documents in the following form: equipment or piece of equipment.
}
}

\newglossaryentry{Device}
{
    name={Device},
	description={
	A part of an information model representing a piece of equipment.  
	
	*ULHEADING:Used in an XML representation of a \gls{Response Document}*:

    **BEGIN:itemize**
	**ITEM** When used as an XML container to organize \block{Device} elements.

	Appears in the documents in the following form: \block{Devices}.

	**ITEM** When used as an XML container to represent a specific piece of equipment and is composed of a set of \gls{Structural Elements} that organize and provide relevance to data published from that piece of equipment.

	Appears in the documents in the following form: \block{Device}.
	**END:itemize**
}
}

\newglossaryentry{Equipment Metadata}
{
    name={Equipment Metadata},
	description={See \gls{Metadata}}
}

\newglossaryentry{Extensible}
{
    name={Extensible},
	description={
	The ability for an implementer to extend \gls{MTConnect Information Model} by adding content not currently addressed in the MTConnect Standard.
}
}

\newglossaryentry{Fault State}
{
    name={Fault State},
	description={
	In the MTConnect Standard, a term that indicates the reported status of a \gls{Condition} category \gls{Data Entity}.   

	Appears in the documents in the following form: \gls{Fault State}.
}
}

\newglossaryentry{HTTP}
{
    name={HTTP},
	description={
	Hyper-Text Transport Protocol.  The protocol used by all web browsers and web applications.

    **BEGIN:note**
	Note:  HTTP is an IETF standard and is defined in RFC 7230. \ See https://tools.ietf.org/html/rfc7230 for more information.
	**END:note**
}
}

\newglossaryentry{HTTP Body}
{
    name={HTTP Body},
	description={\gls{HTTP Body} is the data bytes transmitted in an HTTP transaction message immediately following the headers.}
}

\newglossaryentry{HTTP Error Message}
{
    name={HTTP Error Message},
	description={
	In the MTConnect Standard, a response provided by an \gls{Agent} indicating that an \gls{HTTP Request} is incorrectly formatted or identifies that the requested data is not available from the \gls{Agent}.  

	Appears in the documents in the following form: \gls{HTTP Error Message}.
}
}

\newglossaryentry{HTTP Header}
{
    name={HTTP Header},
	description={
	In the MTConnect Standard, the content of the \gls{Header} portion of either an \gls{HTTP Request} from a client software application or an \gls{HTTP Response} from an \gls{Agent}.

	Appears in the documents in the following form: \gls{HTTP Header}.
}
}

\newglossaryentry{HTTP Header Field}
{
    name={HTTP Header Field},
	description={\gls{HTTP Header Field} are components of the header section of request and response messages in an HTTP transaction.}
}

\newglossaryentry{HTTP Messaging}
{
    name={HTTP Messaging},
	description={\gls{HTTP Messaging} is an interface for information exchange functionality.}
}

\newglossaryentry{HTTP Method}
{
    name={HTTP Method},
	description={
	In the MTConnect Standard, a portion of a command in an \gls{HTTP Request} that indicates the desired action to be performed on the identified resource; often referred to as verbs.
}
}

\newglossaryentry{HTTP Query}
{
    name={HTTP Query},
	description={
	**ULHEADING:General Meaning**:

	A portion of a request for information that more precisely defines the specific information to be published in response to the request. 

	Appears in the documents in the following form: \gls{Query}.

	*ULHEADING:Used in an \gls{HTTP Request Line}*:

	The form \block{query} includes a string of parameters that define filters used to refine the content of a \gls{Response Document} published in response to an \gls{HTTP Request}.

	Appears in the documents in the following form: \block{query}.
}
}

\newglossaryentry{HTTP Request Line}
{
    name={HTTP Request Line},
	description={
	In the MTConnect Standard, the first line of an \gls{HTTP Request} describing a specific \gls{Response Document} to be published by an \gls{Agent}.

	Appears in the documents in the following form: \gls{HTTP Request Line}.
}
}

\newglossaryentry{HTTP Request Method}
{
    name={HTTP Request Method},
	description={It indicates the method to be performed on the resource identified by the given request URI.}
}

\newglossaryentry{HTTP Request URL}
{
    name={HTTP Request URL},
	description={A request specifying the location and mechanism to retrieve a web resource.}
}

\newglossaryentry{HTTP Response}
{
    name={HTTP Response},
	description={
	In the MTConnect Standard, the information published from an \gls{Agent} in reply to an \gls{HTTP Request}.  An \gls{HTTP Response} may be either a \gls{Response Document} or an \gls{HTTP Error Message}.

	Appears in the documents in the following form: \gls{HTTP Response}.
}
}

\newglossaryentry{HTTP Server}
{
    name={HTTP Server},
	description={
	In the MTConnect Standard, a software program that accepts \gls{HTTP Request} from client software applications and publishes \gls{HTTP Response} as a reply to those \gls{Request}.

	Appears in the documents in the following form: \gls{HTTP Server}.
}
}

\newglossaryentry{HTTP Status Code}
{
    name={HTTP Status Code},
	description={
	In the MTConnect Standard, a numeric code contained in an \gls{HTTP Response} that defines a status category associated with the \gls{Response}  either a success status or a category of an HTTP error.  

	Appears in the documents in the following form: \gls{HTTP Status Code}.
}
}

\newglossaryentry{HTTP Version}
{
    name={HTTP Version},
	description={Version of the HTTP protocol.}
}

\newglossaryentry{Header}
{
    name={Header},
	description={See \gls{Document Header}}
}

\newglossaryentry{Implementation}
{
    name={Implementation},
	description={
	A specific instantiation of the MTConnect Standard.
}
}

\newglossaryentry{Information Model}
{
    name={Information Model},
	description={
	The rules, relationships, and terminology that are used to define how information is structured.

	For example, an information model is used to define the structure for each \gls{MTConnect Response Document}; the definition of each piece of information within those documents and the relationship between pieces of information.

	Appears in the documents in the following form: \gls{Information Model}.
}
}

\newglossaryentry{MTConnect Information Model}
{
    name={MTConnect Information Model},
	description={See \gls{Information Model}}
}

\newglossaryentry{Asset Information Model}
{
    name={Asset Information Model},
	description={It associates each electronic \block{MTConnectAssets} document with a unique identifier and allows for some predefined mechanisms to find, create, request, updated, and delete these electronic documents in a way that provides for consistency across multiple pieces of equipment.}
}

\newglossaryentry{Devices Information Model}
{
    name={Devices Information Model},
	description={
	A set of rules and terms that describes the physical and logical configuration for a piece of equipment and the data that may be reported by that equipment.    

	Appears in the documents in the following form: \gls{Devices Information Model}.
}
}

\newglossaryentry{Error Information Model}
{
    name={Error Information Model},
	description={
	The rules and terminology that describes the \gls{Response Document} returned by an \gls{Agent} when it encounters an error while interpreting a \gls{Request} for information from a client software application or when an \gls{Agent} experiences an error while publishing the \gls{Response} to a \gls{Request} for information.

	Appears in the documents in the following form: \gls{Error Information Model}.
}
}

\newglossaryentry{Streams Information Model}
{
    name={Streams Information Model},
	description={
	The rules and terminology (\gls{semantic data model}) that describes the \gls{Streaming Data} returned by an \gls{Agent} from a piece of equipment in response to a \gls{Sample Request} or a \gls{Current Request}.

	Appears in the documents in the following form: \gls{Streams Information Model}.
}
}

\newglossaryentry{Interaction Model}
{
    name={Interaction Model},
	description={
	The definition of information exchanged to support the interactions between pieces of equipment collaborating to complete a task.

	Appears in the documents in the following form: \gls{Interaction Model}.
}
}

\newglossaryentry{Interface}
{
    name={Interface},
	description={
	**ULHEADING:General meaning**:

	The exchange of information between pieces of equipment and/or software systems.

	Appears in the documents in the following form: interface.

	*ULHEADING:Used as an \gls{Interaction Model}*:

	An \gls{Interaction Model} that describes a method for inter-operations between pieces of equipment.

	Appears in the documents in the following form: \gls{Interface}.

	**ULHEADING:Used as an XML container or element**:

	**TAB** - When used as an XML container that consists of one or more types of \block{Interface} XML elements.

	Appears in the documents in the following form: \block{Interfaces}.

	**TAB** - When used as an abstract XML element.  It is replaced in the XML document by types of \block{Interface} elements.

	Appears in the documents in the following form: \block{Interface}
}
}

\newglossaryentry{Lower Camel Case}
{
    name={Lower Camel Case},
	description={the first word is lowercase and the remaining words are capitalized and all spaces between words are removed.}
}

\newglossaryentry{MODBUS}
{
    name={MODBUS},
	description={Modbus is a communication protocol developed by Modicon systems and is a method used for transmitting information over serial lines between electronic devices.}
}

\newglossaryentry{MTConnect}
{
    name={MTConnect},
	description={The name of the standard.}
}

\newglossaryentry{MTConnect Asset}
{
    name={MTConnect Asset},
	description={An \gls{MTConnect Asset} is an \gls{Asset} that is used in the manufacturing process, but is not a critical part of a piece of equipment. An \gls{MTConnect Asset} can be observed by multiple pieces of equipment during its lifecycle.

An \gls{MTConnect Asset} does not produce data and is dependent on \gls{Devices} to provide observations.

}
}

\newglossaryentry{MTConnect Standard}
{
    name={MTConnect Standard},
	description={The name of the standard.}
}

\newglossaryentry{MTConnect XML Document}
{
    name={MTConnect XML Document},
	description={See \gls{Document}.}
}

\newglossaryentry{MTConnect Response Document}
{
    name={MTConnect Response Document},
	description={See \gls{Response Document}.}
}

\newglossaryentry{MTConnectAssets Response Document}
{
    name={MTConnectAssets Response Document},
	description={
	An electronic document published by an \gls{Agent} in response to a \gls{Request} for information from a client software application relating to \gls{MTConnect Asset}.

	Appears in the documents in the following form: \gls{MTConnectAssets Response Document}.
}
}

\newglossaryentry{Asset Response Document}
{
    name={Asset Response Document},
	description={See \gls{MTConnectAssets Response Document}}
}

\newglossaryentry{MTConnectDevices Response Document}
{
    name={MTConnectDevices Response Document},
	description={
	An electronic document published by an \gls{Agent} in response to a \gls{Request} for information from a client software application that includes \gls{Metadata} for one or more pieces of equipment.

	Appears in the documents in the following form: \gls{MTConnectDevices Response Document}.
}
}

\newglossaryentry{MTConnectErrors Response Document}
{
    name={MTConnectErrors Response Document},
	description={
	An electronic document published by an \gls{Agent} whenever it encounters an error while interpreting a \gls{Request} for information from a client software application or when an \gls{Agent} experiences an error while publishing the \gls{Response} to a \gls{Request} for information.

	Appears in the documents in the following form: \gls{MTConnectErrors Response Document}.
}
}

\newglossaryentry{MTConnectStreams Response Document}
{
    name={MTConnectStreams Response Document},
	description={
	An electronic document published by an \gls{Agent} in response to a \gls{Request} for information from a client software application that includes \gls{Streaming Data} from the \gls{Agent}.

	Appears in the documents in the following form: \gls{MTConnectStreams Response Document}.
}
}

\newglossaryentry{Response Document}
{
    name={Response Document},
	description={
	See \gls{Document}.
}
}

\newglossaryentry{Message}
{
    name={Message},
	description={
	**ULHEADING:General meaning**:

	The content of a communication process.

	Appears in the documents in the following form: message.

	*ULHEADING:Used relative to an \gls{Agent}*:

	Describes the information that is exchanged between an \gls{Agent} and a client software application.  A \gls{Message} may contain either a \gls{Request} from a client software application or a \gls{Response} from an \gls{Agent}.

	Appears in the documents in the following form: \gls{Message}.

	*ULHEADING:Used as a type of \gls{Data Entity}*:

	Describes a type of \gls{Data Entity} in the \gls{Devices Information Model} that can contain any text string of information or native code to be transferred from a piece of equipment.

	Appears in the documents in the following form: \block{MESSAGE}.

	**ULHEADING:Used as an Element Name**:

	An \gls{Element Name} for a \gls{Data Entity} in the \gls{Streams Information Model} that can contain any text string of information or native code to be transferred from a piece of equipment.

	Appears in the documents in the following form:  **GLSELEMENTNAME:message event**.
}
}

\newglossaryentry{Metadata}
{
    name={Metadata},
	description={
	Data that provides information about other data.

	For example, \gls{Equipment Metadata} defines both the \gls{Structural Elements} that represent the physical and logical parts and sub-parts of each piece of equipment, the relationships between those parts and sub-parts, and the definitions of the \gls{Data Entities} associated with that piece of equipment.

	Appears in the documents in the following form: \gls{Metadata} or \gls{Equipment Metadata}.
}
}

\newglossaryentry{Data Item}
{
    name={Data Item},
	description={
	**ULHEADING:General meaning**:

	Descriptive information or properties and characteristics associated with a \gls{Data Entity}.

	Appears in the documents in the following form: data item.

	*ULHEADING:Used in an XML representation of a \gls{Data Entity}*:

    **BEGIN:itemize**
	**ITEM** When used as an XML container to organize \block{DataItem} elements.

	Appears in the documents in the following form: \block{DataItems}.

	**ITEM** When used to represent a specific \gls{Data Entity}, the form \block{DataItem} is an XML element.  

	Appears in the documents in the following form: \block{DataItem}.
    **END:itemize**
}
}

\newglossaryentry{Condition}
{
    name={Condition},
	description={
	**ULHEADING:General meaning**:

	An indicator of the health of a piece of equipment or a \gls{Component} and its ability to function.

	**ULHEADING:Used as a modeling element**:

	A data modeling element used to organize and communicate information relative to the health of a piece of equipment or \gls{Component}.

	Appears in the documents in the following form: \gls{Condition}.

	*ULHEADING:Used in \gls{Information Models}*:

	An XML element used to represent \gls{Condition} elements.

    **BEGIN:itemize**
	**ITEM** When used as an XML container to organize \gls{Lower Level} \block{Condition} elements.

	Appears in the documents in the following form: \block{Condition}.

	**ITEM** When used as a \gls{Lower Level} element, the form \block{Condition} is an abstract type XML element.  This \gls{Lower Level} element is a \gls{Data Entity}.  \block{Condition} is replaced in a data model by type of \gls{Condition} element.

	Appears in the documents in the following form: \block{Condition}.
	**END:itemize**

	**BEGIN:note**
	Note: The form \block{Condition} is used to represent both above uses.
	**END:note**
}
}

\newglossaryentry{Event}
{
    name={Event},
	description={
	**ULHEADING:General meaning**:

	The occurrence of something that happens or takes place.

	Appears in the documents in the following form: event.

	*ULHEADING:Used as a type of \gls{Data Entity}*:

	An identification that represents a change in state of information associated with a piece of equipment or an occurrence of an action.  Event also provides a means to publish a message from a piece of equipment.

	Appears in the documents in the following form: \gls{Event}.

	*ULHEADING:Used as a \block{category} attribute for a \gls{Data Entity}*:

	Used as a value for the \block{category} attribute for an XML \block{DataItem} element.

	Appears in the documents in the following form: \block{EVENT}.

	**ULHEADING:Used as an XML container or element**:

    **BEGIN:itemize**
	**ITEM** When used as an XML container that consists of one or more types of \block{Event} XML elements.

	Appears in the documents in the following form: \block{Events}.

	**ITEM** When used as an abstract XML element.  It is replaced in the XML document by types of \block{Event} elements.

	Appears in the documents in the following form: \block{Event}.
    **END:itemize**
}
}

\newglossaryentry{Sample}
{
    name={Sample},
	description={
	**ULHEADING:General meaning**:

	The collection of one or more pieces of information.  

	**ULHEADING:Used when referring to the collection of information**:

	When referring to the collection of a piece of information from a data source.

	Appears in the documents in the following form: sample.

	*ULHEADING:Used as an \gls{MTConnect Request}*:

	When representing a specific type of communications request between a client software application and an \gls{Agent} regarding \gls{Streaming Data}.  

	Appears in the documents in the following form: \gls{Sample Request}.

	*ULHEADING:Used as part of an \gls{HTTP Request}*:

	Used in the \block{path} portion of an \gls{HTTP Request Line}, by a client software application, to initiate a \gls{Sample Request} to an \gls{Agent} to publish an \block{MTConnectStreams} document.

	Appears in the documents in the following form: \block{sample}.

	*ULHEADING:Used to describe a \gls{Data Entity}*:

	Used to define a specific type of \gls{Data Entity}.  A \gls{Sample} type \gls{Data Entity} reports the value for a continuously variable or analog piece of information.

	Appears in the documents in the following form: \gls{Sample} or \gls{Samples}.

	**ULHEADING:Used as an XML container or element**:

    **BEGIN:itemize**
	**ITEM** When used as an XML container that consists of one or more types of Sample XML elements.

	Appears in the documents in the following form: \block{Samples}.

	**ITEM** When used as an abstract XML element.  It is replaced in the XML document by types of \block{Sample} elements representing individual \gls{Sample} type of \gls{Data Entity}.

	Appears in the documents in the following form: \block{Sample}.
    **END:itemize**
}
}

\newglossaryentry{NMTOKEN}
{
    name={NMTOKEN},
	description={
	The data type for XML identifiers.

	**BEGIN:note**
	Note: The identifier must start with a letter, an underscore "_" or a colon.  The next character must be a letter, a number, or one of the following ".", "-", "_", ":".  The identifier must not have any spaces or special characters.
	**END:note**

	Appears in the documents in the following form: \gls{NMTOKEN}.
}
}

\newglossaryentry{Element QName}
{
    name={Element QName},
	description={
	A descriptive identifier contained in both the **CFONT:start-tag** and **CFONT:end-tag** of an XML element that provides the name of the element.

	Appears in the documents in the following form: element name.

	**ULHEADING:Used to describe the name for a specific XML element**:

	Reference to the name provided in the **CFONT:start-tag**, **CFONT:end-tag**, or **CFONT:empty-element tag** for an XML element.

	Appears in the documents in the following form: \gls{Element Name}.
}
}

\newglossaryentry{Observation}
{
    name={Observation},
	description={}
}

\newglossaryentry{Data Entity}
{
    name={Data Entity},
	description={
	A primary data modeling element that represents all elements that either describe data items that may be reported by an \gls{Agent} or the data items that contain the actual data published by an \gls{Agent}.

	Appears in the documents in the following form: \gls{Data Entity}.
}
}

\newglossaryentry{Occurrence}
{
    name={Occurrence},
	description={Occurrence defines the number of times the content defined in the tables **MAY** be provided in the usage case specified}
}

\newglossaryentry{Part}
{
    name={Part},
	description={Each Standard document is referred to as a \gls{Part} of the Standard.}
}

\newglossaryentry{Pascal Case}
{
    name={Pascal Case},
	description={The first letter of each word is capitalized and the remaining letters are in lowercase. All space is removed between letters}
}

\newglossaryentry{Persistence}
{
    name={Persistence},
	description={
	A method for retaining or restoring information.
}
}

\newglossaryentry{Physical Connection}
{
    name={Physical Connection},
	description={The network transmission technologies that physically interconnect an \gls{Agent}.}
}

\newglossaryentry{Protocol}
{
    name={Protocol},
	description={
	A set of rules that allow two or more entities to transmit information from one to the other.
}
}

\newglossaryentry{Transport Protocol}
{
    name={Transport Protocol},
	description={A set of capabilities that provide the rules and procedures used to transport information between an \gls{Agent} and a client software application through a \gls{Physical Connection}.}
}

\newglossaryentry{Publish/Subscribe}
{
    name={Publish/Subscribe},
	description={
	In the MTConnect Standard, a communications messaging pattern that may be used to publish \gls{Streaming Data} from an \gls{Agent}.  When a \gls{Publish/Subscribe} communication method is established between a client software application and an \gls{Agent}, the \gls{Agent} will repeatedly publish a specific \block{MTConnectStreams} document at a defined period.

	Appears in the documents in the following form: \gls{Publish/Subscribe}.
}
}

\newglossaryentry{Publish}
{
    name={Publish},
	description={Sending of messages in a \gls{Publish/Subscribe} pattern.}
}

\newglossaryentry{Subscribe}
{
    name={Subscribe},
	description={Receiving messages in a \gls{Publish/Subscribe} pattern.}
}

\newglossaryentry{Streaming Data}
{
    name={Streaming Data},
	description={
	The values published by a piece of equipment for the \gls{Data Entities} defined by the \gls{Equipment Metadata}.

	Appears in the documents in the following form: \gls{Streaming Data}.
}
}

\newglossaryentry{Data Streaming}
{
    name={Data Streaming},
	description={
	A method for an \gls{Agent} to provide a continuous stream of information in response to a single \gls{Request} from a client software application.

	Appears in the documents in the following form: \gls{Data Streaming}.
}
}

\newglossaryentry{Request}
{
    name={Request},
	description={
	A communications method where a client software application transmits a message to an \gls{Agent}.  That message instructs the \gls{Agent} to respond with specific information.

	Appears in the documents in the following form: \gls{Request}.
}
}

\newglossaryentry{HTTP Request}
{
    name={HTTP Request},
	description={
	In the MTConnect Standard, a communications command issued by a client software application to an \gls{Agent} requesting information defined in the \gls{HTTP Request Line}.

	Appears in the documents in the following form: \gls{HTTP Request}.
}
}

\newglossaryentry{MTConnect Request}
{
    name={MTConnect Request},
	description={
	A communication request for information issued from a client software application to an \gls{Agent}.

	Appears in the documents in the following form: \gls{MTConnect Request}.
}
}

\newglossaryentry{Asset Request}
{
    name={Asset Request},
	description={See \gls{Asset}.}
}

\newglossaryentry{Probe Request}
{
    name={Probe Request},
	description={An **GLSTEXT:http** request to the \gls{Agent} for returning metadata as an \block{MTConnectDevices} **GLSTEXT:xml** document}
}

\newglossaryentry{Probe}
{
    name={Probe},
	description={
	**ULHEADING:General meaning of a physical entity**:

	An instrument commonly used for measuring the physical geometrical characteristics of an object.

    **BEGIN:itemize**
	**ITEM** **ULHEADING:Used to describe a measurement device**:

	The form probe is used to define a measurement device that provides position information.

	Appears in the documents in the following form: probe. 

	**ITEM** *ULHEADING:Used within a \gls{Data Entity}*:

	The form \block{PROBE} is used to designate a subtype for the \gls{Data Entity} \block{PATH_POSITION} indicating a measurement position relating to a probe unit.

	Appears in the documents in the following form: \block{PROBE}.
    **END:itemize**

	*ULHEADING:General meaning for communications with an \gls{Agent}*:

	Probe is used to define a type of communication request. 

    **BEGIN:itemize**
	**ITEM** **ULHEADING:Used as a type of communication request**:

	The form \gls{Probe Request} represents a specific type of communications request between a client software application and an \gls{Agent} regarding \gls{Metadata} for one or more pieces of equipment.

	Appears in the documents in the following form: \gls{Probe Request}.

	**ITEM** *ULHEADING:Used in an \gls{HTTP Request Line}*:

	The form \block{probe} is used to designate a \gls{Probe Request} in the *CFONT:<Path>* portion of an \gls{HTTP Request Line}.

	Appears in the documents in the following form: \block{probe}.
    **END:itemize**
}
}

\newglossaryentry{Current Request}
{
    name={Current Request},
	description={An **GLSTEXT:http** request to the \gls{Agent} for returning latest known values for the \block{DataItem} as an \block{MTConnectStreams} **GLSTEXT:xml** document}
}

\newglossaryentry{Current}
{
    name={Current},
	description={
	**ULHEADING:General meaning**:

	Meaning 1:  A term describing the most recent occurrence of something.

	Meaning 2:  A term used to describe movement; e.g. electric current or air current.

	Appears in the documents in the following form: current

	*ULHEADING:Used in reference to an \gls{Agent}*:

	A reference to the most recent information available to an \gls{Agent}.

	Appears in the documents in the following form: current.

	*ULHEADING:Used as an \gls{MTConnect Request}*:

	A specific type of communications request between a client software application and an \gls{Agent} regarding \gls{Streaming Data}.  

	Appears in the documents in the following form: \gls{Current Request}.

	*ULHEADING:Used as part of an \gls{HTTP Request}*:

	Used in the path portion of an \gls{HTTP Request Line}, by a client software application, to initiate a \gls{Current Request} to an \gls{Agent} to publish an \block{MTConnectStreams} document.

	Appears in the documents in the following form: \block{current}.
}
}

\newglossaryentry{Sample Request}
{
    name={Sample Request},
	description={A request from the \gls{Agent} for a stream of time series data.}
}

\newglossaryentry{REST}
{
    name={REST},
	description={
	REpresentational State Transfer:  A software architecture where a client software application and server move through a series of state transitions based solely on the request from the client and the response from the server. 

	Appears in the documents in the following form: REST.
}
}

\newglossaryentry{Realization}
{
    name={Realization},
	description={Realization is a specialized abstraction relationship between two sets of model elements, one representing a specification (the supplier) and the other represents an implementation of the latter (the client). Realization can be used to model stepwise refinement, optimizations, transformations, templates, model synthesis, framework composition, etc.}
}

\newglossaryentry{Reference}
{
    name={Reference},
	description={\block{Reference} is a pointer to information that is associated with another \gls{Structural Element}.}
}

\newglossaryentry{Request/Response}
{
    name={Request/Response},
	description={
	A communications pattern that supports the transfer of information between an \gls{Agent} and a client software application. In a \gls{Request/Response} information exchange, a client software application requests specific information from an \gls{Agent}. An \gls{Agent} responds to the \gls{Request} by publishing a \gls{Response Document}.   

	Appears in the documents in the following form: \gls{Request/Response}.
}
}

\newglossaryentry{Response}
{
    name={Response},
	description={A response \gls{Interface} which responds to a \gls{Request}.}
}

\newglossaryentry{Responder}
{
    name={Responder},
	description={
	An entity that responds to a \gls{Request} for information in a communications exchange.

	Appears in the documents in the following form: \gls{Responder}.
}
}

\newglossaryentry{Requester}
{
    name={Requester},
	description={
	An entity that initiates a \gls{Request} for information in a communications exchange.

	Appears in the documents in the following form: \gls{Requester}.
}
}

\newglossaryentry{Sensor}
{
    name={Sensor},
	description={A \gls{Sensor} is typically comprised of two major components: a \gls{sensor unit} that provides signal processing, conversion, and communications and the \gls{sensing elements} that provides a signal or measured value.}
}

\newglossaryentry{Standard}
{
    name={Standard},
	description={
	**ULHEADING:General meaning**:

	A document established by consensus that provides rules, guidelines, or characteristics for activities or their results (as defined in ISO/IEC Guide 2:2004).

	**ULHEADING:Used when referring to the MTConnect Standard**: 

	The MTConnect Standard is a standard that provides the definition and semantic data structure for information published by pieces of equipment.

	Appears in the documents in the following form: Standard or MTConnect Standard.
}
}

\newglossaryentry{Structural Element}
{
    name={Structural Element},
	description={
	**ULHEADING:General meaning**:

	An XML element that organizes information that represents the physical and logical parts and sub-parts of a piece of equipment.

	Appears in the documents in the following form: \gls{Structural Element}.

	**ULHEADING:Used to indicate hierarchy of Components**:

	When used to describe a primary physical or logical construct within a piece of equipment. 

	Appears in the documents in the following form: \gls{Top Level} \gls{Structural Element}.

	When used to indicate a \gls{Child Element} which provides additional detail describing the physical or logical structure of a \gls{Top Level} \gls{Structural Element}.

	Appears in the documents in the following form: \gls{Lower Level} \gls{Structural Element}.
}
}

\newglossaryentry{Time Series}
{
    name={Time Series},
	description={A \block{DataItem} representation of a contiguous vector of values supporting high frequency data rates}
}

\newglossaryentry{Top Level}
{
    name={Top Level},
	description={\gls{Structural Elements} that represent the most significant physical or logical functions of a piece of equipment.}
}

\newglossaryentry{URI}
{
    name={URI},
	description={
	Stands for Universal Resource Identifier.  

	See http://www.w3.org/TR/uri-clarification/#RFC3986  
}
}

\newglossaryentry{URN}
{
    name={URN},
	description={
	Stands for Uniform Resource Name.  

	See http://www.w3.org/TR/uri-clarification/#RFC3986  
}
}

\newglossaryentry{UTC/GMT}
{
    name={UTC/GMT},
	description={
	Stands for Coordinated Universal Time/Greenwich Mean Time.  

	UTC/GMT is the primary time standard by which the world regulates clocks and time.

	The time stamp for all information reported in an \gls{MTConnect Response Document} is provided in UTC/GMT format.
}
}

\newglossaryentry{UUID}
{
    name={UUID},
	description={
	**ULHEADING:General meaning**:

	Stands for Universally Unique Identifier. (Can also be referred to as a GUID in some literature  Globally Unique Identifier).

	**BEGIN:note**
	Note:  Defined in RFC 4122 of the IETF.  See https://www.ietf.org/rfc/rfc4122.txt for more information.
	**END:note**

	Appears in the documents in the following form: UUID.

	**ULHEADING:Used as an attribute for an XML element**:

	Used as an attribute that provides a unique identity for a piece of information reported by an \gls{Agent}.

	Appears in the documents in the following form: \block{uuid}.
}
}

\newglossaryentry{Valid Data Value}
{
    name={Valid Data Value},
	description={
	One or more acceptable values or constrained values that can be reported for a \gls{Data Entity}.

	Appears in the documents in the following form: \gls{Valid Data Value}(s).
}
}

\newglossaryentry{Version}
{
    name={Version},
	description={}
}

\newglossaryentry{W3C}
{
    name={W3C},
	description={
	Stands for World Wide Web Consortium.

	W3C is an international community of organizations and the public work together to develop internet standards.  

	W3C Standards are used as a guide within the MTConnect Standard.
}
}

\newglossaryentry{WARNING}
{
    name={WARNING},
	description={
	**ULHEADING:General Meaning**:

	A statement or action that indicates a possible danger, problem, or other unexpected situation.

	*ULHEADING:Used relative to changes in an \gls{MTConnect Document}*:

	Used to indicate that specific content in an \gls{MTConnect Document} may be changed in a future release of the standard.

	Appears in the documents in the following form: **WARNING**.

	*ULHEADING:Used as a \gls{Valid Data Value} for a \gls{Condition}*:

	Used as a \gls{Valid Data Value} for a \gls{Condition} type \gls{Data Entity}.

	Appears in the documents in the following form: \block{WARNING}.

	*ULHEADING:Used as an \gls{Element Name} for a \gls{Data Entity}*:

	Used as the \gls{Element Name} for a \gls{Condition} type \gls{Data Entity} in an \gls{MTConnectStreams Response Document}.

	Appears in the documents in the following form: \block{Warning}.
}
}

\newglossaryentry{XML}
{
    name={XML},
	description={
	Stands for eXtensible Markup Language. 

	XML defines a set of rules for encoding documents that both a human-readable and machine-readable.

	XML is the language used for all code examples in the MTConnect Standard.

	Refer to http://www.w3.org/XML for more information about XML.
}
}

\newglossaryentry{XML Container}
{
    name={XML Container},
	description={
	In the MTConnect Standard, a type of XML element.

	An XML container is used to organize other XML elements that are logically related to each other.   A container may have either \gls{Data Entities} or other \gls{Structural Elements} as \gls{Child Elements}.
}
}

\newglossaryentry{XML Declaration}
{
    name={XML Declaration},
	description={It is a processing instruction that identifies the document as being XML.}
}

\newglossaryentry{XML Document}
{
    name={XML Document},
	description={
	An XML document is a structured text file encoded using XML.

	An XML document is an instantiation of an XML schema.  It has a single root XML element, conforms to the XML specification, and is structured based upon a specific schema.

	\gls{MTConnect Response Document} may be encoded as an XML document.
}
}

\newglossaryentry{XML Schema}
{
    name={XML Schema},
	description={
	In the MTConnect Standard, an instantiation of a schema defining a specific document encoded in XML.
}
}

\newglossaryentry{XPath}
{
    name={XPath},
	description={
	**ULHEADING:General meaning**:

	\gls{XPath} is a command structure that describes a way for a software system to locate information in an XML document.  

	\gls{XPath} uses an addressing syntax based on a path through the document's logical structure. 

	See http://www.w3.org/TR/xpath for more information on \gls{XPath}.

	Appears in the documents in the following form: \gls{XPath}.
}
}

\newglossaryentry{array3d}
{
    name={array3d},
	description={A three dimensional \gls{float} array.}
}

\newglossaryentry{arraystring}
{
    name={arraystring},
	description={An array of \gls{string}.}
}

\newglossaryentry{asset buffer}
{
    name={asset buffer},
	description={A buffer or queue for \block{Assets}.}
}

\newglossaryentry{boolean}
{
    name={boolean},
	description={Boolean data type.}
}

\newglossaryentry{buffer}
{
    name={buffer},
	description={
  **ULHEADING:General meaning**:

  A section of an \gls{Agent} that provides storage for information published from pieces of equipment.

  *ULHEADING:Used relative to \gls{Streaming Data}*:

  A section of an \gls{Agent} that provides storage for information relating to individual pieces of \gls{Streaming Data}. 
  
  Appears in the documents in the following form: \gls{buffer}.

  *ULHEADING:Used relative to \gls{MTConnect Asset}*:

  A section of an \gls{Agent} that provides storage for \gls{Asset Document}.

  Appears in the documents in the following form: \gls{assets buffer}.
}
}

\newglossaryentry{data dictionary}
{
    name={data dictionary},
	description={
	Listing of standardized terms and definitions used in \gls{MTConnect Information Model}.

	Appears in the documents in the following form: \gls{data dictionary}.
}
}

\newglossaryentry{datetime}
{
    name={datetime},
	description={DateTime (yyyy-mm-ddthh:mm:ss.ffff) data type.}
}

\newglossaryentry{float}
{
    name={float},
	description={Float data type.}
}

\newglossaryentry{heartbeat}
{
    name={heartbeat},
	description={
	**ULHEADING:General meaning**:

	A function that indicates to a client application that the communications connection to an \gls{Agent} is still viable during times when there is no new data available to report  often referred to as a "keep alive" message.

	Appears in the documents in the following form: \gls{heartbeat}.

	*ULHEADING:When used as part of an \gls{HTTP Request}*:

	The form \block{heartbeat} is used as a parameter in the query portion of an \gls{HTTP Request Line}.

	Appears in the documents in the following form: \block{heartbeat}.
}
}

\newglossaryentry{id}
{
    name={id},
	description={
	**ULHEADING:General meaning**:

	An identifier used to distinguish a piece of information.

	Appears in the documents in the following form: id.

	**ULHEADING:Used as an XML attribute**:

	When used as an attribute for an XML element - \gls{Structural Element}, \gls{Data Entity}, or \gls{Asset}.  \block{id} provides a unique identity for the element within an XML document.

	Appears in the documents in the following form: \block{id}.
}
}

\newglossaryentry{instance}
{
    name={instance},
	description={
	Describes a set of \gls{Streaming Data} in an \gls{Agent}.  Each time an \gls{Agent} is restarted with an empty \gls{buffer}, data placed in the \gls{buffer} represents a new \gls{instance} of the \gls{Agent}.

	Appears in the documents in the following form: \gls{instance}.
}
}

\newglossaryentry{integer}
{
    name={integer},
	description={Integer data type.}
}

\newglossaryentry{interfaces}
{
    name={interfaces},
	description={**CITETITLE:MTCPart5** provides an interaction model for coordinating activities between manufacturing devices}
}

\newglossaryentry{key-value pair}
{
    name={key-value pair},
	description={An association between an identifier referred to as the \gls{key} and a value which taken together create a \gls{key-value pair}. When used in a set of \gls{key-value pairs} each \gls{key} is unique and will only have one value associated with it at any point in time.}
}

\newglossaryentry{major}
{
    name={major},
	description={Identifier representing a consistent set of functionalities defined by the MTConnect Standard.}
}

\newglossaryentry{minor}
{
    name={minor},
	description={Identifier representing a specific set of functionalities defined by the MTConnect Standard.}
}

\newglossaryentry{namespace}
{
    name={namespace},
	description={\gls{namespace} are used to organize code into logical groups.}
}

\newglossaryentry{ontology}
{
    name={ontology},
	description={logical structure of the terms used to describe a domain of knowledge, including both the definitions of the applicable terms and their relationships ISO 20534:2018}
}

\newglossaryentry{parameter}
{
    name={parameter},
	description={
	**ULHEADING:General Meaning**:

	A variable that must be given a value during the execution of a program or a communications command.

	*ULHEADING:When used as part of an \gls{HTTP Request}*:

	Represents the content (keys and associated values) provided in the \gls{Query} portion of an \gls{HTTP Request Line} that identifies specific information to be returned in a \gls{Response Document}.

	Appears in the documents in the following form: parameter.
}
}

\newglossaryentry{reset}
{
    name={reset},
	description={A reset is associated with an occurrence of a \gls{Data Entity} indicated by the \\block{resetTriggered} attribute. When a reset occurs, the accumulated value or statistic are reverted back to their initial value. A \gls{Data Entity} with a \gls{Data Set} representation removes all \gls{key-value pairs}, setting the \gls{Data Set} to an empty set.}
}

\newglossaryentry{revision}
{
    name={revision},
	description={A supplemental identifier representing only organizational or editorial changes to a \gls{minor} version document with no changes in the functionality described in that document.}
}

\newglossaryentry{schema}
{
    name={schema},
	description={
	**ULHEADING:General meaning**:

	The definition of the structure, rules, and vocabularies used to define the information published in an electronic document.

	Appears in the documents in the following form: schema.

	*ULHEADING:Used in association with an \gls{MTConnect Response Document}*:

	Identifies a specific schema defined for an \gls{MTConnect Response Document}.

	Appears in the documents in the following form: \gls{schema}.
}
}

\newglossaryentry{semantic data model}
{
    name={semantic data model},
	description={
	A methodology for defining the structure and meaning for data in a specific logical way.  

	It provides the rules for encoding electronic information such that it can be interpreted by a software system.  

	Appears in the documents in the following form: \gls{semantic data model}.
}
}

\newglossaryentry{sensing element}
{
    name={sensing element},
	description={A mechanism that provides a signal or measured value.}
}

\newglossaryentry{sensor element}
{
    name={sensor element},
	description={A \gls{sensor element} provides a signal or measured value.}
}

\newglossaryentry{sensor unit}
{
    name={sensor unit},
	description={A \gls{sensor unit} provides signal processing, conversion, and communications.}
}

\newglossaryentry{sequence number}
{
    name={sequence number},
	description={
	The primary key identifier used to manage and locate a specific piece of \gls{Streaming Data} in an \gls{Agent}.

	\gls{sequence number} is a monotonically increasing number within an instance of an \gls{Agent}.

	Appears in the documents in the following form: \gls{sequence number}.
}
}

\newglossaryentry{string}
{
    name={string},
	description={String data type.}
}

\newglossaryentry{subtype}
{
    name={subtype},
	description={
	**ULHEADING:General meaning**:

	A secondary or subordinate type of categorization or classification of information.

	In software and data modeling, a subtype is a type of data that is related to another higher-level type of data.

	Appears in the documents in the following form: subtype.

	*ULHEADING:Used as an attribute for a \gls{Data Entity}*:

	Used as an attribute that provides a sub-categorization for the \block{type} attribute for a piece of information.

	Appears in the documents in the following form: \block{subType}.
}
}

\newglossaryentry{time stamp}
{
    name={time stamp},
	description={
	**ULHEADING:General meaning**:

	The best available estimate of the time that the value(s) for published or recorded information was measured or determined.

	Appears in the documents as "time stamp".

	**ULHEADING:Used as an attribute for recorded or published data**:

	An attribute that identifies the time associated with a \gls{Data Entity} as stored in an \gls{Agent}.

	Appears in the documents in the following form: \block{timestamp}.
}
}

\newglossaryentry{type}
{
    name={type},
	description={
	**ULHEADING:General meaning**:

	A classification or categorization of information.

	In software and data modeling, a type is a grouping function to identify pieces of information that share common characteristics. 

	Appears in the documents in the following form: type.

	*ULHEADING:Used as an attribute for a \gls{Data Entity}*:

	Used as an attribute that provides a categorization for piece of information that share common characteristics.

	Appears in the documents in the following form: \block{type}.
}
}
