% Generated 2020-10-22 16:25:27 +0530
\subsection{Condition Types} \label{sec:Condition Types}


\block{Condition} type elements are reported differently from other data item types. They are reported based on the \gls{Condition State} for each \block{Condition}.

The \property{type} and \property{subType} (where applicable) attributes for a \block{Condition} element \textbf{MAY} be any of the \property{type} and \property{subType} attributes defined for \texttt{SAMPLE} \property{category} or \texttt{EVENT} \property{category} \block{DataItem} listed in the \gls{Devices Information Model}.

This section lists additional \block{Condition} types that have been defined to represent the health and fault status of \glspl{Structural Element}.


\subsubsection{Actuator}




An indication of a fault associated with an actuator.


\subsubsection{ChuckInterlock}
\label{sec:ChuckInterlock}



An indication of the operational condition of the interlock function for an electronically controller chuck.


\subsubsection{Communications}
\label{sec:Communications}



An indication that the piece of equipment has experienced a communications failure.


\subsubsection{DataRange}
\label{sec:DataRange}



An indication that the value of the data associated with a measured value or a calculation is outside of an expected range.


\subsubsection{Direction}
\label{sec:Direction}



An indication of a fault associated with the direction of motion of a \gls{Structural Element}.


\subsubsection{EndOfBar}
\label{sec:EndOfBar}



An indication that the end of a piece of bar stock has been reached.


\subsubsection{Hardware}
\label{sec:Hardware}



An indication of a fault associated with the hardware subsystem of the \gls{Structural Element}.


\subsubsection{InterfaceState}
\label{sec:InterfaceState}



An indication of the operation condition of an \block{Interface} component.


\subsubsection{LogicProgram}
\label{sec:LogicProgram}



An indication that an error occurred in the logic program or programmable logic controller (PLC) associated with a piece of equipment.


\subsubsection{MotionProgram}
\label{sec:MotionProgram}



An indication that an error occurred in the motion program associated with a piece of equipment.


\subsubsection{System}
\label{sec:System}



An indication of a fault associated with a piece of equipment or component that cannot be classified as a specific type.

