% Generated 2021-02-25 13:56:53 +0530
\subsection{Streams} \label{sec:Streams}


\block{Streams} \glspl{organize} \block{DeviceStream} elements.

\block{Streams} \textbf{MAY} contain any number of \block{DeviceStream} elements. If there is no data to be reported for a request for data, an \block{MTConnectStreams} document \textbf{MUST} be returned with an empty \block{Streams} container.

\block{Streams} is the first, or highest, level element in an \block{MTConnectStreams} \gls{Response Document} provided by an \gls{Agent} in response to a \gls{Sample Request} or a \gls{Current Request}.

Note: See \sect{Observations Schema Diagrams} for XML schema of \block{Streams} model.


\subsubsection{DeviceStream}
\label{sec:DeviceStream}



\block{DeviceStream} \glspl{organize} data reported from a single piece of equipment. A \block{DeviceStream} element \textbf{MUST} be provided for each piece of equipment reporting data in an \block{MTConnectStreams} \gls{Response Document}.


\paragraph{Attributes of DeviceStream}\mbox{}
\label{sec:Attributes of DeviceStream}

\tbl{Attributes of DeviceStream} lists the attributes of \texttt{DeviceStream}.

\begin{table}[ht]
\centering 
  \caption{Attributes of DeviceStream}
  \label{table:Attributes of DeviceStream}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Attribute} & {Type} & {Multiplicity} \\
\tabucline[1.5pt]{}

\property{name}[DeviceStream] & \texttt{ID} & 1 \\
\property{uuid}[DeviceStream] & \texttt{ID} & 1 \\
\end{tabu}
\end{table}
\FloatBarrier

Descriptions for attributes of \block{DeviceStream}:

\begin{itemize}

\item \property{name}[DeviceStream] \newline The name of an element or a piece of equipment.

The value reported for \property{name}[DeviceStream] \textbf{MUST} be the same as the value defined for the \property{name}[Device] attribute of the same piece of equipment in the \block{MTConnectDevices} \gls{Response Document}.

\item \property{uuid}[DeviceStream] \newline The uuid associated with the piece of equipment.

The value reported for \property{uuid}[DeviceStream] \textbf{MUST} be the same as the value defined for the \property{uuid}[Device] attribute of the same piece of equipment in the \block{MTConnectDevices} \gls{Response Document}.
\end{itemize}


\paragraph{Elements of DeviceStream}\mbox{}
\label{sec:Elements of DeviceStream}

\tbl{Elements of DeviceStream} lists the elements of \texttt{DeviceStream}.

\begin{table}[ht]
\centering 
  \caption{Elements of DeviceStream}
  \label{table:Elements of DeviceStream}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Element} & {Multiplicity} \\
\tabucline[1.5pt]{}
\texttt{ComponentStream} & 1..* \\
\end{tabu}
\end{table}
\FloatBarrier


Descriptions for elements of \block{DeviceStream}:

\begin{itemize}

\item \block{ComponentStream} \newline See the following \sect{ComponentStream} for details.
\end{itemize}



\subsubsection{ComponentStream}
\label{sec:ComponentStream}



\block{ComponentStream} \glspl{organize} the data associated with each \gls{Structural Element} (\block{Device} element or \block{Component} element) defined for that piece of equipment in the associated \block{MTConnectDevices} \gls{Response Document}.

There \textbf{MUST} be at least one of \block{Sample}, \block{Event}, or \block{Condition} organized by a \block{ComponentStream} element.


\paragraph{Attributes of ComponentStream}\mbox{}
\label{sec:Attributes of ComponentStream}

\tbl{Attributes of ComponentStream} lists the attributes of \texttt{ComponentStream}.

\begin{table}[ht]
\centering 
  \caption{Attributes of ComponentStream}
  \label{table:Attributes of ComponentStream}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Attribute} & {Type} & {Multiplicity} \\
\tabucline[1.5pt]{}

\property{component}[ComponentStream] & \texttt{string} & 1 \\
\property{componentId}[ComponentStream] & \texttt{IDREF} & 1 \\
\property{name}[ComponentStream] & \texttt{string} & 0..1 \\
\property{nativeName}[ComponentStream] & \texttt{string} & 0..1 \\
\property{uuid}[ComponentStream] & \texttt{ID} & 0..1 \\
\end{tabu}
\end{table}
\FloatBarrier

Descriptions for attributes of \block{ComponentStream}:

\begin{itemize}

\item \property{component}[ComponentStream] \newline \property{component} identifies the \gls{Structural Element} associated with the \block{ComponentStream} element.

\item \property{componentId}[ComponentStream] \newline The identifier of the \gls{Structural Element} as defined by the \property{id}
attribute of the corresponding \gls{Structural Element} in the \block{MTConnectDevices} \gls{Response Document}.

\item \property{name}[ComponentStream] \newline The name of the \block{ComponentStream} element.

\item \property{nativeName}[ComponentStream] \newline \property{nativeName} identifies the common name normally associated with the \block{ComponentStream} element.

\item \property{uuid}[ComponentStream] \newline The uuid of the \block{ComponentStream} element.
\end{itemize}


\paragraph{Elements of ComponentStream}\mbox{}
\label{sec:Elements of ComponentStream}

\tbl{Elements of ComponentStream} lists the elements of \texttt{ComponentStream}.

\begin{table}[ht]
\centering 
  \caption{Elements of ComponentStream}
  \label{table:Elements of ComponentStream}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Element} & {Multiplicity} \\
\tabucline[1.5pt]{}
\texttt{Event} (organized by \block{Events}) & 0..* \\
\texttt{Sample} (organized by \block{Samples}) & 0..* \\
\texttt{Condition} (organized by \block{Conditions}) & 0..* \\
\end{tabu}
\end{table}
\FloatBarrier


Descriptions for elements of \block{ComponentStream}:

\begin{itemize}

\item \block{Events} \newline \block{Events} \glspl{organize} the \block{Event} elements.

See \sect{Event} for details on the \block{Event} model.

\item \block{Samples} \newline \block{Samples} \glspl{organize} the \block{Sample} elements.


See \sect{Sample} for details on the \block{Sample} model.

\item \block{Conditions} \newline \block{Condition} \glspl{organize} the \block{Condition} elements.

See \sect{Condition} for details on the \block{Condition} model.
\end{itemize}


