\tabulinesep = 5pt
\begin{longtabu} to \textwidth {
    |l|X[3l]|X[0.75l]|}
\caption{Attributes for Composition} \label{table:attributes-for-composition} \\

\hline
Attribute & Description & Occurrence \\
\hline
\endfirsthead

\hline
\multicolumn{3}{|c|}{Continuation of Table \ref{table:attributes-for-composition}}\\
\hline
Attribute & Description & Occurrence \\
\hline
\endhead
 
\gls{id} 
&
\glsentrydesc{id}
\newline \gls{id} is a required attribute.
\newline An \gls{id} \MUST be unique across all the \gls{id} attributes in the document.
\newline An XML ID-type.
&
1 \\
\hline

\gls{uuid}
&
A unique identifier for this XML element.
\newline \gls{uuid} is an optional attribute. 
\newline The \gls{uuid} \MUST be unique amongst all \gls{uuid} identifiers used in an MTConnect installation. 
\newline For example, this may be a combination of the manufacturer’s code and serial number. The \gls{uuid} \SHOULD be alphanumeric and not exceed 255 characters.
\newline An \gls{nmtoken} XML type.
&
0..1 \\
\hline

\gls{name}
&
The name of the \gls{composition} element.
\newline \gls{name} is an optional attribute.
\newline If provided, \gls{name} \MUST be unique within a \gls{component} element.
\newline An \gls{nmtoken} XML type.
&
0..1 \\
\hline

\gls{type}
&
The type of \gls{composition} element.
\newline \gls{type} is a required attribute.
\newline Examples of types are \gls{motor}, \gls{filter type}, \gls{pump}, and \gls{amplifier}.
\newline Refer to \sect{Composition Type Structural Elements} for a list of currently defined types.
&
1 \\
\hline

\end{longtabu}