
\begin{longtabu} to \textwidth{|l|X[3l]|l|}
\caption{Attributes for ComponentRelationship} \label{table:attributes-for-componentrelationship} \\

\hline
Attribute & Description & Occurrence \\
\hline
\endfirsthead

\hline
\multicolumn{3}{|c|}{Continuation of Table \ref{table:attributes-for-componentrelationship}}\\
\hline
Attribute & Description & Occurrence \\
\hline
\endhead
 




\gls{id}
&
The unique identifier for this \gls{componentrelationship}.
\newline \gls{id} is a required attribute.
\newline The \gls{id} attribute \MUST be unique within the \gls{mtconnectdevices} document.
\newline An XML ID-type.
&
1 \\
\hline

\gls{name}
&
The name associated with this \gls{componentrelationship}.
\newline \gls{name} is provided as an additional human readable identifier for this \gls{componentrelationship}.
\newline \gls{name} is an optional attribute.
\newline An \gls{nmtoken} XML type.
&
0..1 \\
\hline

\gls{type}
&
Defines the authority that this component element has relative to the associated component element.
\newline \gls{type} is a required attribute.
\newline The value provided for \gls{type} \MUST be one of the following values:
\newline \tab \gls{parent}:  This component functions as a parent in the relationship with the associated component element.
\newline  \tab \gls{child}:  This component functions as a child in the relationship with the associated component element.
\newline  \tab \gls{peer}:  This component functions as a peer which provides equal functionality and capabilities in the relationship with the associated component element.
&
1 \\
\hline

\gls{criticality}
&
Defines whether the services or functions provided by the associated component element is required for the operation of this piece of equipment.
\newline \gls{criticality} is an optional attribute.
\newline The value provided for \gls{criticality} \MUST be one of the following values:
\newline \tab \gls{critical}:  The services or functions provided by the associated component element is required for the operation of this piece of equipment.
\newline  \tab \gls{noncritical}:  The services or functions provided by the associated component element is not required for the operation of this piece of equipment.
&
0..1 \\
\hline

\gls{idref}
&
A reference to the associated component element.
\newline The value provided for \gls{idref} \MUST be the value provided for the \gls{id} attribute of the associated \gls{component} element.
\newline \gls{idref} is a required attribute.
\newline An \gls{nmtoken} XML type.
&
1 \\
\hline\end{longtabu}