% Generated 2020-07-27 15:21:27 +0530
\subsection{Compositions} \label{sec:Compositions}

{block:Compositions} {term:organizes} the {block:Composition} elements within a {block:Component} element.


\subsubsection{Composition}
  \label{sec:Composition}


{block:Composition} is used to describe the lowest level structural building blocks contained within a {block:Component} element.

There can be multiple types of {block:Composition} elements defined for a {block:Component} element.


\paragraph{Attributes of Composition}\mbox{}
\label{sec:Attributes of Composition}

\tbl{attributes of Composition} lists the attributes of \texttt{Composition}.

\begin{table}[ht]
\centering 
  \caption{Attributes of Composition}
  \label{table:attributes of Composition}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Attribute} & {Type} & {Multiplicity} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{CompositionTypeEnum} & 1 \\
\texttt{id} & \texttt{ID} & 1 \\
\texttt{name} & \texttt{string} & 0..1 \\
\texttt{uuid} & \texttt{NMTOKEN} & 0..1 \\
\end{tabu}
\end{table}
\FloatBarrier


Descriptions for attributes of \texttt{Composition}:

\begin{itemize}
\item \texttt{type} : The type of either a {term:Structural Element} or a {block:DataItem} being measured.
\item \texttt{id} : The unique identifier for this element.
\item \texttt{name} : The name of this element.
\item \texttt{uuid} : A unique identifier for this element.
\end{itemize}

\paragraph{Elements of Composition}\mbox{}
\label{sec:Elements of Composition}

\tbl{elements of Composition} lists the elements of \texttt{Composition}.

\begin{table}[ht]
\centering 
  \caption{Elements of Composition}
  \label{table:elements of Composition}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Association Name} & {Element} & {Multiplicity} \\
\tabucline[1.5pt]{}
\texttt{Description} & \texttt{Description} & 0..1 \\
\end{tabu}
\end{table}
\FloatBarrier


Descriptions for elements of \texttt{Composition}:

\begin{itemize}
\item \texttt{Description} : An element that can contain any descriptive content.
\end{itemize}
\FloatBarrier
