% Generated 2021-02-25 13:56:51 +0530
\subsection{Composition Types} \label{sec:Composition Types}


This section defines \block{Composition} type elements that are currently available to describe sub-parts of a \block{Component} element.


\subsubsection[Actuator]{Actuator \\ {\small type: ACTUATOR}}




A mechanism for moving or controlling a mechanical part of a piece of equipment.   
 It takes energy usually provided by air, electric current, or liquid and converts the energy into some kind of motion. 



\subsubsection[Amplifier]{Amplifier \\ {\small type: AMPLIFIER}}
\label{sec:Amplifier}



An electronic component or circuit for amplifying power, electric current, or voltage.



\subsubsection[Ballscrew]{Ballscrew \\ {\small type: BALLSCREW}}
\label{sec:Ballscrew}



A mechanical structure for transforming rotary motion into linear motion.



\subsubsection[Belt]{Belt \\ {\small type: BELT}}
\label{sec:Belt}



An endless flexible band used to transmit motion for a piece of equipment or to convey materials and objects.



\subsubsection[Brake]{Brake \\ {\small type: BRAKE}}
\label{sec:Brake}



A mechanism for slowing or stopping a moving object by the absorption or transfer of the energy of momentum, usually by means of friction, electrical force, or magnetic force.



\subsubsection[Chain]{Chain \\ {\small type: CHAIN}}
\label{sec:Chain}



An interconnected series of objects that band together and are used to transmit motion for a piece of equipment or to convey materials and objects.



\subsubsection[Chopper]{Chopper \\ {\small type: CHOPPER}}
\label{sec:Chopper}



A mechanism used to break material into smaller pieces.



\subsubsection[Chuck]{Chuck \\ {\small type: CHUCK}}




A mechanism that holds a part, stock material, or any other item in place.



\subsubsection[Chute]{Chute \\ {\small type: CHUTE}}
\label{sec:Chute}



An inclined channel for conveying material.



\subsubsection[CircuitBreaker]{CircuitBreaker \\ {\small type: CIRCUIT\textunderscore BREAKER}}
\label{sec:CircuitBreaker}



A mechanism for interrupting an electric circuit.



\subsubsection[Clamp]{Clamp \\ {\small type: CLAMP}}
\label{sec:Clamp}



A mechanism used to strengthen, support, or fasten objects in place.



\subsubsection[Compressor]{Compressor \\ {\small type: COMPRESSOR}}
\label{sec:Compressor}



A pump or other mechanism for reducing volume and increasing pressure of gases in order to condense the gases to drive pneumatically powered pieces of equipment.



\subsubsection[CoolingTower]{CoolingTower \\ {\small type: COOLING\textunderscore TOWER}}
\label{sec:CoolingTower}



A heat exchange system that uses a fluid to transfer heat to the atmosphere.



\subsubsection[Door]{Door \\ {\small type: DOOR}}




A mechanical mechanism or closure that can cover a physical access portal into a piece of equipment allowing or restricting access to other parts of the equipment.



\subsubsection[Drain]{Drain \\ {\small type: DRAIN}}
\label{sec:Drain}



A mechanism that allows material to flow for the purpose of drainage from, for example, a vessel or tank.



\subsubsection[Encoder]{Encoder \\ {\small type: ENCODER}}
\label{sec:Encoder}



A mechanism to measure position.



\subsubsection[ExpiredPot]{ExpiredPot \\ {\small type: EXPIRED\textunderscore POT}}
\label{sec:ExpiredPot}



A \block{Pot} for a tool that is no longer useable for removal from a \block{ToolMagazine} or \block{Turret}.



\subsubsection[ExposureUnit]{ExposureUnit \\ {\small type: EXPOSURE\textunderscore UNIT}}
\label{sec:ExposureUnit}



A mechanism for emitting a type of radiation



\subsubsection[ExtrusionUnit]{ExtrusionUnit \\ {\small type: EXTRUSION\textunderscore UNIT}}
\label{sec:ExtrusionUnit}



A mechanism for dispensing liquid or powered materials



\subsubsection[Fan]{Fan \\ {\small type: FAN}}
\label{sec:Fan}



Any mechanism for producing a current of air.



\subsubsection[Filter]{Filter \\ {\small type: FILTER}}
\label{sec:Filter}



Any substance or structure through which liquids or gases are passed to remove suspended impurities or to recover solids.



\subsubsection[Galvanomotor]{Galvanomotor \\ {\small type: GALVANOMOTOR}}
\label{sec:Galvanomotor}



An electromechanical actuator that produces deflection of a beam of light or energy in response to electric current through its coil in a magnetic field.



\subsubsection[Gripper]{Gripper \\ {\small type: GRIPPER}}
\label{sec:Gripper}



A mechanism that holds a part, stock material, or any other item in place.



\subsubsection[Hopper]{Hopper \\ {\small type: HOPPER}}
\label{sec:Hopper}



A chamber or bin in which materials are stored temporarily, typically being filled through the top and dispensed through the bottom.



\subsubsection[LinearPositionFeedback]{LinearPositionFeedback \\ {\small type: LINEAR\textunderscore POSITION\textunderscore FEEDBACK}}
\label{sec:LinearPositionFeedback}



A mechanism that measures linear motion or position.

\textbf{DEPRECATION WARNING} : May be deprecated in the future. Recommend using \block{ENCODER}.



\subsubsection[Motor]{Motor \\ {\small type: MOTOR}}
\label{sec:Motor}



A mechanism that converts electrical, pneumatic, or hydraulic energy into mechanical energy.



\subsubsection[Oil]{Oil \\ {\small type: OIL}}
\label{sec:Oil}



A viscous liquid.



\subsubsection[Pot]{Pot \\ {\small type: POT}}
\label{sec:Pot}



A tool storage location associated with a \block{ToolMagazine} or \block{AutomaticToolChanger}.



\subsubsection[PowerSupply]{PowerSupply \\ {\small type: POWER\textunderscore SUPPLY}}
\label{sec:PowerSupply}



A unit that provides power to electric mechanisms.



\subsubsection[Pulley]{Pulley \\ {\small type: PULLEY}}
\label{sec:Pulley}



A mechanism or wheel that turns in a frame or block and serves to change the direction of or to transmit force.



\subsubsection[Pump]{Pump \\ {\small type: PUMP}}
\label{sec:Pump}



An apparatus raising, driving, exhausting, or compressing fluids or gases by means of a piston, plunger, or set of rotating vanes.



\subsubsection[Reel]{Reel \\ {\small type: REEL}}
\label{sec:Reel}



A rotary storage unit for material



\subsubsection[RemovalPot]{RemovalPot \\ {\small type: REMOVAL\textunderscore POT}}
\label{sec:RemovalPot}



A \block{Pot} for a tool to be removed from a \block{ToolMagazine} or \block{Turret} to a location outside of the piece of equipment.



\subsubsection[ReturnPot]{ReturnPot \\ {\small type: RETURN\textunderscore POT}}
\label{sec:ReturnPot}



A \block{Pot} for a tool removed from \gls{Spindle} or \block{Turret} and awaiting for return to a \block{ToolMagazine}.



\subsubsection[SensingElement]{SensingElement \\ {\small type: SENSING\textunderscore ELEMENT}}
\label{sec:SensingElement}



A mechanism that provides a signal or measured value.



\subsubsection[Spreader]{Spreader \\ {\small type: SPREADER}}
\label{sec:Spreader}



A mechanism for flattening or spreading materials



\subsubsection[StagingPot]{StagingPot \\ {\small type: STAGING\textunderscore POT}}
\label{sec:StagingPot}



A \block{Pot} for a tool awaiting transfer to a \block{ToolMagazine} or \block{Turret} from outside of the piece of equipment.



\subsubsection[Station]{Station \\ {\small type: STATION}}
\label{sec:Station}



A storage or mounting location for a tool associated with a \block{Turret}, \block{GangToolBar}, or \block{ToolRack}.



\subsubsection[StorageBattery]{StorageBattery \\ {\small type: STORAGE\textunderscore BATTERY}}
\label{sec:StorageBattery}



A component consisting of one or more cells, in which chemical energy is converted into electricity and used as a source of power. 



\subsubsection[Switch]{Switch \\ {\small type: SWITCH}}
\label{sec:Switch}



A mechanism for turning on or off an electric current or for making or breaking a circuit.



\subsubsection[Table]{Table \\ {\small type: TABLE}}




A surface for holding an object or material



\subsubsection[Tank]{Tank \\ {\small type: TANK}}
\label{sec:Tank}



A receptacle or container for holding material.



\subsubsection[Tensioner]{Tensioner \\ {\small type: TENSIONER}}
\label{sec:Tensioner}



A mechanism that provides or applies a stretch or strain to another mechanism.



\subsubsection[TransferArm]{TransferArm \\ {\small type: TRANSFER\textunderscore ARM}}
\label{sec:TransferArm}



A mechanism for physically moving a tool from one location to another.



\subsubsection[TransferPot]{TransferPot \\ {\small type: TRANSFER\textunderscore POT}}
\label{sec:TransferPot}



A \block{Pot} for a tool awaiting transfer from a \block{ToolMagazine} to \gls{Spindle} or \block{Turret}.



\subsubsection[Transformer]{Transformer \\ {\small type: TRANSFORMER}}
\label{sec:Transformer}



A mechanism that transforms electric energy from a source to a secondary circuit.



\subsubsection[Valve]{Valve \\ {\small type: VALVE}}
\label{sec:Valve}



Any mechanism for halting or controlling the flow of a liquid, gas, or other material through a passage, pipe, inlet, or outlet.



\subsubsection[Vat]{Vat \\ {\small type: VAT}}
\label{sec:Vat}



A container for liquid or powdered materials



\subsubsection[Water]{Water \\ {\small type: WATER}}
\label{sec:Water}



A fluid.



\subsubsection[Wire]{Wire \\ {\small type: WIRE}}
\label{sec:Wire}



A string like piece or filament of relatively rigid or flexible material provided in a variety of diameters.



\subsubsection[Workpiece]{Workpiece \\ {\small type: WORKPIECE}}
\label{sec:Workpiece}



An object or material on which a form of work is performed.


