% Generated 2021-08-25 18:02:22 +0530
\subsection{Devices} \label{sec:Devices}


\block{Devices} \textbf{MUST} \gls{organize} one or more \block{Device} elements.


\subsubsection{Device}
\label{sec:Device}



A \block{Device} is a \block{Component} that represents a piece of equipment that produces \glspl{observation} about itself. It \glspl{organize} its parts as \block{Components}.

A \block{Device} \textbf{MUST} have a \property{name} and \property{uuid} attribute to identify itself. 

A \block{Device} \textbf{MUST} have the following \block{DataItems}: \block{Availability}, \block{AssetChanged}, and \block{AssetRemoved}.

See \sect{Component} for details on the \block{Device} model. 



\paragraph{Attributes of Device}\mbox{}
\label{sec:Attributes of Device}

\tbl{Attributes of Device} lists the attributes of \texttt{Device}.

\begin{table}[ht]
\centering 
  \caption{Attributes of Device}
  \label{table:Attributes of Device}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Attribute} & {Type} & {Multiplicity} \\
\tabucline[1.5pt]{}

\property{iso841Class}[Device] & \texttt{string} & 0..1 \\
\property{uuid}[Device] & \texttt{ID} & 1 \\
\property{mtconnectVersion}[Device] & \texttt{string} & 0..1 \\
\property{name}[Device] & \texttt{string} & 1 \\
\end{tabu}
\end{table}
\FloatBarrier

Descriptions for attributes of \block{Device}:

\begin{itemize}

\item \property{iso841Class}[Device] \newline \textbf{DEPRECATED} in \textit{MTConnect Version 1.1}.

\item \property{mtconnectVersion}[Device] \newline The MTConnect version of the \gls{Device Information Model} used to configure the information to be published for a piece of equipment in an \gls{MTConnect Response Document}.
\end{itemize}


\paragraph{Elements of Device}\mbox{}
\label{sec:Elements of Device}

\tbl{Elements of Device} lists the elements of \texttt{Device}.

\begin{table}[ht]
\centering 
  \caption{Elements of Device}
  \label{table:Elements of Device}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Element} & {Multiplicity} \\
\tabucline[1.5pt]{}
\texttt{Process} (organized by \block{Processes}) & 0..* \\
\texttt{Structure} (organized by \block{Structures}) & 0..* \\
\texttt{Resource} (organized by \block{Resources}) & 0..* \\
\texttt{Interface} (organized by \block{Interfaces}) & 0..* \\
\texttt{Adapter} (organized by \block{Adapters}) & 0..* \\
\texttt{Axis} (organized by \block{Axes}) & 0..* \\
\texttt{System} (organized by \block{Systems}) & 0..* \\
\texttt{Auxiliary} (organized by \block{Auxiliaries}) & 0..* \\
\texttt{Part} (organized by \block{Parts}) & 0..* \\
\end{tabu}
\end{table}
\FloatBarrier


Descriptions for elements of \block{Device}:

\begin{itemize}

\item \block{Processes} \newline \block{Processes} \glspl{organize} \block{Process} component types. 

\item \block{Structures} \newline \block{Structures} \glspl{organize} \block{Structure} component types. 

\item \block{Resources} \newline \block{Resources} \glspl{organize} \block{Resource} component types. 

\item \block{Interfaces} \newline \block{Interfaces} \glspl{organize} \block{Interface} component types. 

\item \block{Adapters} \newline \block{Adapters} \glspl{organize} \block{Adapter} component types. 

\item \block{Axes} \newline \block{Axes} \glspl{organize} \block{Axis} component types. 

\item \block{Systems} \newline \block{Systems} \glspl{organize} \block{System} component types. 

\item \block{Auxiliaries} \newline \block{Auxiliaries} \glspl{organize} \block{Auxiliary} component types. 

\item \block{Parts} \newline \block{Parts} \glspl{organize} information for \glspl{part} being processed by a piece of equipment.
\end{itemize}



\subsubsection{Agent}
\label{sec:Agent}



\block{Agent} is a \block{Device} representing the \gls{MTConnect Agent} and all its connected data sources.

* It \textbf{MUST} be provided by all \gls{MTConnect Agent} implementations.

\begin{itemize}
    \item It \textbf{MUST} be provided by all \gls{MTConnect Agent} implementations.
    \item It \textbf{MUST} provide notifications when devices are added or changed.
    \item It \textbf{MUST} provide connection information for each data source currently supplying data to the \gls{MTConnect Agent}.
    \item \textbf{MAY} provide information about telemetry relating to data sources.
    \item It \textbf{MAY} provide information about the \gls{MTConnect Agent} resource utilization.

\end{itemize}

