% Generated 2020-10-22 16:25:25 +0530
\subsection{Elements for DataItem} \label{sec:Elements for DataItem}


This section provides detailed descriptions for the elements of a \block{DataItem}.


\subsubsection{Constraints}
\label{sec:Constraints}



\block{Constraints} \glspl{organize} a set of expected values that can be reported for this \block{DataItem}.


\paragraph{Elements of Constraints}\mbox{}
\label{sec:Elements of Constraints}

\tbl{Elements of Constraints} lists the elements of \texttt{Constraints}.

\begin{table}[ht]
\centering 
  \caption{Elements of Constraints}
  \label{table:Elements of Constraints}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Element Name} & {Type} & {Multiplicity} \\
\tabucline[1.5pt]{}
\texttt{<<deprecated>>} \block{Filter} & \texttt{FilterEnum} & 0..1 \\
\block{Maximum} & \texttt{float} & 0..1 \\
\block{Minimum} & \texttt{float} & 0..1 \\
\block{Nominal} & \texttt{float} & 0..1 \\
\block{Value} & \texttt{float} & 0..* \\
\end{tabu}
\end{table}
\FloatBarrier


Descriptions for elements of \block{Constraints}:

\begin{itemize}
\item \block{Filter} : \textbf{DEPRECATED} in \textit{MTConnect Version 1.4} – Moved to the
\block{Filters} element of \block{DataItem}.
\item \block{Maximum} : If the data reported for a data item is a range of numeric values, the expected value reported \textbf{MAY} be described with an upper limit defined by this constraint.
\item \block{Minimum} : If the data reported for a data item is a range of numeric values, the expected value reported \textbf{MAY} be described with a lower limit defined by this constraint.
\item \block{Nominal} : The target or expected value for this data item.
\item \block{Value} : \property{Value} represents a single data value that is expected to be reported for a \block{DataItem} element.

\property{Value} \textbf{MUST NOT} be used in conjunction with any other \block{Constraint} elements.
\end{itemize}

\subsubsection{Definition}
\label{sec:Definition}



The \block{Definition} defines the meaning of \block{Entry} and \block{Cell} elements associated with the \block{DataItem} when the \property{representation} is either \block{DATA} or \block{TABLE}.


\paragraph{Elements of Definition}\mbox{}
\label{sec:Elements of Definition}

\tbl{Elements of Definition} lists the elements of \texttt{Definition}.

\begin{table}[ht]
\centering 
  \caption{Elements of Definition}
  \label{table:Elements of Definition}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Element Name} & {Type} & {Multiplicity} \\
\tabucline[1.5pt]{}
\block{CellDefinitions} & \texttt{CellDefinition} & 0..* \\
\block{Description} & \texttt{Description} & 0..1 \\
\block{EntryDefinitions} & \texttt{EntryDefinition} & 0..* \\
\end{tabu}
\end{table}
\FloatBarrier


Descriptions for elements of \block{Definition}:

\begin{itemize}
\item \block{CellDefinitions} : \block{CellDefinitions} \glspl{organize} \block{CellDefinition} elements.
\item \block{Description} : The \block{Description} of the \block{Definition}. See \block{Component} \block{Description}.
\item \block{EntryDefinitions} : \block{EntryDefinitions} \glspl{organize} \block{EntryDefinition} elements.
\end{itemize}

\subsubsection{Filter}




\block{Filter} provides a means to control when an \gls{Agent} records updated information for a data item. 


\paragraph{Attributes of Filter}\mbox{}
\label{sec:Attributes of Filter}

\tbl{Attributes of Filter} lists the attributes of \texttt{Filter}.

\begin{table}[ht]
\centering 
  \caption{Attributes of Filter}
  \label{table:Attributes of Filter}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Attribute} & {Type} & {Multiplicity} \\
\tabucline[1.5pt]{}
\property{type}[Filter] & \texttt{FilterEnum} & 1 \\
\end{tabu}
\end{table}
\FloatBarrier


Descriptions for attributes of \block{Filter}:

\begin{itemize}

\item \property{type}[Filter] : The type of \block{Filter}

\tabulinesep = 5pt
\begin{longtabu} to \textwidth {
    |l|X|}
\caption{FilterEnum Enumeration}
\label{enum:FilterEnum} \\

\hline
Name & Description \\
\hline
\endfirsthead
\hline
\multicolumn{2}{|c|}{Continuation of Table \texttt{FilterEnum} Enumeration} \\
\hline
Name & Description \\
\hline
\endhead
\texttt{MINIMUM\textunderscore DELTA} & For a \texttt{MINIMUM\textunderscore DELTA} type \block{Filter}, a new value \textbf{MUST NOT} be reported for a data item unless the measured value has changed from the
last reported value by at least the delta given as the value of this element.

The value of \block{Filter} \textbf{MUST} be an absolute value using the same units as the reported data. \\ \hline
\texttt{PERIOD} & For a \texttt{PERIOD} type \block{Filter}, the data reported for a data item is provided on a periodic basis. The \texttt{PERIOD} for reporting data is defined in the
value of the \block{Filter}.

The value of \block{Filter} \textbf{MUST} be an absolute value reported in seconds representing the time between reported samples of the value of the data item. \\ \hline
\end{longtabu}

\end{itemize}

\subsubsection{InitialValue}
\label{sec:InitialValue}



\block{InitialValue} defines the starting value for a data item as well as the value to be set for the data item after a reset event.


\paragraph{Attributes of InitialValue}\mbox{}
\label{sec:Attributes of InitialValue}

\tbl{Attributes of InitialValue} lists the attributes of \texttt{InitialValue}.

\begin{table}[ht]
\centering 
  \caption{Attributes of InitialValue}
  \label{table:Attributes of InitialValue}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Attribute} & {Type} & {Multiplicity} \\
\tabucline[1.5pt]{}
\property{value}[InitialValue] & \texttt{string} & 1 \\
\end{tabu}
\end{table}
\FloatBarrier


Descriptions for attributes of \block{InitialValue}:

\begin{itemize}

\item \property{value}[InitialValue] : 
\end{itemize}

\subsubsection{ResetTrigger}
\label{sec:ResetTrigger}



\block{ResetTrigger} identifies the type of event that may cause a reset to occur.


\paragraph{Attributes of ResetTrigger}\mbox{}
\label{sec:Attributes of ResetTrigger}

\tbl{Attributes of ResetTrigger} lists the attributes of \texttt{ResetTrigger}.

\begin{table}[ht]
\centering 
  \caption{Attributes of ResetTrigger}
  \label{table:Attributes of ResetTrigger}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Attribute} & {Type} & {Multiplicity} \\
\tabucline[1.5pt]{}
\property{type}[ResetTrigger] & \texttt{ResetTriggerEnum} & 1 \\
\end{tabu}
\end{table}
\FloatBarrier


Descriptions for attributes of \block{ResetTrigger}:

\begin{itemize}

\item \property{type}[ResetTrigger] : The type of \block{ResetTrigger}

\tabulinesep = 5pt
\begin{longtabu} to \textwidth {
    |l|X|}
\caption{ResetTriggerEnum Enumeration}
\label{enum:ResetTriggerEnum} \\

\hline
Name & Description \\
\hline
\endfirsthead
\hline
\multicolumn{2}{|c|}{Continuation of Table \texttt{ResetTriggerEnum} Enumeration} \\
\hline
Name & Description \\
\hline
\endhead
\texttt{ACTION\textunderscore COMPLETE} & The value of the \gls{Data Item} that is measuring an action or operation is to be reset upon completion of that action or operation. \\ \hline
\texttt{ANNUAL} & The value of the \gls{Data Item} is to be reset at the end of a 12-month period. \\ \hline
\texttt{DAY} & The value of the \gls{Data Item} is to be reset at the end of a 24-hour period. \\ \hline
\texttt{LIFE} & The value of the \gls{Data Item} is not reset and accumulates for the entire life of the piece of equipment. \\ \hline
\texttt{MAINTENANCE} & The value of the \gls{Data Item} is to be reset upon completion of a maintenance event. \\ \hline
\texttt{MONTH} & The value of the \gls{Data Item} is to be reset at the end of a monthly period. \\ \hline
\texttt{POWER\textunderscore ON} & The value of the \gls{Data Item} is to be reset when power was applied to the piece of equipment after a planned or unplanned interruption of power has occurred. \\ \hline
\texttt{SHIFT} & The value of the \gls{Data Item} is to be reset at the end of a work shift. \\ \hline
\texttt{WEEK} & The value of the \gls{Data Item} is to be reset at the end of a 7-day period. \\ \hline
\end{longtabu}

\end{itemize}

\subsubsection{Source}
\label{sec:Source}



\block{Source} identifies the \block{Component}, \block{DataItem}, or \block{Composition} representing the area of the piece of equipment from which a measured value originates.


\paragraph{Attributes of Source}\mbox{}
\label{sec:Attributes of Source}

\tbl{Attributes of Source} lists the attributes of \texttt{Source}.

\begin{table}[ht]
\centering 
  \caption{Attributes of Source}
  \label{table:Attributes of Source}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Attribute} & {Type} & {Multiplicity} \\
\tabucline[1.5pt]{}
\property{componentId}[Source] & \texttt{ID} & 0..1 \\
\property{compositionId}[Source] & \texttt{ID} & 0..1 \\
\property{dataItemId}[Source] & \texttt{ID} & 0..1 \\
\property{value}[Source] & \texttt{string} & 0..1 \\
\end{tabu}
\end{table}
\FloatBarrier


Descriptions for attributes of \block{Source}:

\begin{itemize}

\item \property{componentId}[Source] : The identifier attribute of the \block{Component} element that represents the physical part of a piece of equipment where the data represented by the \block{DataItem} element originated.

\item \property{compositionId}[Source] : The identifier attribute of the \block{Composition} element that the reported data is most closely associated.

\item \property{dataItemId}[Source] : The identifier attribute of the \block{DataItem} that represents the originally measured value of the data referenced by this data item.

\item \property{value}[Source] : The value of the id of the source element.
\end{itemize}
