% Generated 2020-02-05 07:16:58 -0500
\subsection{EventTypes} \label{model:EventTypes}
\subsubsection[ActiveAxes]{ActiveAxes \\ {\small Subtype of Event}}
  \label{type:ActiveAxes}

\FloatBarrier

The set of axes currently associated with a {model:Path} or {model:Controller} {term:Structural Element}.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ActiveAxes}}
  \label{properties:ActiveAxes}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{ACTIVE_AXES} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[ActuatorState]{ActuatorState \\ {\small Subtype of Event}}
  \label{type:ActuatorState}

\FloatBarrier

Represents the operational state of an apparatus for moving or controlling a mechanism or system.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ActuatorState}}
  \label{properties:ActuatorState}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{ACTUATOR_STATE} \\
\texttt{result} & \texttt{ActuatorStateEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Alarm]{Alarm \\ {\small Subtype of Event}}
  \label{type:Alarm}

\FloatBarrier

*DEPRECATED:* Replaced with {model:CONDITION} category data items in Version 1.1.0.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Alarm}}
  \label{properties:Alarm}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{ALARM} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[AssetChanged]{AssetChanged \\ {\small Subtype of Event}}
  \label{type:AssetChanged}

\FloatBarrier

The value of the {term:CDATA} for the event *MUST* be the {model:assetId} of the asset that has been added or changed. There will not be a separate message for new assets.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of AssetChanged}}
  \label{properties:AssetChanged}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{ASSET_CHANGED} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[AssetRemoved]{AssetRemoved \\ {\small Subtype of Event}}
  \label{type:AssetRemoved}

\FloatBarrier

The value of the {term:CDATA} for the event *MUST* be the {model:assetId} of the asset that has been removed. The asset will still be visible if requested with the {model:includeRemoved} parameter as described in the protocol section. When assets are removed they are not moved to the beginning of the most recently modified list.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of AssetRemoved}}
  \label{properties:AssetRemoved}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{ASSET_REMOVED} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Availability]{Availability \\ {\small Subtype of Event}}
  \label{type:Availability}

\FloatBarrier

Represents the {term:Agent}'s ability to communicate with the data source.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Availability}}
  \label{properties:Availability}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{AVAILABILITY} \\
\texttt{result} & \texttt{AvailabilityEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[AxisCoupling]{AxisCoupling \\ {\small Subtype of Event}}
  \label{type:AxisCoupling}

\FloatBarrier

Describes the way the axes will be associated to each other. 
  
 This is used in conjunction with {model:COUPLED_AXES} to indicate the way they are interacting.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of AxisCoupling}}
  \label{properties:AxisCoupling}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{AXIS_COUPLING} \\
\texttt{result} & \texttt{AxisCouplingEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[AxisFeedrateOverride]{AxisFeedrateOverride \\ {\small Subtype of Event}}
  \label{type:AxisFeedrateOverride}

\FloatBarrier

The value of a signal or calculation issued to adjust the feedrate of an individual linear type axis.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of AxisFeedrateOverride}}
  \label{properties:AxisFeedrateOverride}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{AXIS_FEEDRATE_OVERRIDE} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[JogAxisFeedrateOverride]{JogAxisFeedrateOverride \\ {\small Subtype of AxisFeedrateOverride}}\mbox{}
  \label{type:JogAxisFeedrateOverride}

\FloatBarrier

The feedrate specified by a logic or motion program, by a pre-set value, or set by a switch as the feedrate for the {model:Axes}. 

\paragraph[ProgrammedAxisFeedrateOverride]{ProgrammedAxisFeedrateOverride \\ {\small Subtype of AxisFeedrateOverride}}\mbox{}
  \label{type:ProgrammedAxisFeedrateOverride}

\FloatBarrier

The value of a signal or calculation specified by a logic or motion program or set by a switch.

\paragraph[RapidAxisFeedrateOverride]{RapidAxisFeedrateOverride \\ {\small Subtype of AxisFeedrateOverride}}\mbox{}
  \label{type:RapidAxisFeedrateOverride}

\FloatBarrier

The value of a signal or calculation issued to adjust the feedrate of a component or composition that is operating in a rapid positioning mode.

\FloatBarrier
\subsubsection[AxisInterlock]{AxisInterlock \\ {\small Subtype of Event}}
  \label{type:AxisInterlock}

\FloatBarrier

An indicator of the state of the axis lockout function when power has been removed and the axis is allowed to move freely.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of AxisInterlock}}
  \label{properties:AxisInterlock}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{AXIS_INTERLOCK} \\
\texttt{result} & \texttt{ActuatorStateEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[AxisState]{AxisState \\ {\small Subtype of Event}}
  \label{type:AxisState}

\FloatBarrier

An indicator of the controlled state of a {model:Linear} or {model:Rotary} component representing an axis.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of AxisState}}
  \label{properties:AxisState}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{AXIS_STATE} \\
\texttt{result} & \texttt{AxisStateEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Block]{Block \\ {\small Subtype of Event}}
  \label{type:Block}

\FloatBarrier

The line of code or command being executed by a {model:Controller} {term:Structural Element}.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Block}}
  \label{properties:Block}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{BLOCK} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[BlockCount]{BlockCount \\ {\small Subtype of Event}}
  \label{type:BlockCount}

\FloatBarrier

The total count of the number of blocks of program code that have been executed since execution started.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of BlockCount}}
  \label{properties:BlockCount}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{BLOCK_COUNT} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[ChuckInterlock]{ChuckInterlock \\ {\small Subtype of Event}}
  \label{type:ChuckInterlock}

\FloatBarrier

An indication of the state of an interlock function or control logic state intended to prevent the associated {model:CHUCK} component from being operated.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ChuckInterlock}}
  \label{properties:ChuckInterlock}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{CHUCK_INTERLOCK} \\
\texttt{result} & \texttt{ActuatorStateEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ManualUnclampChuckInterlock]{ManualUnclampChuckInterlock \\ {\small Subtype of ChuckInterlock}}\mbox{}
  \label{type:ManualUnclampChuckInterlock}

\FloatBarrier

An indication of the state of an operator controlled interlock that can inhibit the ability to initiate an unclamp action of an electronically controlled chuck.
 The {term:Valid Data Value} *MUST* be {model:ACTIVE} or {model:INACTIVE}. 
 When {model:MANUAL_UNCLAMP} is {model:ACTIVE}, it is expected that a chuck cannot be unclamped until {model:MANUAL_UNCLAMP} is set to {model:INACTIVE}. 

\FloatBarrier
\subsubsection[ChuckState]{ChuckState \\ {\small Subtype of Event}}
  \label{type:ChuckState}

\FloatBarrier

An indication of the operating state of a mechanism that holds a part or stock material during a manufacturing process. It may also represent a mechanism that holds any other mechanism in place within a piece of equipment.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ChuckState}}
  \label{properties:ChuckState}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{CHUCK_STATE} \\
\texttt{result} & \texttt{ChuckStateEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[CloseChuck]{CloseChuck \\ {\small Subtype of Event}}
  \label{type:CloseChuck}

\FloatBarrier

Service to close a chuck.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of CloseChuck}}
  \label{properties:CloseChuck}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{CLOSE_CHUCK} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[CloseDoor]{CloseDoor \\ {\small Subtype of Event}}
  \label{type:CloseDoor}

\FloatBarrier

Service to close a door.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of CloseDoor}}
  \label{properties:CloseDoor}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{CLOSE_DOOR} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Code]{Code \\ {\small Subtype of Event}}
  \label{type:Code}

\FloatBarrier

*DEPRECATED* in Version 1.1.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Code}}
  \label{properties:Code}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{CODE} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[CompositionState]{CompositionState \\ {\small Subtype of Event}}
  \label{type:CompositionState}

\FloatBarrier

An indication of the operating condition of a mechanism represented by a {model:Composition} type element.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of CompositionState}}
  \label{properties:CompositionState}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{COMPOSITION_STATE} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActionCompositionState]{ActionCompositionState \\ {\small Subtype of CompositionState}}\mbox{}
  \label{type:ActionCompositionState}

\FloatBarrier

An indication of the operating state of a mechanism represented by a {model:Composition} type component.
 The operating state indicates whether the {model:Composition} element is activated or disabled. 
 The {term:Valid Data Value} *MUST* be {model:ACTIVE} or {model:INACTIVE}.

\paragraph[LateralCompositionState]{LateralCompositionState \\ {\small Subtype of CompositionState}}\mbox{}
  \label{type:LateralCompositionState}

\FloatBarrier

An indication of the position of a mechanism that may move in a lateral direction.   The mechanism is represented by a {model:Composition} type component. 
 The position information indicates whether the {model:Composition} element is positioned to the right, to the left, or is in transition.  
 The {term:Valid Data Value} *MUST* be {model:RIGHT}, {model:LEFT}, or {model:TRANSITIONING}.

\paragraph[MotionCompositionState]{MotionCompositionState \\ {\small Subtype of CompositionState}}\mbox{}
  \label{type:MotionCompositionState}

\FloatBarrier

An indication of the open or closed state of a mechanism.   The mechanism is represented by a {model:Composition} type component. 
 The operating state indicates whether the state of the {model:Composition} element is open, closed, or unlatched.   
 The {term:Valid Data Value} *MUST* be {model:OPEN}, {model:UNLATCHED}, or {model:CLOSED}.

\paragraph[SwitchedCompositionState]{SwitchedCompositionState \\ {\small Subtype of CompositionState}}\mbox{}
  \label{type:SwitchedCompositionState}

\FloatBarrier

An indication of the activation state of a mechanism represented by a {model:Composition} type component.
 The activation state indicates whether the {model:Composition} element is activated or not.
 The {term:Valid Data Value} *MUST* be {model:ON} or {model:OFF}.

\paragraph[VerticalCompositionState]{VerticalCompositionState \\ {\small Subtype of CompositionState}}\mbox{}
  \label{type:VerticalCompositionState}

\FloatBarrier

An indication of the position of a mechanism that may move in a vertical direction. The mechanism is represented by a {model:Composition} type component. 
 The position information indicates whether the {model:Composition} element is positioned to the top, to the bottom, or is in transition.  
 The {term:Valid Data Value} *MUST* be {model:UP}, {model:DOWN}, or {model:TRANSITIONING}.

\FloatBarrier
\subsubsection[ControllerMode]{ControllerMode \\ {\small Subtype of Event}}
  \label{type:ControllerMode}

\FloatBarrier

The current operating mode of the {model:Controller} component.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ControllerMode}}
  \label{properties:ControllerMode}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{CONTROLLER_MODE} \\
\texttt{result} & \texttt{ControllerModeEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[ControllerModeOverride]{ControllerModeOverride \\ {\small Subtype of Event}}
  \label{type:ControllerModeOverride}

\FloatBarrier

A setting or operator selection that changes the behavior of a piece of equipment.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ControllerModeOverride}}
  \label{properties:ControllerModeOverride}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{CONTROLLER_MODE_OVERRIDE} \\
\texttt{result} & \texttt{ControllerModeOverrideEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[DryRunControllerModeOverride]{DryRunControllerModeOverride \\ {\small Subtype of ControllerModeOverride}}\mbox{}
  \label{type:DryRunControllerModeOverride}

\FloatBarrier

A setting or operator selection used to execute a test mode to confirm the execution of machine functions. 
 The {term:Valid Data Value} *MUST* be {model:ON} or {model:OFF}. 
 When {model:DRY_RUN} is {model:ON}, the equipment performs all of its normal functions, except no part or product is produced.  If the equipment has a spindle, spindle operation is suspended.

\paragraph[MachineAxisLockControllerModeOverride]{MachineAxisLockControllerModeOverride \\ {\small Subtype of ControllerModeOverride}}\mbox{}
  \label{type:MachineAxisLockControllerModeOverride}

\FloatBarrier

A setting or operator selection that changes the behavior of the controller on a piece of equipment. 
 The {term:Valid Data Value} *MUST* be {model:ON} or {model:OFF}. 
 When {model:MACHINE_AXIS_LOCK} is {model:ON}, program execution continues normally, but no equipment motion occurs 

\paragraph[OptionalStopControllerModeOverride]{OptionalStopControllerModeOverride \\ {\small Subtype of ControllerModeOverride}}\mbox{}
  \label{type:OptionalStopControllerModeOverride}

\FloatBarrier

A setting or operator selection that changes the behavior of the controller on a piece of equipment. 
 The {term:Valid Data Value} *MUST* be {model:ON} or {model:OFF}.
 The program execution is stopped after a specific program block is executed when {model:OPTIONAL_STOP} is {model:ON}.    
 In the case of a G-Code program, a program {model:BLOCK} containing a M01 code designates the command for an {model:OPTIONAL_STOP}. 
 {model:EXECUTION} *MUST* change to {model:OPTIONAL_STOP} after a program block specifying an optional stop is executed and the {model:OPTIONAL_STOP} selection is {model:ON}.

\paragraph[SingleBlockControllerModeOverride]{SingleBlockControllerModeOverride \\ {\small Subtype of ControllerModeOverride}}\mbox{}
  \label{type:SingleBlockControllerModeOverride}

\FloatBarrier

A setting or operator selection that changes the behavior of the controller on a piece of equipment. 
 The {term:Valid Data Value} *MUST* be {model:ON} or {model:OFF}.
 Program execution is paused after each {model:BLOCK} of code is executed when {model:SINGLE_BLOCK} is {model:ON}.   
 When {model:SINGLE_BLOCK} is {model:ON}, {model:EXECUTION} *MUST* change to {model:INTERRUPTED} after completion of each {model:BLOCK} of code. 

\paragraph[ToolChangeStopControllerModeOverride]{ToolChangeStopControllerModeOverride \\ {\small Subtype of ControllerModeOverride}}\mbox{}
  \label{type:ToolChangeStopControllerModeOverride}

\FloatBarrier

A setting or operator selection that changes the behavior of the controller on a piece of equipment. 
 The {term:Valid Data Value} *MUST* be {model:ON} or {model:OFF}. 
 Program execution is paused when a command is executed requesting a cutting tool to be changed. 
 {model:EXECUTION} *MUST* change to {model:INTERRUPTED} after completion of the command requesting a cutting tool to be changed and {model:TOOL_CHANGE_STOP} is {model:ON}.

\FloatBarrier
\subsubsection[CoupledAxes]{CoupledAxes \\ {\small Subtype of Event}}
  \label{type:CoupledAxes}

\FloatBarrier

Refers to the set of associated axes.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of CoupledAxes}}
  \label{properties:CoupledAxes}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{COUPLED_AXES} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[DateCode]{DateCode \\ {\small Subtype of Event}}
  \label{type:DateCode}

\FloatBarrier

The time and date code associated with a material or other physical item.
  
 {model:DATE_CODE} *MUST* be reported in ISO 8601 format.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of DateCode}}
  \label{properties:DateCode}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{DATE_CODE} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ExpirationDateCode]{ExpirationDateCode \\ {\small Subtype of DateCode}}\mbox{}
  \label{type:ExpirationDateCode}

\FloatBarrier

The time and date code relating to the expiration or end of useful life for a material or other physical item.

\paragraph[FirstUseDateCode]{FirstUseDateCode \\ {\small Subtype of DateCode}}\mbox{}
  \label{type:FirstUseDateCode}

\FloatBarrier

The time and date code relating the first use of a material or other physical item.

\paragraph[ManufactureDateCode]{ManufactureDateCode \\ {\small Subtype of DateCode}}\mbox{}
  \label{type:ManufactureDateCode}

\FloatBarrier

The time and date code relating to the production of a material or other physical item.

\FloatBarrier
\subsubsection[DeviceUuid]{DeviceUuid \\ {\small Subtype of Event}}
  \label{type:DeviceUuid}

\FloatBarrier

The identifier of another piece of equipment that is temporarily associated with a component of this piece of equipment to perform a particular function.
  
 The {term:Valid Data Value} *MUST* be a NMTOKEN XML type.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of DeviceUuid}}
  \label{properties:DeviceUuid}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{DEVICE_UUID} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Direction]{Direction \\ {\small Subtype of Event}}
  \label{type:Direction}

\FloatBarrier

The direction of motion.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Direction}}
  \label{properties:Direction}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{DIRECTION} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[LinearDirection]{LinearDirection \\ {\small Subtype of Direction}}\mbox{}
  \label{type:LinearDirection}

\FloatBarrier

The direction of motion of a linear motion.

\paragraph[RotaryDirection]{RotaryDirection \\ {\small Subtype of Direction}}\mbox{}
  \label{type:RotaryDirection}

\FloatBarrier

The rotational direction of a rotary motion using the right hand rule convention.
 The {term:Valid Data Value} *MUST* be {model:CLOCKWISE} or {model:COUNTER_CLOCKWISE}.

\FloatBarrier
\subsubsection[DoorState]{DoorState \\ {\small Subtype of Event}}
  \label{type:DoorState}

\FloatBarrier

The operational state of a {model:DOOR} type component or composition element.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of DoorState}}
  \label{properties:DoorState}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{DOOR_STATE} \\
\texttt{result} & \texttt{ChuckStateEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[EmergencyStop]{EmergencyStop \\ {\small Subtype of Event}}
  \label{type:EmergencyStop}

\FloatBarrier

The current state of the emergency stop signal for a piece of equipment, controller path, or any other component or subsystem of a piece of equipment.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of EmergencyStop}}
  \label{properties:EmergencyStop}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{EMERGENCY_STOP} \\
\texttt{result} & \texttt{EmergencyStopEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[EndOfBar]{EndOfBar \\ {\small Subtype of Event}}
  \label{type:EndOfBar}

\FloatBarrier

An indication of whether the end of a piece of bar stock being feed by a bar feeder has been reached.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of EndOfBar}}
  \label{properties:EndOfBar}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{END_OF_BAR} \\
\texttt{result} & \texttt{EndOfBarEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[AuxiliaryEndOfBar]{AuxiliaryEndOfBar \\ {\small Subtype of EndOfBar}}\mbox{}
  \label{type:AuxiliaryEndOfBar}

\FloatBarrier

When multiple locations on a piece of bar stock are referenced as the indication for the {model:END_OF_BAR}, the additional location(s) *MUST* be designated as {model:AUXILIARY} indication(s) for the {model:END_OF_BAR}.  

\paragraph[PrimaryEndOfBar]{PrimaryEndOfBar \\ {\small Subtype of EndOfBar}}\mbox{}
  \label{type:PrimaryEndOfBar}

\FloatBarrier

Specific applications *MAY* reference one or more locations on a piece of bar stock as the indication for the {model:END_OF_BAR}. The main or most important location *MUST* be designated as the {model:PRIMARY} indication for the {model:END_OF_BAR}.   
 If no {model:subType} is specified, {model:PRIMARY} *MUST* be the default {model:END_OF_BAR} indication.

\FloatBarrier
\subsubsection[EquipmentMode]{EquipmentMode \\ {\small Subtype of Event}}
  \label{type:EquipmentMode}

\FloatBarrier

An indication that a piece of equipment, or a sub-part of a piece of equipment, is performing specific types of activities.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of EquipmentMode}}
  \label{properties:EquipmentMode}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{EQUIPMENT_MODE} \\
\texttt{result} & \texttt{ControllerModeOverrideEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[DelayEquipmentMode]{DelayEquipmentMode \\ {\small Subtype of EquipmentMode}}\mbox{}
  \label{type:DelayEquipmentMode}

\FloatBarrier

A piece of equipment waiting for an event or an action to occur.

\paragraph[LoadedEquipmentMode]{LoadedEquipmentMode \\ {\small Subtype of EquipmentMode}}\mbox{}
  \label{type:LoadedEquipmentMode}

\FloatBarrier

Subparts of a piece of equipment are under load.

\paragraph[OperatingEquipmentMode]{OperatingEquipmentMode \\ {\small Subtype of EquipmentMode}}\mbox{}
  \label{type:OperatingEquipmentMode}

\FloatBarrier

A piece of equipment are powered or performing any activity.

\paragraph[PoweredEquipmentMode]{PoweredEquipmentMode \\ {\small Subtype of EquipmentMode}}\mbox{}
  \label{type:PoweredEquipmentMode}

\FloatBarrier

Primary  power is  applied  to the  piece  of  equipment and,  as  a minimum, the controller or logic portion of the piece of equipment is powered and functioning or components that are required to remain on are powered.

\paragraph[WorkingEquipmentMode]{WorkingEquipmentMode \\ {\small Subtype of EquipmentMode}}\mbox{}
  \label{type:WorkingEquipmentMode}

\FloatBarrier

A piece of equipment performing any activity, the equipment is active and performing a function under load or not.

\FloatBarrier
\subsubsection[Execution]{Execution \\ {\small Subtype of Event}}
  \label{type:Execution}

\FloatBarrier

The execution status of the {model:Controller}.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Execution}}
  \label{properties:Execution}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{EXECUTION} \\
\texttt{result} & \texttt{ExecutionEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[FunctionalMode]{FunctionalMode \\ {\small Subtype of Event}}
  \label{type:FunctionalMode}

\FloatBarrier

The current intended production status of the device or component.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of FunctionalMode}}
  \label{properties:FunctionalMode}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{FUNCTIONAL_MODE} \\
\texttt{result} & \texttt{FunctionalModeEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Hardness]{Hardness \\ {\small Subtype of Event}}
  \label{type:Hardness}

\FloatBarrier

The measurement of the hardness of a material.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Hardness}}
  \label{properties:Hardness}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{HARDNESS} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[BrinellHardness]{BrinellHardness \\ {\small Subtype of Hardness}}\mbox{}
  \label{type:BrinellHardness}

\FloatBarrier

A scale to measure the resistance to deformation of a surface.

\paragraph[LeebHardness]{LeebHardness \\ {\small Subtype of Hardness}}\mbox{}
  \label{type:LeebHardness}

\FloatBarrier

A scale to measure the elasticity of a surface.

\paragraph[MohsHardness]{MohsHardness \\ {\small Subtype of Hardness}}\mbox{}
  \label{type:MohsHardness}

\FloatBarrier

A scale to measure the resistance to scratching of a surface.

\paragraph[RockwellHardness]{RockwellHardness \\ {\small Subtype of Hardness}}\mbox{}
  \label{type:RockwellHardness}

\FloatBarrier

A scale to measure the resistance to deformation of a surface.

\paragraph[ShoreHardness]{ShoreHardness \\ {\small Subtype of Hardness}}\mbox{}
  \label{type:ShoreHardness}

\FloatBarrier

A scale to measure the resistance to deformation of a surface.

\paragraph[VickersHardness]{VickersHardness \\ {\small Subtype of Hardness}}\mbox{}
  \label{type:VickersHardness}

\FloatBarrier

A scale to measure the resistance to deformation of a surface.

\FloatBarrier
\subsubsection[InterfaceState]{InterfaceState \\ {\small Subtype of Event}}
  \label{type:InterfaceState}

\FloatBarrier

An indication of the operational state of an {model:Interface} component.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of InterfaceState}}
  \label{properties:InterfaceState}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{INTERFACE_STATE} \\
\texttt{result} & \texttt{InterfaceStateEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Line]{Line \\ {\small Subtype of Event}}
  \label{type:Line}

\FloatBarrier

*DEPRECATED* in Version 1.4.0.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Line}}
  \label{properties:Line}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{LINE} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[MaximumLine]{MaximumLine \\ {\small Subtype of Line}}\mbox{}
  \label{type:MaximumLine}

\FloatBarrier

Maximum value of a data entity or attribute.

\paragraph[MinimumLine]{MinimumLine \\ {\small Subtype of Line}}\mbox{}
  \label{type:MinimumLine}

\FloatBarrier

The minimum value of a data entity or attribute.

\FloatBarrier
\subsubsection[LineLabel]{LineLabel \\ {\small Subtype of Event}}
  \label{type:LineLabel}

\FloatBarrier

An optional identifier for a {model:BLOCK} of code in a {model:PROGRAM}.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of LineLabel}}
  \label{properties:LineLabel}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{LINE_LABEL} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[LineNumber]{LineNumber \\ {\small Subtype of Event}}
  \label{type:LineNumber}

\FloatBarrier

A reference to the position of a block of program code within a control program.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of LineNumber}}
  \label{properties:LineNumber}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{LINE_NUMBER} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[AbsoluteLineNumber]{AbsoluteLineNumber \\ {\small Subtype of LineNumber}}\mbox{}
  \label{type:AbsoluteLineNumber}

\FloatBarrier

The position of a block of program code relative to the beginning of the control program.

\paragraph[IncrementalLineNumber]{IncrementalLineNumber \\ {\small Subtype of LineNumber}}\mbox{}
  \label{type:IncrementalLineNumber}

\FloatBarrier

The position of a block of program code relative to the occurrence of the last {model:LINE_LABEL} encountered in the control program.

\FloatBarrier
\subsubsection[Material]{Material \\ {\small Subtype of Event}}
  \label{type:Material}

\FloatBarrier

The identifier of a material used or consumed in the manufacturing process.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Material}}
  \label{properties:Material}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{MATERIAL} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[MaterialChange]{MaterialChange \\ {\small Subtype of Event}}
  \label{type:MaterialChange}

\FloatBarrier

Service to change the type of material or product being loaded or fed to a piece of equipment.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of MaterialChange}}
  \label{properties:MaterialChange}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{MATERIAL_CHANGE} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[MaterialFeed]{MaterialFeed \\ {\small Subtype of Event}}
  \label{type:MaterialFeed}

\FloatBarrier

Service to advance material or feed product to a piece of equipment from a continuous or bulk source.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of MaterialFeed}}
  \label{properties:MaterialFeed}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{MATERIAL_FEED} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[MaterialLayer]{MaterialLayer \\ {\small Subtype of Event}}
  \label{type:MaterialLayer}

\FloatBarrier

Identifies the layers of material applied to a part or product as part of an additive manufacturing process.
  
 The {term:Valid Data Value} *MUST* be an integer.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of MaterialLayer}}
  \label{properties:MaterialLayer}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{MATERIAL_LAYER} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualMaterialLayer]{ActualMaterialLayer \\ {\small Subtype of MaterialLayer}}\mbox{}
  \label{type:ActualMaterialLayer}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[TargetMaterialLayer]{TargetMaterialLayer \\ {\small Subtype of MaterialLayer}}\mbox{}
  \label{type:TargetMaterialLayer}

\FloatBarrier

The desired measure or count for a data item value.

\FloatBarrier
\subsubsection[MaterialLoad]{MaterialLoad \\ {\small Subtype of Event}}
  \label{type:MaterialLoad}

\FloatBarrier

Service to load a piece of material or product.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of MaterialLoad}}
  \label{properties:MaterialLoad}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{MATERIAL_LOAD} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[MaterialRetract]{MaterialRetract \\ {\small Subtype of Event}}
  \label{type:MaterialRetract}

\FloatBarrier

Service to remove or retract material or product.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of MaterialRetract}}
  \label{properties:MaterialRetract}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{MATERIAL_RETRACT} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[MaterialUnload]{MaterialUnload \\ {\small Subtype of Event}}
  \label{type:MaterialUnload}

\FloatBarrier

Service to unload a piece of material or product.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of MaterialUnload}}
  \label{properties:MaterialUnload}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{MATERIAL_UNLOAD} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Message]{Message \\ {\small Subtype of Event}}
  \label{type:Message}

\FloatBarrier

Any text string of information to be transferred from a piece of equipment to a client software application.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Message}}
  \label{properties:Message}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{MESSAGE} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[OpenChuck]{OpenChuck \\ {\small Subtype of Event}}
  \label{type:OpenChuck}

\FloatBarrier

Service to open a chuck.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of OpenChuck}}
  \label{properties:OpenChuck}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{OPEN_CHUCK} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[OpenDoor]{OpenDoor \\ {\small Subtype of Event}}
  \label{type:OpenDoor}

\FloatBarrier

Service to open a door.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of OpenDoor}}
  \label{properties:OpenDoor}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{OPEN_DOOR} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[OperatorId]{OperatorId \\ {\small Subtype of Event}}
  \label{type:OperatorId}

\FloatBarrier

The identifier of the person currently responsible for operating the piece of equipment.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of OperatorId}}
  \label{properties:OperatorId}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{OPERATOR_ID} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[PalletId]{PalletId \\ {\small Subtype of Event}}
  \label{type:PalletId}

\FloatBarrier

The identifier for a pallet.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of PalletId}}
  \label{properties:PalletId}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{PALLET_ID} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[PartChange]{PartChange \\ {\small Subtype of Event}}
  \label{type:PartChange}

\FloatBarrier

Service to change the part or product associated with a piece of equipment to a different part or product.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of PartChange}}
  \label{properties:PartChange}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{PART_CHANGE} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[PartCount]{PartCount \\ {\small Subtype of Event}}
  \label{type:PartCount}

\FloatBarrier

The count of parts produced.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of PartCount}}
  \label{properties:PartCount}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{PART_COUNT} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[AllPartCount]{AllPartCount \\ {\small Subtype of PartCount}}\mbox{}
  \label{type:AllPartCount}

\FloatBarrier

The count of all the parts produced.  If the subtype is not given, this is the default.

\paragraph[BadPartCount]{BadPartCount \\ {\small Subtype of PartCount}}\mbox{}
  \label{type:BadPartCount}

\FloatBarrier

Indicates the count of incorrect parts produced.

\paragraph[GoodPartCount]{GoodPartCount \\ {\small Subtype of PartCount}}\mbox{}
  \label{type:GoodPartCount}

\FloatBarrier

Indicates the count of correct parts made.

\paragraph[RemainingPartCount]{RemainingPartCount \\ {\small Subtype of PartCount}}\mbox{}
  \label{type:RemainingPartCount}

\FloatBarrier

Remaining measure of an object or an action.

\paragraph[TargetPartCount]{TargetPartCount \\ {\small Subtype of PartCount}}\mbox{}
  \label{type:TargetPartCount}

\FloatBarrier

The desired measure or count for a data item value.

\FloatBarrier
\subsubsection[PartDetect]{PartDetect \\ {\small Subtype of Event}}
  \label{type:PartDetect}

\FloatBarrier

An indication designating whether a part or work piece has been detected or is present.
  
 The {term:Valid Data Value} *MUST* be {model:PRESENT} or {model:NOT_PRESENT}.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of PartDetect}}
  \label{properties:PartDetect}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{PART_DETECT} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[PartId]{PartId \\ {\small Subtype of Event}}
  \label{type:PartId}

\FloatBarrier

An identifier of a part in a manufacturing operation.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of PartId}}
  \label{properties:PartId}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{PART_ID} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[PartNumber]{PartNumber \\ {\small Subtype of Event}}
  \label{type:PartNumber}

\FloatBarrier

An identifier of a part or product moving through the manufacturing process. 
 The {term:Valid Data Value} *MUST* be a text string. 

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of PartNumber}}
  \label{properties:PartNumber}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{PART_NUMBER} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[PathFeedrateOverride]{PathFeedrateOverride \\ {\small Subtype of Event}}
  \label{type:PathFeedrateOverride}

\FloatBarrier

The value of a signal or calculation issued to adjust the feedrate for the axes associated with a {model:Path} component that may represent a single axis or the coordinated movement of multiple axes.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of PathFeedrateOverride}}
  \label{properties:PathFeedrateOverride}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{PATH_FEEDRATE_OVERRIDE} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[JogPathFeedrateOverride]{JogPathFeedrateOverride \\ {\small Subtype of PathFeedrateOverride}}\mbox{}
  \label{type:JogPathFeedrateOverride}

\FloatBarrier

The feedrate specified by a logic or motion program, by a pre-set value, or set by a switch as the feedrate for the {model:Axes}. 

\paragraph[ProgrammedPathFeedrateOverride]{ProgrammedPathFeedrateOverride \\ {\small Subtype of PathFeedrateOverride}}\mbox{}
  \label{type:ProgrammedPathFeedrateOverride}

\FloatBarrier

The value of a signal or calculation specified by a logic or motion program or set by a switch.

\paragraph[RapidPathFeedrateOverride]{RapidPathFeedrateOverride \\ {\small Subtype of PathFeedrateOverride}}\mbox{}
  \label{type:RapidPathFeedrateOverride}

\FloatBarrier

The value of a signal or calculation issued to adjust the feedrate of a component or composition that is operating in a rapid positioning mode.

\FloatBarrier
\subsubsection[PathMode]{PathMode \\ {\small Subtype of Event}}
  \label{type:PathMode}

\FloatBarrier

Describes the operational relationship between a {model:Path} {term:Structural Element} and another {model:Path} {term:Structural Element} for pieces of equipment comprised of multiple logical groupings of controlled axes or other logical operations.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of PathMode}}
  \label{properties:PathMode}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{PATH_MODE} \\
\texttt{result} & \texttt{PathModeEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[PowerState]{PowerState \\ {\small Subtype of Event}}
  \label{type:PowerState}

\FloatBarrier

The indication of the status of the source of energy for a {term:Structural Element} to allow it to perform its intended function or the state of an enabling signal providing permission for the {term:Structural Element} to perform its functions.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of PowerState}}
  \label{properties:PowerState}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{POWER_STATE} \\
\texttt{result} & \texttt{ControllerModeOverrideEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ControlPowerState]{ControlPowerState \\ {\small Subtype of PowerState}}\mbox{}
  \label{type:ControlPowerState}

\FloatBarrier

The state of the enabling signal or control logic that enables or disables the function or operation of the {term:Structural Element}.

\paragraph[LinePowerState]{LinePowerState \\ {\small Subtype of PowerState}}\mbox{}
  \label{type:LinePowerState}

\FloatBarrier

The state of the power source for the {term:Structural Element}.

\FloatBarrier
\subsubsection[PowerStatus]{PowerStatus \\ {\small Subtype of Event}}
  \label{type:PowerStatus}

\FloatBarrier

*DEPRECATED* in Version 1.1.0.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of PowerStatus}}
  \label{properties:PowerStatus}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{POWER_STATUS} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[ProcessTime]{ProcessTime \\ {\small Subtype of Event}}
  \label{type:ProcessTime}

\FloatBarrier

The time and date associated with an activity or event.
  
 {model:PROCESS_TIME} *MUST* be reported in ISO 8601 format.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ProcessTime}}
  \label{properties:ProcessTime}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{PROCESS_TIME} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[CompleteProcessTime]{CompleteProcessTime \\ {\small Subtype of ProcessTime}}\mbox{}
  \label{type:CompleteProcessTime}

\FloatBarrier

Completion of an action.

\paragraph[StartProcessTime]{StartProcessTime \\ {\small Subtype of ProcessTime}}\mbox{}
  \label{type:StartProcessTime}

\FloatBarrier

The time and date associated with the beginning of an activity or event.

\paragraph[TargetCompletionProcessTime]{TargetCompletionProcessTime \\ {\small Subtype of ProcessTime}}\mbox{}
  \label{type:TargetCompletionProcessTime}

\FloatBarrier

The projected time and date associated with the end or completion of an activity or event.

\FloatBarrier
\subsubsection[Program]{Program \\ {\small Subtype of Event}}
  \label{type:Program}

\FloatBarrier

The name of the logic or motion program being executed by the {model:Controller} component.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Program}}
  \label{properties:Program}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{PROGRAM} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[ProgramComment]{ProgramComment \\ {\small Subtype of Event}}
  \label{type:ProgramComment}

\FloatBarrier

A comment or non-executable statement in the control program.
 The {term:Valid Data Value} *MUST* be a text string.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ProgramComment}}
  \label{properties:ProgramComment}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{PROGRAM_COMMENT} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[ProgramEdit]{ProgramEdit \\ {\small Subtype of Event}}
  \label{type:ProgramEdit}

\FloatBarrier

An indication of the status of the {model:Controller} components program editing mode. 
 On many controls, a program can be edited while another program is currently being executed.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ProgramEdit}}
  \label{properties:ProgramEdit}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{PROGRAM_EDIT} \\
\texttt{result} & \texttt{ProgramEditEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[ProgramEditName]{ProgramEditName \\ {\small Subtype of Event}}
  \label{type:ProgramEditName}

\FloatBarrier

The name of the program being edited. 
 This is used in conjunction with {model:PROGRAM_EDIT} when in {model:ACTIVE} state. 
 The {term:Valid Data Value} *MUST* be a text string.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ProgramEditName}}
  \label{properties:ProgramEditName}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{PROGRAM_EDIT_NAME} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[ProgramHeader]{ProgramHeader \\ {\small Subtype of Event}}
  \label{type:ProgramHeader}

\FloatBarrier

The non-executable header section of the control program.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ProgramHeader}}
  \label{properties:ProgramHeader}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{PROGRAM_HEADER} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[ProgramLocation]{ProgramLocation \\ {\small Subtype of Event}}
  \label{type:ProgramLocation}

\FloatBarrier

The Uniform Resource Identifier (URI) for the source file associated with {model:PROGRAM}.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ProgramLocation}}
  \label{properties:ProgramLocation}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{PROGRAM_LOCATION} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActiveProgramLocation]{ActiveProgramLocation \\ {\small Subtype of ProgramLocation}}\mbox{}
  \label{type:ActiveProgramLocation}

\FloatBarrier

The value of the {term:Data Entity} that is engaging.

\paragraph[MainProgramLocation]{MainProgramLocation \\ {\small Subtype of ProgramLocation}}\mbox{}
  \label{type:MainProgramLocation}

\FloatBarrier

The identity of the primary logic or motion program currently being executed. It is the starting nest level in a call structure and may contain calls to sub programs.

\paragraph[ScheduleProgramLocation]{ScheduleProgramLocation \\ {\small Subtype of ProgramLocation}}\mbox{}
  \label{type:ScheduleProgramLocation}

\FloatBarrier

The identity of a control program that is used to specify the order of execution of other programs.

\FloatBarrier
\subsubsection[ProgramLocationType]{ProgramLocationType \\ {\small Subtype of Event}}
  \label{type:ProgramLocationType}

\FloatBarrier

Defines whether the logic or motion program defined by {model:PROGRAM} is being executed from the local memory of the controller or from an outside source.
  
 The {term:Valid Data Value} *MUST* be {model:LOCAL} or {model:EXTERNAL}.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ProgramLocationType}}
  \label{properties:ProgramLocationType}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{PROGRAM_LOCATION_TYPE} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActiveProgramLocationType]{ActiveProgramLocationType \\ {\small Subtype of ProgramLocationType}}\mbox{}
  \label{type:ActiveProgramLocationType}

\FloatBarrier

The value of the {term:Data Entity} that is engaging.

\paragraph[MainProgramLocationType]{MainProgramLocationType \\ {\small Subtype of ProgramLocationType}}\mbox{}
  \label{type:MainProgramLocationType}

\FloatBarrier

The identity of the primary logic or motion program currently being executed. It is the starting nest level in a call structure and may contain calls to sub programs.

\paragraph[ScheduleProgramLocationType]{ScheduleProgramLocationType \\ {\small Subtype of ProgramLocationType}}\mbox{}
  \label{type:ScheduleProgramLocationType}

\FloatBarrier

The identity of a control program that is used to specify the order of execution of other programs.

\FloatBarrier
\subsubsection[ProgramNestLevel]{ProgramNestLevel \\ {\small Subtype of Event}}
  \label{type:ProgramNestLevel}

\FloatBarrier

An indication of the nesting level within a control program that is associated with the code or instructions that is currently being executed.
  
 If an Initial Value is not defined, the nesting level associated with the highest or initial nesting level of the program *MUST* default to zero (0).
  
 The value reported for {model:PROGRAM_NEST_LEVEL} *MUST* be an integer.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ProgramNestLevel}}
  \label{properties:ProgramNestLevel}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{PROGRAM_NEST_LEVEL} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[RotaryMode]{RotaryMode \\ {\small Subtype of Event}}
  \label{type:RotaryMode}

\FloatBarrier

The current operating mode for a {model:Rotary} type axis.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of RotaryMode}}
  \label{properties:RotaryMode}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{ROTARY_MODE} \\
\texttt{result} & \texttt{RotaryModeEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[RotaryVelocityOverride]{RotaryVelocityOverride \\ {\small Subtype of Event}}
  \label{type:RotaryVelocityOverride}

\FloatBarrier

The value of a command issued to adjust the programmed velocity for a {model:Rotary} type axis.
 This command represents a percentage change to the velocity calculated by a logic or motion program or set by a switch for a {model:Rotary} type axis.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of RotaryVelocityOverride}}
  \label{properties:RotaryVelocityOverride}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{ROTARY_VELOCITY_OVERRIDE} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[SerialNumber]{SerialNumber \\ {\small Subtype of Event}}
  \label{type:SerialNumber}

\FloatBarrier

The serial number associated with a {model:Component}, {model:Asset}, or {model:Device}. The {term:Valid Data Value} *MUST* be a text string.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of SerialNumber}}
  \label{properties:SerialNumber}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{SERIAL_NUMBER} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[SpindleInterlock]{SpindleInterlock \\ {\small Subtype of Event}}
  \label{type:SpindleInterlock}

\FloatBarrier

An indication of the status of the spindle for a piece of equipment when power has been removed and it is free to rotate.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of SpindleInterlock}}
  \label{properties:SpindleInterlock}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{SPINDLE_INTERLOCK} \\
\texttt{result} & \texttt{ActuatorStateEnum} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[ToolAssetId]{ToolAssetId \\ {\small Subtype of Event}}
  \label{type:ToolAssetId}

\FloatBarrier

The identifier of an individual tool asset.The {term:Valid Data Value} *MUST* be a text string.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ToolAssetId}}
  \label{properties:ToolAssetId}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{TOOL_ASSET_ID} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[ToolGroup]{ToolGroup \\ {\small Subtype of Event}}
  \label{type:ToolGroup}

\FloatBarrier

An identifier for the tool group associated with a specific tool. Commonly used to designate spare tools.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ToolGroup}}
  \label{properties:ToolGroup}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{TOOL_GROUP} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[ToolId]{ToolId \\ {\small Subtype of Event}}
  \label{type:ToolId}

\FloatBarrier

*DEPRECATED* in Version 1.2.0.   See {model:TOOL_ASSET_ID}. *DEPRECATED:The identifier of the tool currently in use for a given {model:Path}.*

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ToolId}}
  \label{properties:ToolId}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{TOOL_ID} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[ToolNumber]{ToolNumber \\ {\small Subtype of Event}}
  \label{type:ToolNumber}

\FloatBarrier

The identifier assigned by the {model:Controller} component to a cutting tool when in use by a piece of equipment. 
 The {term:Valid Data Value} *MUST* be a text string.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ToolNumber}}
  \label{properties:ToolNumber}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{TOOL_NUMBER} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[ToolOffset]{ToolOffset \\ {\small Subtype of Event}}
  \label{type:ToolOffset}

\FloatBarrier

A reference to the tool offset variables applied to the active cutting tool associated with a {model:Path} in a {model:Controller} type component.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ToolOffset}}
  \label{properties:ToolOffset}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{TOOL_OFFSET} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[LengthToolOffset]{LengthToolOffset \\ {\small Subtype of ToolOffset}}\mbox{}
  \label{type:LengthToolOffset}

\FloatBarrier

A reference to a length type tool offset variable.

\paragraph[RadialToolOffset]{RadialToolOffset \\ {\small Subtype of ToolOffset}}\mbox{}
  \label{type:RadialToolOffset}

\FloatBarrier

A reference to a radial type tool offset variable.

\FloatBarrier
\subsubsection[User]{User \\ {\small Subtype of Event}}
  \label{type:User}

\FloatBarrier

The identifier of the person currently responsible for operating the piece of equipment.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of User}}
  \label{properties:User}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{USER} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[MaintenanceUser]{MaintenanceUser \\ {\small Subtype of User}}\mbox{}
  \label{type:MaintenanceUser}

\FloatBarrier

Action related to maintenance on the piece of equipment.

\paragraph[OperatorUser]{OperatorUser \\ {\small Subtype of User}}\mbox{}
  \label{type:OperatorUser}

\FloatBarrier

The identifier of the person currently responsible for operating the piece of equipment.

\paragraph[SetUpUser]{SetUpUser \\ {\small Subtype of User}}\mbox{}
  \label{type:SetUpUser}

\FloatBarrier

The identifier of the person currently responsible for preparing a piece of equipment for production or restoring the piece of equipment to a neutral state after production.

\FloatBarrier
\subsubsection[Variable]{Variable \\ {\small Subtype of Event}}
  \label{type:Variable}

\FloatBarrier

A data value whose meaning may change over time due to changes in the opertion of a piece of equipment or the process being executed on that piece of equipment.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Variable}}
  \label{properties:Variable}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{VARIABLE} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[WaitState]{WaitState \\ {\small Subtype of Event}}
  \label{type:WaitState}

\FloatBarrier

An indication of the reason that {model:EXECUTION} is reporting a value of {model:WAIT}.
  
 The {term:Valid Data Value} *MUST* be {model:POWERING_UP}, {model:POWERING_DOWN}, {model:PART_LOAD}, {model:PART_UNLOAD}, {model:TOOL_LOAD}, {model:TOOL_UNLOAD}, {model:MATERIAL_LOAD}, {model:MATERIAL_UNLOAD}, {model:SECONDARY_PROCESS}, {model:PAUSING}, or {model:RESUMING}.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of WaitState}}
  \label{properties:WaitState}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{WAIT_STATE} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Wire]{Wire \\ {\small Subtype of Event}}
  \label{type:Wire}

\FloatBarrier

A string like piece or filament of relatively rigid or flexible material provided in a variety of diameters.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Wire}}
  \label{properties:Wire}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{WIRE} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[WorkOffset]{WorkOffset \\ {\small Subtype of Event}}
  \label{type:WorkOffset}

\FloatBarrier

A reference to the offset variables for a work piece or part associated with a {model:Path} in a {model:Controller} type component.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of WorkOffset}}
  \label{properties:WorkOffset}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{WORK_OFFSET} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[WorkholdingId]{WorkholdingId \\ {\small Subtype of Event}}
  \label{type:WorkholdingId}

\FloatBarrier

The identifier for the current workholding or part clamp in use by a piece of equipment. 
 The {term:Valid Data Value} *MUST* be a text string.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of WorkholdingId}}
  \label{properties:WorkholdingId}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{WORKHOLDING_ID} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
