% Generated 2020-07-27 15:21:27 +0530
\subsection{References} \label{sec:References}

{block:References} {term:organizes} {block:Reference} elements.


\subsubsection{Reference}
  \label{sec:Reference}


{block:Reference} is a pointer to information that is associated with another {term:Structural Element} defined elsewhere for a piece of equipment.


\paragraph{Attributes of Reference}\mbox{}
\label{sec:Attributes of Reference}

\tbl{attributes of Reference} lists the attributes of \texttt{Reference}.

\begin{table}[ht]
\centering 
  \caption{Attributes of Reference}
  \label{table:attributes of Reference}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Attribute} & {Type} & {Multiplicity} \\
\tabucline[1.5pt]{}
\texttt{idRef} & \texttt{ID} & 1 \\
\texttt{name} & \texttt{string} & 0..1 \\
\end{tabu}
\end{table}
\FloatBarrier


Descriptions for attributes of \texttt{Reference}:

\begin{itemize}
\item \texttt{idRef} : A pointer to the {block:id} attribute of an element that contains the information to be associated with this XML element.
\item \texttt{name} : The name of an element or a piece of equipment.
\end{itemize}
\FloatBarrier

\subsubsection{DataItemRef}
  \label{sec:DataItemRef}


{block:DataItemRef} is a pointer to a {term:Data Entity} associated with another {term:Structural Element} defined for a piece of equipment.  {block:DataItemRef} allows the data associated with a data item defined in another {term:Structural Element} to be directly associated with this element.


\paragraph{Attributes of DataItemRef}\mbox{}
\label{sec:Attributes of DataItemRef}

\tbl{attributes of DataItemRef} lists the attributes of \texttt{DataItemRef}.

\begin{table}[ht]
\centering 
  \caption{Attributes of DataItemRef}
  \label{table:attributes of DataItemRef}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Attribute} & {Type} & {Multiplicity} \\
\tabucline[1.5pt]{}
\texttt{idRef} & \texttt{DataItem} & 1 \\
\end{tabu}
\end{table}
\FloatBarrier


Descriptions for attributes of \texttt{DataItemRef}:

\begin{itemize}
\item \texttt{idRef} : A pointer to the {property:id} attribute of the {block:DataItem} that contains the information to be associated with this element.
\end{itemize}
\FloatBarrier

\subsubsection{ComponentRef}
  \label{sec:ComponentRef}


{block:ComponentRef} is a pointer to all of the information associated with another {term:Structural Element} defined for a piece of equipment.  {block:ComponentRef} allows all of the information ({term:Lower Level} {block:Components} and all {term:Data Entities}) that is associated with the other {term:Structural Element} to be directly associated with this element.


\paragraph{Attributes of ComponentRef}\mbox{}
\label{sec:Attributes of ComponentRef}

\tbl{attributes of ComponentRef} lists the attributes of \texttt{ComponentRef}.

\begin{table}[ht]
\centering 
  \caption{Attributes of ComponentRef}
  \label{table:attributes of ComponentRef}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Attribute} & {Type} & {Multiplicity} \\
\tabucline[1.5pt]{}
\texttt{idRef} & \texttt{Component} & 1 \\
\end{tabu}
\end{table}
\FloatBarrier


Descriptions for attributes of \texttt{ComponentRef}:

\begin{itemize}
\item \texttt{idRef} : A pointer to the {property:id} attribute of the {block:Component} that contains the information to be associated with this element.
\end{itemize}
\FloatBarrier
