% Generated 2020-02-05 07:16:58 -0500
\subsection{SampleTypes} \label{model:SampleTypes}
\subsubsection[Acceleration]{Acceleration \\ {\small Subtype of Sample}}
  \label{type:Acceleration}

\FloatBarrier

The measurement of the rate of change of velocity.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Acceleration}}
  \label{properties:Acceleration}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{MILLIMETER/SECOND$^2$} \\
\texttt{type} & \texttt{ACCELERATION} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[AccumulatedTime]{AccumulatedTime \\ {\small Subtype of Sample}}
  \label{type:AccumulatedTime}

\FloatBarrier

The measurement of accumulated time for an activity or event.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of AccumulatedTime}}
  \label{properties:AccumulatedTime}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{SECOND} \\
\texttt{type} & \texttt{ACCUMULATED_TIME} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Amperage]{Amperage \\ {\small Subtype of Sample}}
  \label{type:Amperage}

\FloatBarrier

The measurement of electrical current.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Amperage}}
  \label{properties:Amperage}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{AMPERE} \\
\texttt{type} & \texttt{AMPERAGE} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualAmperage]{ActualAmperage \\ {\small Subtype of Amperage}}\mbox{}
  \label{type:ActualAmperage}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[AlternatingAmperage]{AlternatingAmperage \\ {\small Subtype of Amperage}}\mbox{}
  \label{type:AlternatingAmperage}

\FloatBarrier

The measurement of alternating voltage or current.   If not specified further in statistic, defaults to RMS voltage. 

\paragraph[DirectAmperage]{DirectAmperage \\ {\small Subtype of Amperage}}\mbox{}
  \label{type:DirectAmperage}

\FloatBarrier

The measurement of DC current or voltage.

\paragraph[TargetAmperage]{TargetAmperage \\ {\small Subtype of Amperage}}\mbox{}
  \label{type:TargetAmperage}

\FloatBarrier

The desired measure or count for a data item value.

\FloatBarrier
\subsubsection[Angle]{Angle \\ {\small Subtype of Sample}}
  \label{type:Angle}

\FloatBarrier

The measurement of angular position.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Angle}}
  \label{properties:Angle}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{DEGREE} \\
\texttt{type} & \texttt{ANGLE} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualAngle]{ActualAngle \\ {\small Subtype of Angle}}\mbox{}
  \label{type:ActualAngle}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[CommandedAngle]{CommandedAngle \\ {\small Subtype of Angle}}\mbox{}
  \label{type:CommandedAngle}

\FloatBarrier

A value specified by the {model:Controller} type component.

\FloatBarrier
\subsubsection[AngularAcceleration]{AngularAcceleration \\ {\small Subtype of Sample}}
  \label{type:AngularAcceleration}

\FloatBarrier

The measurement rate of change of angular velocity.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of AngularAcceleration}}
  \label{properties:AngularAcceleration}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{DEGREE/SECOND$^2$} \\
\texttt{type} & \texttt{ANGULAR_ACCELERATION} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[AngularVelocity]{AngularVelocity \\ {\small Subtype of Sample}}
  \label{type:AngularVelocity}

\FloatBarrier

The measurement of the rate of change of angular position.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of AngularVelocity}}
  \label{properties:AngularVelocity}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{DEGREE/SECOND} \\
\texttt{type} & \texttt{ANGULAR_VELOCITY} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[AxisFeedrate]{AxisFeedrate \\ {\small Subtype of Sample}}
  \label{type:AxisFeedrate}

\FloatBarrier

The measurement of the feedrate of a linear axis.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of AxisFeedrate}}
  \label{properties:AxisFeedrate}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{MILLIMETER/SECOND} \\
\texttt{type} & \texttt{AXIS_FEEDRATE} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualAxisFeedrate]{ActualAxisFeedrate \\ {\small Subtype of AxisFeedrate}}\mbox{}
  \label{type:ActualAxisFeedrate}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[CommandedAxisFeedrate]{CommandedAxisFeedrate \\ {\small Subtype of AxisFeedrate}}\mbox{}
  \label{type:CommandedAxisFeedrate}

\FloatBarrier

A value specified by the {model:Controller} type component.

\paragraph[JogAxisFeedrate]{JogAxisFeedrate \\ {\small Subtype of AxisFeedrate}}\mbox{}
  \label{type:JogAxisFeedrate}

\FloatBarrier

The feedrate specified by a logic or motion program, by a pre-set value, or set by a switch as the feedrate for the {model:Axes}. 

\paragraph[OverrideAxisFeedrate]{OverrideAxisFeedrate \\ {\small Subtype of AxisFeedrate}}\mbox{}
  \label{type:OverrideAxisFeedrate}

\FloatBarrier

The operators overridden value.

\paragraph[ProgrammedAxisFeedrate]{ProgrammedAxisFeedrate \\ {\small Subtype of AxisFeedrate}}\mbox{}
  \label{type:ProgrammedAxisFeedrate}

\FloatBarrier

The value of a signal or calculation specified by a logic or motion program or set by a switch.

\paragraph[RapidAxisFeedrate]{RapidAxisFeedrate \\ {\small Subtype of AxisFeedrate}}\mbox{}
  \label{type:RapidAxisFeedrate}

\FloatBarrier

The value of a signal or calculation issued to adjust the feedrate of a component or composition that is operating in a rapid positioning mode.

\FloatBarrier
\subsubsection[CapacityFluid]{CapacityFluid \\ {\small Subtype of Sample}}
  \label{type:CapacityFluid}

\FloatBarrier

The fluid capacity of an object or container.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of CapacityFluid}}
  \label{properties:CapacityFluid}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{MILLILITER} \\
\texttt{type} & \texttt{CAPACITY_FLUID} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[CapacitySpatial]{CapacitySpatial \\ {\small Subtype of Sample}}
  \label{type:CapacitySpatial}

\FloatBarrier

The geometric capacity of an object or container.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of CapacitySpatial}}
  \label{properties:CapacitySpatial}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{CUBIC_MILLIMETER} \\
\texttt{type} & \texttt{CAPACITY_SPATIAL} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[ClockTime]{ClockTime \\ {\small Subtype of Sample}}
  \label{type:ClockTime}

\FloatBarrier

The value provided by a timing device at a specific point in time.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ClockTime}}
  \label{properties:ClockTime}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{yyyy-mm-ddthh:mm:ss.ffff} \\
\texttt{type} & \texttt{CLOCK_TIME} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Concentration]{Concentration \\ {\small Subtype of Sample}}
  \label{type:Concentration}

\FloatBarrier

The measurement of the percentage of one component within a mixture of components

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Concentration}}
  \label{properties:Concentration}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{PERCENT} \\
\texttt{type} & \texttt{CONCENTRATION} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Conductivity]{Conductivity \\ {\small Subtype of Sample}}
  \label{type:Conductivity}

\FloatBarrier

The measurement of the ability of a material to conduct electricity.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Conductivity}}
  \label{properties:Conductivity}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{SIEMENS/METER} \\
\texttt{type} & \texttt{CONDUCTIVITY} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[CuttingSpeed]{CuttingSpeed \\ {\small Subtype of Sample}}
  \label{type:CuttingSpeed}

\FloatBarrier

The speed difference (relative velocity) between the cutting mechanism and the surface of the workpiece it is operating on.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of CuttingSpeed}}
  \label{properties:CuttingSpeed}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{MILLIMETER/SECOND} \\
\texttt{type} & \texttt{CUTTING_SPEED} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualCuttingSpeed]{ActualCuttingSpeed \\ {\small Subtype of CuttingSpeed}}\mbox{}
  \label{type:ActualCuttingSpeed}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[CommandedCuttingSpeed]{CommandedCuttingSpeed \\ {\small Subtype of CuttingSpeed}}\mbox{}
  \label{type:CommandedCuttingSpeed}

\FloatBarrier

A value specified by the {model:Controller} type component.

\paragraph[ProgrammedCuttingSpeed]{ProgrammedCuttingSpeed \\ {\small Subtype of CuttingSpeed}}\mbox{}
  \label{type:ProgrammedCuttingSpeed}

\FloatBarrier

The value of a signal or calculation specified by a logic or motion program or set by a switch.

\FloatBarrier
\subsubsection[Density]{Density \\ {\small Subtype of Sample}}
  \label{type:Density}

\FloatBarrier

The volumetric mass of a material per unit volume of that material.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Density}}
  \label{properties:Density}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{MILLIGRAM/CUBIC_MILLIMETER} \\
\texttt{type} & \texttt{DENSITY} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[DepositionAccelerationVolumetric]{DepositionAccelerationVolumetric \\ {\small Subtype of Sample}}
  \label{type:DepositionAccelerationVolumetric}

\FloatBarrier

The rate of change in spatial volume of material deposited in an additive manufacturing process.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of DepositionAccelerationVolumetric}}
  \label{properties:DepositionAccelerationVolumetric}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{CUBIC_MILLIMETER/SECOND$^2$} \\
\texttt{type} & \texttt{DEPOSITION_ACCELERATION_VOLUMETRIC} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualDepositionAccelerationVolumetric]{ActualDepositionAccelerationVolumetric \\ {\small Subtype of DepositionAccelerationVolumetric}}\mbox{}
  \label{type:ActualDepositionAccelerationVolumetric}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[CommandedDepositionAccelerationVolumetric]{CommandedDepositionAccelerationVolumetric \\ {\small Subtype of DepositionAccelerationVolumetric}}\mbox{}
  \label{type:CommandedDepositionAccelerationVolumetric}

\FloatBarrier

A value specified by the {model:Controller} type component.

\FloatBarrier
\subsubsection[DepositionDensity]{DepositionDensity \\ {\small Subtype of Sample}}
  \label{type:DepositionDensity}

\FloatBarrier

The density of the material deposited in an additive manufacturing process per unit of volume.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of DepositionDensity}}
  \label{properties:DepositionDensity}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{MILLIGRAM/CUBIC_MILLIMETER} \\
\texttt{type} & \texttt{DEPOSITION_DENSITY} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualDepositionDensity]{ActualDepositionDensity \\ {\small Subtype of DepositionDensity}}\mbox{}
  \label{type:ActualDepositionDensity}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[CommandedDepositionDensity]{CommandedDepositionDensity \\ {\small Subtype of DepositionDensity}}\mbox{}
  \label{type:CommandedDepositionDensity}

\FloatBarrier

A value specified by the {model:Controller} type component.

\FloatBarrier
\subsubsection[DepositionMass]{DepositionMass \\ {\small Subtype of Sample}}
  \label{type:DepositionMass}

\FloatBarrier

The mass of the material deposited in an additive manufacturing process.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of DepositionMass}}
  \label{properties:DepositionMass}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{MILLIGRAM} \\
\texttt{type} & \texttt{DEPOSITION_MASS} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualDepositionMass]{ActualDepositionMass \\ {\small Subtype of DepositionMass}}\mbox{}
  \label{type:ActualDepositionMass}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[CommandedDepositionMass]{CommandedDepositionMass \\ {\small Subtype of DepositionMass}}\mbox{}
  \label{type:CommandedDepositionMass}

\FloatBarrier

A value specified by the {model:Controller} type component.

\FloatBarrier
\subsubsection[DepositionRateVolumetric]{DepositionRateVolumetric \\ {\small Subtype of Sample}}
  \label{type:DepositionRateVolumetric}

\FloatBarrier

The rate at which a spatial volume of material is deposited in an additive manufacturing process.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of DepositionRateVolumetric}}
  \label{properties:DepositionRateVolumetric}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{CUBIC_MILLIMETER/SECOND} \\
\texttt{type} & \texttt{DEPOSITION_RATE_VOLUMETRIC} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualDepositionRateVolumetric]{ActualDepositionRateVolumetric \\ {\small Subtype of DepositionRateVolumetric}}\mbox{}
  \label{type:ActualDepositionRateVolumetric}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[CommandedDepositionRateVolumetric]{CommandedDepositionRateVolumetric \\ {\small Subtype of DepositionRateVolumetric}}\mbox{}
  \label{type:CommandedDepositionRateVolumetric}

\FloatBarrier

A value specified by the {model:Controller} type component.

\FloatBarrier
\subsubsection[DepositionVolume]{DepositionVolume \\ {\small Subtype of Sample}}
  \label{type:DepositionVolume}

\FloatBarrier

The spatial volume of material to be deposited in an additive manufacturing process.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of DepositionVolume}}
  \label{properties:DepositionVolume}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{CUBIC_MILLIMETER} \\
\texttt{type} & \texttt{DEPOSITION_VOLUME} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualDepositionVolume]{ActualDepositionVolume \\ {\small Subtype of DepositionVolume}}\mbox{}
  \label{type:ActualDepositionVolume}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[CommandedDepositionVolume]{CommandedDepositionVolume \\ {\small Subtype of DepositionVolume}}\mbox{}
  \label{type:CommandedDepositionVolume}

\FloatBarrier

A value specified by the {model:Controller} type component.

\FloatBarrier
\subsubsection[Displacement]{Displacement \\ {\small Subtype of Sample}}
  \label{type:Displacement}

\FloatBarrier

The measurement of the change in position of an object.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Displacement}}
  \label{properties:Displacement}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{MILLIMETER} \\
\texttt{type} & \texttt{DISPLACEMENT} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[ElectricalEnergy]{ElectricalEnergy \\ {\small Subtype of Sample}}
  \label{type:ElectricalEnergy}

\FloatBarrier

The measurement of electrical energy consumption by a component.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ElectricalEnergy}}
  \label{properties:ElectricalEnergy}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{WATT_SECOND} \\
\texttt{type} & \texttt{ELECTRICAL_ENERGY} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[EquipmentTimer]{EquipmentTimer \\ {\small Subtype of Sample}}
  \label{type:EquipmentTimer}

\FloatBarrier

The measurement of the amount of time a piece of equipment or a sub-part of a piece of equipment has performed specific activities.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of EquipmentTimer}}
  \label{properties:EquipmentTimer}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{SECOND} \\
\texttt{type} & \texttt{EQUIPMENT_TIMER} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[DelayEquipmentTimer]{DelayEquipmentTimer \\ {\small Subtype of EquipmentTimer}}\mbox{}
  \label{type:DelayEquipmentTimer}

\FloatBarrier

A piece of equipment waiting for an event or an action to occur.

\paragraph[LoadedEquipmentTimer]{LoadedEquipmentTimer \\ {\small Subtype of EquipmentTimer}}\mbox{}
  \label{type:LoadedEquipmentTimer}

\FloatBarrier

Subparts of a piece of equipment are under load.

\paragraph[OperatingEquipmentTimer]{OperatingEquipmentTimer \\ {\small Subtype of EquipmentTimer}}\mbox{}
  \label{type:OperatingEquipmentTimer}

\FloatBarrier

A piece of equipment are powered or performing any activity.

\paragraph[PoweredEquipmentTimer]{PoweredEquipmentTimer \\ {\small Subtype of EquipmentTimer}}\mbox{}
  \label{type:PoweredEquipmentTimer}

\FloatBarrier

Primary  power is  applied  to the  piece  of  equipment and,  as  a minimum, the controller or logic portion of the piece of equipment is powered and functioning or components that are required to remain on are powered.

\paragraph[WorkingEquipmentTimer]{WorkingEquipmentTimer \\ {\small Subtype of EquipmentTimer}}\mbox{}
  \label{type:WorkingEquipmentTimer}

\FloatBarrier

A piece of equipment performing any activity, the equipment is active and performing a function under load or not.

\FloatBarrier
\subsubsection[FillLevel]{FillLevel \\ {\small Subtype of Sample}}
  \label{type:FillLevel}

\FloatBarrier

The measurement of the amount of a substance remaining compared to the planned maximum amount of that substance.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of FillLevel}}
  \label{properties:FillLevel}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{PERCENT} \\
\texttt{type} & \texttt{FILL_LEVEL} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Flow]{Flow \\ {\small Subtype of Sample}}
  \label{type:Flow}

\FloatBarrier

The measurement of the rate of flow of a fluid.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Flow}}
  \label{properties:Flow}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{LITER/SECOND} \\
\texttt{type} & \texttt{FLOW} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Frequency]{Frequency \\ {\small Subtype of Sample}}
  \label{type:Frequency}

\FloatBarrier

The measurement of the number of occurrences of a repeating event per unit time.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Frequency}}
  \label{properties:Frequency}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{HERTZ} \\
\texttt{type} & \texttt{FREQUENCY} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[GlobalPosition]{GlobalPosition \\ {\small Subtype of Sample}}
  \label{type:GlobalPosition}

\FloatBarrier

*DEPRECATED* in Version 1.1

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of GlobalPosition}}
  \label{properties:GlobalPosition}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{GLOBAL_POSITION} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Length]{Length \\ {\small Subtype of Sample}}
  \label{type:Length}

\FloatBarrier

The measurement of the length of an object.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Length}}
  \label{properties:Length}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{MILLIMETER} \\
\texttt{type} & \texttt{LENGTH} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[RemainingLength]{RemainingLength \\ {\small Subtype of Length}}\mbox{}
  \label{type:RemainingLength}

\FloatBarrier

Remaining measure of an object or an action.

\paragraph[StandardLength]{StandardLength \\ {\small Subtype of Length}}\mbox{}
  \label{type:StandardLength}

\FloatBarrier

The standard or original length of an object.

\paragraph[UseableLength]{UseableLength \\ {\small Subtype of Length}}\mbox{}
  \label{type:UseableLength}

\FloatBarrier

The remaining useable length of an object.

\FloatBarrier
\subsubsection[Level]{Level \\ {\small Subtype of Sample}}
  \label{type:Level}

\FloatBarrier

*DEPRECATED* in Version 1.2.  See {model:FILL_LEVEL}

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Level}}
  \label{properties:Level}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{type} & \texttt{LEVEL} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[LinearForce]{LinearForce \\ {\small Subtype of Sample}}
  \label{type:LinearForce}

\FloatBarrier

The measurement of the push or pull introduced by an actuator or exerted on an object.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of LinearForce}}
  \label{properties:LinearForce}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{NEWTON} \\
\texttt{type} & \texttt{LINEAR_FORCE} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Load]{Load \\ {\small Subtype of Sample}}
  \label{type:Load}

\FloatBarrier

The measurement of the actual versus the standard rating of a piece of equipment.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Load}}
  \label{properties:Load}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{PERCENT} \\
\texttt{type} & \texttt{LOAD} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Mass]{Mass \\ {\small Subtype of Sample}}
  \label{type:Mass}

\FloatBarrier

The measurement of the mass of an object(s) or an amount of material.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Mass}}
  \label{properties:Mass}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{KILOGRAM} \\
\texttt{type} & \texttt{MASS} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[PH]{PH \\ {\small Subtype of Sample}}
  \label{type:PH}

\FloatBarrier

A measure of the acidity or alkalinity of a solution.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of PH}}
  \label{properties:PH}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{PH} \\
\texttt{type} & \texttt{PH} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[PathFeedrate]{PathFeedrate \\ {\small Subtype of Sample}}
  \label{type:PathFeedrate}

\FloatBarrier

The measurement of the feedrate for the axes, or a single axis, associated with a {model:Path} component-a vector.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of PathFeedrate}}
  \label{properties:PathFeedrate}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{MILLIMETER/SECOND} \\
\texttt{type} & \texttt{PATH_FEEDRATE} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualPathFeedrate]{ActualPathFeedrate \\ {\small Subtype of PathFeedrate}}\mbox{}
  \label{type:ActualPathFeedrate}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[CommandedPathFeedrate]{CommandedPathFeedrate \\ {\small Subtype of PathFeedrate}}\mbox{}
  \label{type:CommandedPathFeedrate}

\FloatBarrier

A value specified by the {model:Controller} type component.

\paragraph[JogPathFeedrate]{JogPathFeedrate \\ {\small Subtype of PathFeedrate}}\mbox{}
  \label{type:JogPathFeedrate}

\FloatBarrier

The feedrate specified by a logic or motion program, by a pre-set value, or set by a switch as the feedrate for the {model:Axes}. 

\paragraph[OverridePathFeedrate]{OverridePathFeedrate \\ {\small Subtype of PathFeedrate}}\mbox{}
  \label{type:OverridePathFeedrate}

\FloatBarrier

The operators overridden value.

\paragraph[ProgrammedPathFeedrate]{ProgrammedPathFeedrate \\ {\small Subtype of PathFeedrate}}\mbox{}
  \label{type:ProgrammedPathFeedrate}

\FloatBarrier

The value of a signal or calculation specified by a logic or motion program or set by a switch.

\paragraph[RapidPathFeedrate]{RapidPathFeedrate \\ {\small Subtype of PathFeedrate}}\mbox{}
  \label{type:RapidPathFeedrate}

\FloatBarrier

The value of a signal or calculation issued to adjust the feedrate of a component or composition that is operating in a rapid positioning mode.

\FloatBarrier
\subsubsection[PathFeedratePerRevolution]{PathFeedratePerRevolution \\ {\small Subtype of Sample}}
  \label{type:PathFeedratePerRevolution}

\FloatBarrier

The feedrate for the axes, or a single axis.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of PathFeedratePerRevolution}}
  \label{properties:PathFeedratePerRevolution}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{MILLIMETER/REVOLUTION} \\
\texttt{type} & \texttt{PATH_FEEDRATE_PER_REVOLUTION} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualPathFeedratePerRevolution]{ActualPathFeedratePerRevolution \\ {\small Subtype of PathFeedratePerRevolution}}\mbox{}
  \label{type:ActualPathFeedratePerRevolution}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[CommandedPathFeedratePerRevolution]{CommandedPathFeedratePerRevolution \\ {\small Subtype of PathFeedratePerRevolution}}\mbox{}
  \label{type:CommandedPathFeedratePerRevolution}

\FloatBarrier

A value specified by the {model:Controller} type component.

\paragraph[ProgrammedPathFeedratePerRevolution]{ProgrammedPathFeedratePerRevolution \\ {\small Subtype of PathFeedratePerRevolution}}\mbox{}
  \label{type:ProgrammedPathFeedratePerRevolution}

\FloatBarrier

The value of a signal or calculation specified by a logic or motion program or set by a switch.

\FloatBarrier
\subsubsection[PathPosition]{PathPosition \\ {\small Subtype of Sample}}
  \label{type:PathPosition}

\FloatBarrier

A measured or calculated position of a control point associated with a {model:Controller} element, or {model:Path} element if provided, of a piece of equipment.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of PathPosition}}
  \label{properties:PathPosition}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{MILLIMETER_3D} \\
\texttt{type} & \texttt{PATH_POSITION} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualPathPosition]{ActualPathPosition \\ {\small Subtype of PathPosition}}\mbox{}
  \label{type:ActualPathPosition}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[CommandedPathPosition]{CommandedPathPosition \\ {\small Subtype of PathPosition}}\mbox{}
  \label{type:CommandedPathPosition}

\FloatBarrier

A value specified by the {model:Controller} type component.

\paragraph[ProbePathPosition]{ProbePathPosition \\ {\small Subtype of PathPosition}}\mbox{}
  \label{type:ProbePathPosition}

\FloatBarrier

The position provided by a measurement probe.

\paragraph[TargetPathPosition]{TargetPathPosition \\ {\small Subtype of PathPosition}}\mbox{}
  \label{type:TargetPathPosition}

\FloatBarrier

The desired measure or count for a data item value.

\FloatBarrier
\subsubsection[Position]{Position \\ {\small Subtype of Sample}}
  \label{type:Position}

\FloatBarrier

A measured or calculated position of a {model:Component} element as reported by a piece of equipment.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Position}}
  \label{properties:Position}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{MILLIMETER} \\
\texttt{type} & \texttt{POSITION} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualPosition]{ActualPosition \\ {\small Subtype of Position}}\mbox{}
  \label{type:ActualPosition}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[CommandedPosition]{CommandedPosition \\ {\small Subtype of Position}}\mbox{}
  \label{type:CommandedPosition}

\FloatBarrier

A value specified by the {model:Controller} type component.

\paragraph[ProgrammedPosition]{ProgrammedPosition \\ {\small Subtype of Position}}\mbox{}
  \label{type:ProgrammedPosition}

\FloatBarrier

The value of a signal or calculation specified by a logic or motion program or set by a switch.

\paragraph[TargetPosition]{TargetPosition \\ {\small Subtype of Position}}\mbox{}
  \label{type:TargetPosition}

\FloatBarrier

The desired measure or count for a data item value.

\FloatBarrier
\subsubsection[PowerFactor]{PowerFactor \\ {\small Subtype of Sample}}
  \label{type:PowerFactor}

\FloatBarrier

The measurement of the ratio of real power flowing to a load to the apparent power in that AC circuit.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of PowerFactor}}
  \label{properties:PowerFactor}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{PERCENT} \\
\texttt{type} & \texttt{POWER_FACTOR} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Pressure]{Pressure \\ {\small Subtype of Sample}}
  \label{type:Pressure}

\FloatBarrier

The measurement of force per unit area exerted by a gas or liquid.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Pressure}}
  \label{properties:Pressure}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{PASCAL} \\
\texttt{type} & \texttt{PRESSURE} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[ProcessTimer]{ProcessTimer \\ {\small Subtype of Sample}}
  \label{type:ProcessTimer}

\FloatBarrier

The measurement of the amount of time a piece of equipment has performed different types of activities associated with the process being performed at that piece of equipment.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of ProcessTimer}}
  \label{properties:ProcessTimer}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{SECOND} \\
\texttt{type} & \texttt{PROCESS_TIMER} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[DelayProcessTimer]{DelayProcessTimer \\ {\small Subtype of ProcessTimer}}\mbox{}
  \label{type:DelayProcessTimer}

\FloatBarrier

A piece of equipment waiting for an event or an action to occur.

\paragraph[ProcessProcessTimer]{ProcessProcessTimer \\ {\small Subtype of ProcessTimer}}\mbox{}
  \label{type:ProcessProcessTimer}

\FloatBarrier

The measurement of the time from the beginning of production of a part or product on a piece of equipment until the time that production is complete for that part or product on that piece of equipment.  This includes the time that the piece of equipment is running, producing parts or products, or in the process of producing parts.

\FloatBarrier
\subsubsection[Resistance]{Resistance \\ {\small Subtype of Sample}}
  \label{type:Resistance}

\FloatBarrier

The measurement of the degree to which a substance opposes the passage of an electric current.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Resistance}}
  \label{properties:Resistance}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{OHM} \\
\texttt{type} & \texttt{RESISTANCE} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[RotaryVelocity]{RotaryVelocity \\ {\small Subtype of Sample}}
  \label{type:RotaryVelocity}

\FloatBarrier

The measurement of the rotational speed of a rotary axis.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of RotaryVelocity}}
  \label{properties:RotaryVelocity}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{REVOLUTION/MINUTE} \\
\texttt{type} & \texttt{ROTARY_VELOCITY} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualRotaryVelocity]{ActualRotaryVelocity \\ {\small Subtype of RotaryVelocity}}\mbox{}
  \label{type:ActualRotaryVelocity}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[CommandedRotaryVelocity]{CommandedRotaryVelocity \\ {\small Subtype of RotaryVelocity}}\mbox{}
  \label{type:CommandedRotaryVelocity}

\FloatBarrier

A value specified by the {model:Controller} type component.

\paragraph[OverrideRotaryVelocity]{OverrideRotaryVelocity \\ {\small Subtype of RotaryVelocity}}\mbox{}
  \label{type:OverrideRotaryVelocity}

\FloatBarrier

The operators overridden value.

\paragraph[ProgrammedRotaryVelocity]{ProgrammedRotaryVelocity \\ {\small Subtype of RotaryVelocity}}\mbox{}
  \label{type:ProgrammedRotaryVelocity}

\FloatBarrier

The value of a signal or calculation specified by a logic or motion program or set by a switch.

\FloatBarrier
\subsubsection[SoundLevel]{SoundLevel \\ {\small Subtype of Sample}}
  \label{type:SoundLevel}

\FloatBarrier

The measurement of a sound level or sound pressure level relative to atmospheric pressure.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of SoundLevel}}
  \label{properties:SoundLevel}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{DECIBEL} \\
\texttt{type} & \texttt{SOUND_LEVEL} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[AScaleSoundLevel]{AScaleSoundLevel \\ {\small Subtype of SoundLevel}}\mbox{}
  \label{type:AScaleSoundLevel}

\FloatBarrier

A Scale weighting factor.   This is the default weighting factor if no factor is specified

\paragraph[BScaleSoundLevel]{BScaleSoundLevel \\ {\small Subtype of SoundLevel}}\mbox{}
  \label{type:BScaleSoundLevel}

\FloatBarrier

B Scale weighting factor

\paragraph[CScaleSoundLevel]{CScaleSoundLevel \\ {\small Subtype of SoundLevel}}\mbox{}
  \label{type:CScaleSoundLevel}

\FloatBarrier

C Scale weighting factor

\paragraph[DScaleSoundLevel]{DScaleSoundLevel \\ {\small Subtype of SoundLevel}}\mbox{}
  \label{type:DScaleSoundLevel}

\FloatBarrier

D Scale weighting factor

\paragraph[NoScaleSoundLevel]{NoScaleSoundLevel \\ {\small Subtype of SoundLevel}}\mbox{}
  \label{type:NoScaleSoundLevel}

\FloatBarrier

No weighting factor on the frequency scale

\FloatBarrier
\subsubsection[SpindleSpeed]{SpindleSpeed \\ {\small Subtype of Sample}}
  \label{type:SpindleSpeed}

\FloatBarrier

*DEPRECATED* in Version 1.2.  Replaced by {model:ROTARY_VELOCITY}

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of SpindleSpeed}}
  \label{properties:SpindleSpeed}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{REVOLUTION/MINUTE} \\
\texttt{type} & \texttt{SPINDLE_SPEED} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualSpindleSpeed]{ActualSpindleSpeed \\ {\small Subtype of SpindleSpeed}}\mbox{}
  \label{type:ActualSpindleSpeed}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[CommandedSpindleSpeed]{CommandedSpindleSpeed \\ {\small Subtype of SpindleSpeed}}\mbox{}
  \label{type:CommandedSpindleSpeed}

\FloatBarrier

A value specified by the {model:Controller} type component.

\paragraph[OverrideSpindleSpeed]{OverrideSpindleSpeed \\ {\small Subtype of SpindleSpeed}}\mbox{}
  \label{type:OverrideSpindleSpeed}

\FloatBarrier

The operators overridden value.

\FloatBarrier
\subsubsection[Strain]{Strain \\ {\small Subtype of Sample}}
  \label{type:Strain}

\FloatBarrier

The measurement of the amount of deformation per unit length of an object when a load is applied.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Strain}}
  \label{properties:Strain}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{PERCENT} \\
\texttt{type} & \texttt{STRAIN} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Temperature]{Temperature \\ {\small Subtype of Sample}}
  \label{type:Temperature}

\FloatBarrier

The measurement of temperature.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Temperature}}
  \label{properties:Temperature}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{CELSIUS} \\
\texttt{type} & \texttt{TEMPERATURE} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Tension]{Tension \\ {\small Subtype of Sample}}
  \label{type:Tension}

\FloatBarrier

The measurement of a force that stretches or elongates an object.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Tension}}
  \label{properties:Tension}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{NEWTON} \\
\texttt{type} & \texttt{TENSION} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Tilt]{Tilt \\ {\small Subtype of Sample}}
  \label{type:Tilt}

\FloatBarrier

The measurement of angular displacement.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Tilt}}
  \label{properties:Tilt}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{MICRO_RADIAN} \\
\texttt{type} & \texttt{TILT} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Torque]{Torque \\ {\small Subtype of Sample}}
  \label{type:Torque}

\FloatBarrier

The measurement of the turning force exerted on an object or by an object.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Torque}}
  \label{properties:Torque}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{NEWTON_METER} \\
\texttt{type} & \texttt{TORQUE} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Velocity]{Velocity \\ {\small Subtype of Sample}}
  \label{type:Velocity}

\FloatBarrier

The measurement of the rate of change of position of a {model:Component}.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Velocity}}
  \label{properties:Velocity}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{MILLIMETER/SECOND} \\
\texttt{type} & \texttt{VELOCITY} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Viscosity]{Viscosity \\ {\small Subtype of Sample}}
  \label{type:Viscosity}

\FloatBarrier

The measurement of a fluids resistance to flow.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Viscosity}}
  \label{properties:Viscosity}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{PASCAL_SECOND} \\
\texttt{type} & \texttt{VISCOSITY} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[VoltAmpere]{VoltAmpere \\ {\small Subtype of Sample}}
  \label{type:VoltAmpere}

\FloatBarrier

The measurement of the apparent power in an electrical circuit, equal to the product of root-mean-square (RMS) voltage and RMS current (commonly referred to as VA).

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of VoltAmpere}}
  \label{properties:VoltAmpere}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{VOLT_AMPERE} \\
\texttt{type} & \texttt{VOLT_AMPERE} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[VoltAmpereReactive]{VoltAmpereReactive \\ {\small Subtype of Sample}}
  \label{type:VoltAmpereReactive}

\FloatBarrier

The measurement of reactive power in an AC electrical circuit (commonly referred to as VAR).

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of VoltAmpereReactive}}
  \label{properties:VoltAmpereReactive}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{VOLT_AMPERE_REACTIVE} \\
\texttt{type} & \texttt{VOLT_AMPERE_REACTIVE} \\
\end{tabu}
\end{table}
\FloatBarrier

\FloatBarrier
\subsubsection[Voltage]{Voltage \\ {\small Subtype of Sample}}
  \label{type:Voltage}

\FloatBarrier

The measurement of electrical potential between two points.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Voltage}}
  \label{properties:Voltage}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{VOLT} \\
\texttt{type} & \texttt{VOLTAGE} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualVoltage]{ActualVoltage \\ {\small Subtype of Voltage}}\mbox{}
  \label{type:ActualVoltage}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[AlternatingVoltage]{AlternatingVoltage \\ {\small Subtype of Voltage}}\mbox{}
  \label{type:AlternatingVoltage}

\FloatBarrier

The measurement of alternating voltage or current.   If not specified further in statistic, defaults to RMS voltage. 

\paragraph[DirectVoltage]{DirectVoltage \\ {\small Subtype of Voltage}}\mbox{}
  \label{type:DirectVoltage}

\FloatBarrier

The measurement of DC current or voltage.

\paragraph[TargetVoltage]{TargetVoltage \\ {\small Subtype of Voltage}}\mbox{}
  \label{type:TargetVoltage}

\FloatBarrier

The desired measure or count for a data item value.

\FloatBarrier
\subsubsection[VolumeFluid]{VolumeFluid \\ {\small Subtype of Sample}}
  \label{type:VolumeFluid}

\FloatBarrier

The fluid volume of an object or container.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of VolumeFluid}}
  \label{properties:VolumeFluid}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{MILLILITER} \\
\texttt{type} & \texttt{VOLUME_FLUID} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualVolumeFluid]{ActualVolumeFluid \\ {\small Subtype of VolumeFluid}}\mbox{}
  \label{type:ActualVolumeFluid}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[ConsumedVolumeFluid]{ConsumedVolumeFluid \\ {\small Subtype of VolumeFluid}}\mbox{}
  \label{type:ConsumedVolumeFluid}

\FloatBarrier

The amount of bulk material consumed from an object or container during a manufacturing process.

\FloatBarrier
\subsubsection[VolumeSpatial]{VolumeSpatial \\ {\small Subtype of Sample}}
  \label{type:VolumeSpatial}

\FloatBarrier

The geometric volume of an object or container.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of VolumeSpatial}}
  \label{properties:VolumeSpatial}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{CUBIC_MILLIMETER} \\
\texttt{type} & \texttt{VOLUME_SPATIAL} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualVolumeSpatial]{ActualVolumeSpatial \\ {\small Subtype of VolumeSpatial}}\mbox{}
  \label{type:ActualVolumeSpatial}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[ConsumedVolumeSpatial]{ConsumedVolumeSpatial \\ {\small Subtype of VolumeSpatial}}\mbox{}
  \label{type:ConsumedVolumeSpatial}

\FloatBarrier

The amount of bulk material consumed from an object or container during a manufacturing process.

\FloatBarrier
\subsubsection[Wattage]{Wattage \\ {\small Subtype of Sample}}
  \label{type:Wattage}

\FloatBarrier

The measurement of power flowing through or dissipated by an electrical circuit or piece of equipment.

\begin{table}[ht]
\centering 
  \caption{\texttt{Properties of Wattage}}
  \label{properties:Wattage}
\tabulinesep=3pt
\begin{tabu} to 6in {|l|l|} \everyrow{\hline}
\hline
\rowfont\bfseries {Properties} & {Value} \\
\tabucline[1.5pt]{}
\texttt{units} & \texttt{WATT} \\
\texttt{type} & \texttt{WATTAGE} \\
\end{tabu}
\end{table}
\FloatBarrier

\paragraph[ActualWattage]{ActualWattage \\ {\small Subtype of Wattage}}\mbox{}
  \label{type:ActualWattage}

\FloatBarrier

The measured value of the data item type given by a sensor or encoder.

\paragraph[TargetWattage]{TargetWattage \\ {\small Subtype of Wattage}}\mbox{}
  \label{type:TargetWattage}

\FloatBarrier

The desired measure or count for a data item value.

\FloatBarrier
