
\newglossaryentry{array3d}
{
    name={array3d},
	description={A three dimensional \gls{float} array.},
	plural={array3ds}
}

\newglossaryentry{arraystring}
{
    name={arraystring},
	description={An array of \gls{string}.},
	plural={arraystrings}
}

\newglossaryentry{asset buffer}
{
    name={asset buffer},
	description={A \gls{buffer} for \block{Assets}.},
	plural={asset buffers}
}

\newglossaryentry{Assets Information Model}
{
    name={Assets Information Model},
	description={An {{Information Model}} that provides semantic models for \glspl{MTConnect Asset}.},
	plural={Assets Information Models}
}

\newglossaryentry{Asset Request}
{
    name={Asset Request},
	description={An \gls{HTTP Request} to the \gls{Agent} regarding \glspl{MTConnect Asset}.},
	plural={Asset Requests}
}

\newglossaryentry{Asset Response Document}
{
    name={Asset Response Document},
	description={Used to describe an \gls{Information Model} that contains the rules and terminology that describe information that may be included in electronic documents representing \glspl{MTConnect Asset}.},
	plural={Asset Response Documents}
}

\newglossaryentry{boolean}
{
    name={boolean},
	description={Boolean data type.},
	plural={booleans}
}

\newglossaryentry{Data Model}
{
    name={Data Model},
	description={A data model organizes elements of data and standardizes how they relate to one another and to the properties of real-world entities.},
	plural={Data Models}
}

\newglossaryentry{datetime}
{
    name={datetime},
	description={DateTime (yyyy-mm-ddthh:mm:ss.ffff) data type.},
	plural={datetimes}
}

\newglossaryentry{float}
{
    name={float},
	description={Float data type.},
	plural={floats}
}

\newglossaryentry{Header}
{
    name={Header},
	description={Supplemental data usually placed at the beginning of a \gls{Document}.},
	plural={Headers}
}

\newglossaryentry{HTTP Body}
{
    name={HTTP Body},
	description={\gls{HTTP Body} is the data bytes transmitted in an HTTP transaction message immediately following the headers.},
	plural={HTTP Bodies}
}

\newglossaryentry{HTTP Header Field}
{
    name={HTTP Header Field},
	description={\gls{HTTP Header Field} are components of the header section of request and response messages in an HTTP transaction.},
	plural={HTTP Header Fields}
}

\newglossaryentry{HTTP Messaging}
{
    name={HTTP Messaging},
	description={\gls{HTTP Messaging} is an \gls{Interface} for information exchange functionality.},
	plural={HTTP Messagings}
}

\newglossaryentry{HTTP Request Method}
{
    name={HTTP Request Method},
	description={The Method  token indicates the method to be performed on the resource identified by the Request-URI. \textit{IETF RFC2616}},
	plural={HTTP Request Methods}
}

\newglossaryentry{HTTP Request URI}
{
    name={HTTP Request URI},
	description={The Request-URI is a Uniform Resource Identifier and identifies the resource upon which to apply the request. \textit{IETF RFC2616}},
	plural={HTTP Request URIs}
}

\newglossaryentry{HTTP Version}
{
    name={HTTP Version},
	description={Version of the HTTP protocol.},
	plural={HTTP Versions}
}

\newglossaryentry{integer}
{
    name={integer},
	description={Integer data type.},
	plural={integers}
}

\newglossaryentry{Lower Camel Case}
{
    name={Lower Camel Case},
	description={the first word is lowercase and the remaining words are capitalized and all spaces between words are removed.},
	plural={Lower Camel Cases}
}

\newglossaryentry{major}
{
    name={major},
	description={Identifier representing a consistent set of functionalities defined by the MTConnect Standard.},
	plural={majors}
}

\newglossaryentry{minor}
{
    name={minor},
	description={Identifier representing a specific set of functionalities defined by the MTConnect Standard.},
	plural={minors}
}

\newglossaryentry{MODBUS}
{
    name={MODBUS},
	description={Modbus is a communication protocol developed by Modicon systems and is a method used for transmitting information over serial lines between electronic devices.},
	plural={MODBUSs}
}

\newglossaryentry{MTConnect}
{
    name={MTConnect},
	description={The name of the standard.},
	plural={MTConnects}
}

\newglossaryentry{MTConnect Asset}
{
    name={MTConnect Asset},
	description={An \gls{MTConnect Asset} is an \gls{Asset} used by the manufacturing process to perform tasks.
\newline Note 1 to Entry: An \gls{MTConnect Asset} relies upon an \gls{MTConnect Device} to provide \glspl{observation} and information about itself and the \gls{MTConnect Device} revises the information to reflect changes to the \gls{MTConnect Asset} during their interaction. Examples of \glspl{MTConnect Asset} are Cutting Tools, Part Information, Manufacturing Processes, Fixtures, and Files.
\newline Note 2 to Entry: A singular \property{assetId}[Asset] uniquely identifies an \gls{MTConnect Asset} throughout its lifecycle and is used to track and relate the \gls{MTConnect Asset} to other \glspl{MTConnect Device} and entities.
\newline Note 3 to Entry: \glspl{MTConnect Asset} are temporally associated with a device and can be removed from the device without damage or alteration to its primary functions.},
	plural={MTConnect Assets}
}

\newglossaryentry{MTConnect Information Model}
{
    name={MTConnect Information Model},
	description={An \gls{Information Model} that defined the semantics of the MTConnect Standard.},
	plural={MTConnect Information Models}
}

\newglossaryentry{MTConnect Response Document}
{
    name={MTConnect Response Document},
	description={A \gls{Response Document} published by an \gls{MTConnect Agent}.},
	plural={MTConnect Response Documents}
}

\newglossaryentry{MTConnect Standard}
{
    name={MTConnect Standard},
	description={The name of the standard.},
	plural={MTConnect Standards}
}

\newglossaryentry{namespace}
{
    name={namespace},
	description={\gls{namespace} are used to organize code into logical groups.},
	plural={namespaces}
}

\newglossaryentry{occurrence}
{
    name={occurrence},
	description={Occurrence defines the number of times the content defined \textbf{MAY} be provided in the usage case specified.},
	plural={occurrences}
}

\newglossaryentry{ontology}
{
    name={ontology},
	description={logical structure of the terms used to describe a domain of knowledge, including both the definitions of the applicable terms and their relationships. \textit{ISO 20534:2018}},
	plural={ontologies}
}

\newglossaryentry{Part}
{
    name={Part},
	description={\gls{Part} is a discrete item that has both defined and measurable physical characteristics including mass, material and features and is created by applying one or more manufacturing process steps to a workpiece},
	plural={Parts}
}

\newglossaryentry{Pascal Case}
{
    name={Pascal Case},
	description={The first letter of each word is capitalized and the remaining letters are in lowercase. All space is removed between letters},
	plural={Pascal Cases}
}

\newglossaryentry{Physical Connection}
{
    name={Physical Connection},
	description={The network transmission technologies that physically interconnect an \gls{Agent}.},
	plural={Physical Connections}
}

\newglossaryentry{Probe Request}
{
    name={Probe Request},
	description={A \gls{Probe Request} is a \gls{Request} to an \gls{Agent} to produce an \gls{MTConnectDevices Response Document} containing the \gls{Devices Information Model}.},
	plural={Probe Requests}
}

\newglossaryentry{Publish}
{
    name={Publish},
	description={Sending of messages in a \gls{Publish/Subscribe} pattern.},
	plural={Publishs}
}

\newglossaryentry{Realization}
{
    name={Realization},
	description={Realization is a specialized abstraction relationship between two sets of model elements, one representing a specification (the supplier) and the other represents an implementation of the latter (the client). Realization can be used to model stepwise refinement, optimizations, transformations, templates, model synthesis, framework composition, etc.},
	plural={Realizations}
}

\newglossaryentry{Reference}
{
    name={Reference},
	description={\block{Reference} is a pointer to information that is associated with another \gls{Structural Element}.},
	plural={References}
}

\newglossaryentry{Response}
{
    name={Response},
	description={A response \gls{Interface} which responds to a \gls{Request}.},
	plural={Responses}
}

\newglossaryentry{revision}
{
    name={revision},
	description={A supplemental identifier representing only organizational or editorial changes to a \gls{minor} version document with no changes in the functionality described in that document.},
	plural={revisions}
}

\newglossaryentry{sensing element}
{
    name={sensing element},
	description={A mechanism that provides a signal or measured value.},
	plural={sensing elements}
}

\newglossaryentry{sensor element}
{
    name={sensor element},
	description={A \gls{sensor element} provides a signal or measured value.},
	plural={sensor elements}
}

\newglossaryentry{Sensor}
{
    name={Sensor},
	description={A \gls{sensing element} that responds to a physical stimulus and transmits a resulting signal.},
	plural={Sensors}
}

\newglossaryentry{sensor unit}
{
    name={sensor unit},
	description={An intelligent piece of equipment that manages the signals of one or more \glspl{sensing element} and provides the measured values.},
	plural={sensor units}
}

\newglossaryentry{string}
{
    name={string},
	description={String data type.},
	plural={strings}
}

\newglossaryentry{Subscribe}
{
    name={Subscribe},
	description={Receiving messages in a \gls{Publish/Subscribe} pattern.},
	plural={Subscribes}
}

\newglossaryentry{Time Series}
{
    name={Time Series},
	description={A \block{DataItem} representation of a contiguous vector of values supporting high frequency data rates.},
	plural={Time Series}
}

\newglossaryentry{Transport Protocol}
{
    name={Transport Protocol},
	description={A set of capabilities that provide the rules and procedures used to transport information between an \gls{Agent} and a client software application through a \gls{Physical Connection}.},
	plural={Transport Protocols}
}

\newglossaryentry{XML Declaration}
{
    name={XML Declaration},
	description={It is a processing instruction that identifies the document as being XML.},
	plural={XML Declarations}
}

\newglossaryentry{Abstract Element}
{
    name={Abstract Element},
	description={An element that defines a set of common characteristics that are shared by a group of elements.
An abstract element cannot appear in a document. In a specific implementation, an abstract element is replaced by a derived element that is itself not an abstract element. The characteristics for the derived element are inherited from the abstract element. 
},
	plural={Abstract Elements}
}

\newglossaryentry{Adapter}
{
    name={Adapter},
	description={An optional piece of hardware or software that transforms information provided by a piece of equipment into a form that can be received by an \gls{Agent}.},
	plural={Adapters}
}

\newglossaryentry{Agent}
{
    name={Agent},
	description={Software that collects data published from one or more piece(s) of equipment, organizes that data in a structured manner, and responds to requests for data from client software systems by providing a structured response in the form of a \gls{Response Document} that is constructed using the \gls{semantic data model} of a Standard. 
},
	plural={Agents}
}

\newglossaryentry{Application Programming Interface}
{
    name={Application Programming Interface},
	description={Collection of invocation methods and associated parameters used by one piece of software to request actions from another piece of software. \textit{ISO/IEC 18012-1:2004}
\newline Note 1 to entry: The API defined in the MTConnect Standard describes the methods for providing the \gls{Request/Response} Information Exchange between an \gls{Agent} and client software applications.},
	plural={Application Programming Interfaces}
}

\newglossaryentry{Archetype}
{
    name={Archetype},
	description={\block{Archetype} is an \gls{Asset} that provides the requirements, constraints, and common properties for a type of \gls{Asset}.},
	plural={Archetypes}
}

\newglossaryentry{Asset Document}
{
    name={Asset Document},
	description={An electronic document published by an \gls{Agent} in response to a \gls{Request} for information from a client software application relating to Assets.
},
	plural={Asset Documents}
}

\newglossaryentry{Attribute}
{
    name={Attribute},
	description={Used to provide additional information or properties for an \gls{Element}.
},
	plural={Attributes}
}

\newglossaryentry{Base Functional Structure}
{
    name={Base Functional Structure},
	description={A consistent set of functionalities defined by the MTConnect Standard. This functionality includes the protocol(s) used to communicate data to a client software application, the \gls{semantic data model} defining how that data is organized into \gls{Response Document}, and the encoding of those \gls{Response Document}.
},
	plural={Base Functional Structures}
}

\newglossaryentry{buffer}
{
    name={buffer},
	description={A section of an \gls{Agent} that provides storage for information published from pieces of equipment.},
	plural={buffers}
}

\newglossaryentry{CDATA}
{
    name={CDATA},
	description={\gls{CDATA} is used to describe a value (text or data) published as part of an XML element.},
	plural={CDATAs}
}

\newglossaryentry{Child Element}
{
    name={Child Element},
	description={An \gls{Element} of a data modeling structure that illustrates the relationship between itself and the higher-level \gls{Parent Element} within which it is contained.},
	plural={Child Elements}
}

\newglossaryentry{Client}
{
    name={Client},
	description={A \gls{Application} that sends \gls{Request} for information to an \gls{Agent}; e.g. software applications or a function that implements the \gls{Request} portion of an \gls{Interface} \gls{Interaction Model}.
},
	plural={Clients}
}

\newglossaryentry{Component}
{
    name={Component},
	description={A \gls{Structural Element} that represents a physical or logical part or subpart of a piece of equipment.},
	plural={Components}
}

\newglossaryentry{Composition}
{
    name={Composition},
	description={A \gls{Structural Element} that describes the lowest level basic structural or functional building block contained within a \block{Component} element.},
	plural={Compositions}
}

\newglossaryentry{Condition}
{
    name={Condition},
	description={An indicator of the ability of a piece of equipment or \gls{Component} to function to specification.},
	plural={Conditions}
}

\newglossaryentry{Controlled Vocabulary}
{
    name={Controlled Vocabulary},
	description={A restricted set of values that may be published as the \gls{Valid Data Value} for a \gls{Data Entity}.},
	plural={Controlled Vocabularies}
}

\newglossaryentry{Current Request}
{
    name={Current Request},
	description={A \gls{Current Request} is a \gls{Request} to an \gls{Agent} to produce an \gls{MTConnectStreams Response Document} containing the \gls{Observations Information Model} for a snapshot of the latest \glspl{observation} at the moment of the \gls{Request} or at a given \gls{sequence number}.},
	plural={Current Requests}
}

\newglossaryentry{Current}
{
    name={Current},
	description={occurring in or existing at the present time.},
	plural={Currents}
}

\newglossaryentry{data dictionary}
{
    name={data dictionary},
	description={Listing of standardized terms and definitions used in \gls{MTConnect Information Model}.},
	plural={data dictionaries}
}

\newglossaryentry{Data Entity}
{
    name={Data Entity},
	description={A primary data modeling element that represents all elements that either describe \glspl{Data Item} that may be reported by an \gls{Agent} or the \glspl{observation} that contain the actual data published by an \gls{Agent}.
},
	plural={Data Entities}
}

\newglossaryentry{Data Item}
{
    name={Data Item},
	description={Descriptive information or properties and characteristics associated with a piece of data.
},
	plural={Data Items}
}

\newglossaryentry{Data Set}
{
    name={Data Set},
	description={A set of \glspl{key-value pair} where each entry is uniquely identified by the \gls{key}.},
	plural={Data Sets}
}

\newglossaryentry{Data Source}
{
    name={Data Source},
	description={Any piece of equipment that can produce data that is published to an \gls{Agent}.
},
	plural={Data Sources}
}

\newglossaryentry{Data Streaming}
{
    name={Data Streaming},
	description={A method for an \gls{Agent} to provide a continuous stream of information in response to a single \gls{Request} from a \gls{Client}.},
	plural={Data Streamings}
}

\newglossaryentry{Deprecated}
{
    name={Deprecated},
	description={An indication that specific content in an \gls{MTConnect Document} is currently usable but is regarded as being obsolete or superseded. },
	plural={Deprecateds}
}

\newglossaryentry{Deprecation Warning}
{
    name={Deprecation Warning},
	description={An indication that specific content in an \gls{MTConnect Document} may be changed to \gls{Deprecated} in a future release of the standard.},
	plural={Deprecation Warnings}
}

\newglossaryentry{Devices Information Model}
{
    name={Devices Information Model},
	description={An \gls{Information Model} that describes the physical and logical configuration for a piece of equipment and the data that may be reported by that equipment. },
	plural={Devices Information Models}
}

\newglossaryentry{Device}
{
    name={Device},
	description={A \gls{Device} is a \gls{Component} representing a piece of equipment or a manufacturing system that produces observations about itself or publishes data. It organizes its parts as \glspl{Component}.},
	plural={Devices}
}

\newglossaryentry{Document}
{
    name={Document},
	description={A piece of written, printed, or electronic matter that provides information or evidence that serves as an official record.},
	plural={Documents}
}

\newglossaryentry{Document Body}
{
    name={Document Body},
	description={The portion of the content of an \gls{MTConnect Response Document} that is defined by the relative \gls{MTConnect Information Model}. The \gls{Document Body} contains the \glspl{Structural Element} and \glspl{Data Entity} reported in a \gls{Response Document}.
},
	plural={Document Bodies}
}

\newglossaryentry{Document Header}
{
    name={Document Header},
	description={The portion of the content of an \gls{MTConnect Response Document} that provides information from an \gls{Agent} defining version information, storage capacity, protocol, and other information associated with the management of the data stored in or retrieved from the \gls{Agent}.
},
	plural={Document Headers}
}

\newglossaryentry{Element}
{
    name={Element},
	description={A constituent part or a basic unit of identifiable and definable data.},
	plural={Elements}
}

\newglossaryentry{Element QName}
{
    name={Element QName},
	description={A \gls{QName} of an \gls{Element} in an XML document.},
	plural={Element QNames}
}

\newglossaryentry{Equipment}
{
    name={Equipment},
	description={Represents anything that can publish information and is used in the operations of a manufacturing facility shop floor.  Examples of equipment are machine tools, ovens, sensor units, workstations, software applications, and bar feeders.},
	plural={Equipments}
}

\newglossaryentry{Equipment Metadata}
{
    name={Equipment Metadata},
	description={\gls{Equipment Metadata} is {{Metadata}} that defines both the \glspl{Structural Element} that represent the physical and logical parts and sub-parts of each piece of equipment, the relationships between those parts and sub-parts, and the definitions of the \glspl{Data Entity} associated with that piece of equipment.},
	plural={Equipment Metadatas}
}

\newglossaryentry{Error Information Model}
{
    name={Error Information Model},
	description={An \gls{Information Model} that describes the \gls{Response Document} returned by an \gls{Agent} when it encounters an error while interpreting a \gls{Request} for information from a \gls{Client} or when an \gls{Agent} experiences an error while publishing the \gls{Response} to a \gls{Request} for information.},
	plural={Error Information Models}
}

\newglossaryentry{Event}
{
    name={Event},
	description={Something that happens or takes place.},
	plural={Events}
}

\newglossaryentry{Extensible}
{
    name={Extensible},
	description={The ability for an implementer to extend \gls{MTConnect Information Model} by adding content not currently addressed in the MTConnect Standard.
},
	plural={Extensibles}
}

\newglossaryentry{heartbeat}
{
    name={heartbeat},
	description={A function that indicates to a \gls{Client} that the communications connection to an \gls{Agent} is still viable during times when there is no new data available to report  often referred to as a "keep alive" message.},
	plural={heartbeats}
}

\newglossaryentry{Higher Level}
{
    name={Higher Level},
	description={A nested element that is above a lower level element.},
	plural={Higher Levels}
}

\newglossaryentry{HTTP}
{
    name={HTTP},
	description={Hyper-Text Transport Protocol. \textit{IETF RFC 7230}
},
	plural={HTTPs}
}

\newglossaryentry{HTTP Error Message}
{
    name={HTTP Error Message},
	description={A response provided by an \gls{Agent} indicating that an \gls{HTTP Request} is incorrectly formatted or identifies that the requested data is not available from the \gls{Agent}. },
	plural={HTTP Error Messages}
}

\newglossaryentry{HTTP Header}
{
    name={HTTP Header},
	description={The \gls{Header} of either an \gls{HTTP Request} from a \gls{Client} or an \gls{HTTP Response} from an \gls{Agent}.},
	plural={HTTP Headers}
}

\newglossaryentry{HTTP Method}
{
    name={HTTP Method},
	description={A portion of a command in an \gls{HTTP Request} that indicates the desired action to be performed on the identified resource; often referred to as verbs.
},
	plural={HTTP Methods}
}

\newglossaryentry{HTTP Request}
{
    name={HTTP Request},
	description={A request message from a client to a server includes, within the first line of that message, the method to be applied to the resource, the identifier of the resource, and the protocol version in use. \textit{IETF RFC2616}
Note 1 to entry: In MTConnect Standard, a request issued by a \gls{Client} to an \gls{Agent} requesting information defined in the \gls{HTTP Request Line}.},
	plural={HTTP Requests}
}

\newglossaryentry{HTTP Request Line}
{
    name={HTTP Request Line},
	description={The Request-Line begins with a method token, followed by the Request-URI and the protocol version, and ending with CRLF. A CRLF is allowed in the definition of TEXT only as part of a header field continuation.\textit{IETF RFC2616}
Note 1 to entry: the first line of an \gls{HTTP Request} describing a specific \gls{Response Document} to be published by an \gls{Agent}.},
	plural={HTTP Request Lines}
}

\newglossaryentry{HTTP Response}
{
    name={HTTP Response},
	description={After receiving and interpreting a request message, a server responds with an HTTP response message. \textit{IETF RFC2616}
Note 1 to entry: In MTConnect Standard, the information published from an \gls{Agent} in reply to an \gls{HTTP Request}. },
	plural={HTTP Responses}
}

\newglossaryentry{HTTP Server}
{
    name={HTTP Server},
	description={A server that accepts \gls{HTTP Request} from \gls{Client} and publishes \gls{HTTP Response} as a reply to those \gls{HTTP Request}.},
	plural={HTTP Servers}
}

\newglossaryentry{HTTP Status Code}
{
    name={HTTP Status Code},
	description={The Status-Code element is a 3-digit integer result code of the attempt to understand and satisfy the request.  \textit{IETF RFC2616}},
	plural={HTTP Status Codes}
}

\newglossaryentry{id}
{
    name={id},
	description={An identifier used to distinguish a piece of information.},
	plural={ids}
}

\newglossaryentry{Implementation}
{
    name={Implementation},
	description={A specific instantiation of the MTConnect Standard.},
	plural={Implementations}
}

\newglossaryentry{Information Model}
{
    name={Information Model},
	description={The rules, relationships, and terminology that are used to define how information is structured.},
	plural={Information Models}
}

\newglossaryentry{instance}
{
    name={instance},
	description={Describes a set of \gls{Streaming Data} in an \gls{Agent}.  Each time an \gls{Agent} is restarted with an empty \gls{buffer}, data placed in the \gls{buffer} represents a new \gls{instance} of the \gls{Agent}.},
	plural={instances}
}

\newglossaryentry{Interaction Model}
{
    name={Interaction Model},
	description={Defines how information is exchanged across an \gls{Interface} to enable interactions between independent systems.},
	plural={Interaction Models}
}

\newglossaryentry{Interface}
{
    name={Interface},
	description={The means by which communication is achieved between independent systems.},
	plural={Interfaces}
}

\newglossaryentry{key-value pair}
{
    name={key-value pair},
	description={An association between an identifier referred to as the \gls{key} and a value which taken together create a \gls{key-value pair}. When used in a set of \glspl{key-value pair} each \gls{key} is unique and will only have one value associated with it at any point in time.},
	plural={key-value pairs}
}

\newglossaryentry{Lower Level}
{
    name={Lower Level},
	description={A nested element that is below a higher level element.},
	plural={Lower Levels}
}

\newglossaryentry{Message}
{
    name={Message},
	description={A communication in writing, in speech, or by signals.},
	plural={Messages}
}

\newglossaryentry{Metadata}
{
    name={Metadata},
	description={Data that provides information about other data.
},
	plural={Metadatas}
}

\newglossaryentry{MTConnect Agent}
{
    name={MTConnect Agent},
	description={An \gls{Agent} for the \gls{MTConnect Information Model}.},
	plural={MTConnect Agents}
}

\newglossaryentry{MTConnect Document}
{
    name={MTConnect Document},
	description={Printed or electronic document(s) that represent a Part(s) of the MTConnect Standard.},
	plural={MTConnect Documents}
}

\newglossaryentry{MTConnect Request}
{
    name={MTConnect Request},
	description={A \gls{Request} for information issued from a \gls{Client} to an \gls{MTConnect Agent}.},
	plural={MTConnect Requests}
}

\newglossaryentry{MTConnect XML Document}
{
    name={MTConnect XML Document},
	description={An XML \gls{Response Document}.},
	plural={MTConnect XML Documents}
}

\newglossaryentry{MTConnectAssets Response Document}
{
    name={MTConnectAssets Response Document},
	description={A \gls{Response Document} published by an \gls{MTConnect Agent} in response to an \gls{Asset Request}.},
	plural={MTConnectAssets Response Documents}
}

\newglossaryentry{MTConnectDevices Response Document}
{
    name={MTConnectDevices Response Document},
	description={A \gls{Response Document} published by an \gls{MTConnect Agent} in response to a \gls{Probe Request}.},
	plural={MTConnectDevices Response Documents}
}

\newglossaryentry{MTConnectErrors Response Document}
{
    name={MTConnectErrors Response Document},
	description={A \gls{Response Document} published by an \gls{MTConnect Agent} whenever it encounters an error while interpreting an \gls{MTConnect Request}.},
	plural={MTConnectErrors Response Documents}
}

\newglossaryentry{MTConnectStreams Response Document}
{
    name={MTConnectStreams Response Document},
	description={A \gls{Response Document} published by an \gls{MTConnect Agent} in response to a \gls{Current Request} or a \gls{Current Request}.},
	plural={MTConnectStreams Response Documents}
}

\newglossaryentry{NMTOKEN}
{
    name={NMTOKEN},
	description={The data type for XML identifiers.},
	plural={NMTOKENs}
}

\newglossaryentry{parameter}
{
    name={parameter},
	description={A variable that must be given a value during the execution of a program or a communications command.},
	plural={parameters}
}

\newglossaryentry{Parent Element}
{
    name={Parent Element},
	description={An \gls{Element} of a data modeling structure that illustrates the relationship between itself and the lower-level \gls{Child Element}.},
	plural={Parent Elements}
}

\newglossaryentry{Persistence}
{
    name={Persistence},
	description={A method for retaining or restoring information.},
	plural={Persistences}
}

\newglossaryentry{Probe}
{
    name={Probe},
	description={An instrument commonly used for measuring the physical geometrical characteristics of an object.},
	plural={Probes}
}

\newglossaryentry{Protocol}
{
    name={Protocol},
	description={A set of rules that allow two or more entities to transmit information from one to the other.},
	plural={Protocols}
}

\newglossaryentry{Publish/Subscribe}
{
    name={Publish/Subscribe},
	description={An asynchronous communication method in which messages are exchanged between applications without knowing the identity of the sender or recipient.
Note 1 to entry: In the MTConnect Standard, a communications messaging pattern that may be used to publish \gls{Streaming Data} from an \gls{Agent}. },
	plural={Publish/Subscribes}
}

\newglossaryentry{HTTP Query}
{
    name={HTTP Query},
	description={A portion of a request for information that more precisely defines the specific information to be published in response to the request. },
	plural={HTTP Queries}
}

\newglossaryentry{Request}
{
    name={Request},
	description={A communications method where a \gls{Client} transmits a message to an \gls{Agent}.  That message instructs the \gls{Agent} to respond with specific information.},
	plural={Requests}
}

\newglossaryentry{Requester}
{
    name={Requester},
	description={An entity that initiates a \gls{Request} for information in a communications exchange.},
	plural={Requesters}
}

\newglossaryentry{Request/Response}
{
    name={Request/Response},
	description={A communications pattern that supports the transfer of information between an \gls{Agent} and a \gls{Client}. 
In a \gls{Request/Response} information exchange, a client software application requests specific information from an \gls{Agent}. An \gls{Agent} responds to the \gls{Request} by publishing a \gls{Response Document}. },
	plural={Request/Responses}
}

\newglossaryentry{reset}
{
    name={reset},
	description={A reset is associated with an occurrence of a \gls{Data Entity} indicated by the \\block{resetTriggered} attribute. When a reset occurs, the accumulated value or statistic are reverted back to their initial value. A \gls{Data Entity} with a \gls{Data Set} representation removes all \glspl{key-value pair}, setting the \gls{Data Set} to an empty set.},
	plural={resets}
}

\newglossaryentry{Responder}
{
    name={Responder},
	description={An entity that responds to a \gls{Request} for information in a communications exchange.},
	plural={Responders}
}

\newglossaryentry{Response Document}
{
    name={Response Document},
	description={An electronic document published by an \gls{MTConnect Agent} in response to a \gls{Probe Request}, \gls{Current Request}, \gls{Sample Request} or \gls{Asset Request}.},
	plural={Response Documents}
}

\newglossaryentry{REST}
{
    name={REST},
	description={REpresentational State Transfer:  A software architecture where a client and a server move through a series of state transitions based solely on the request from the client and the response from the server. 
},
	plural={RESTs}
}

\newglossaryentry{Root Element}
{
    name={Root Element},
	description={The first \gls{Structural Element} provided in a \gls{Response Document} encoded using XML. },
	plural={Root Elements}
}

\newglossaryentry{Sample Request}
{
    name={Sample Request},
	description={A \gls{Sample Request} is a \gls{Request} to an \gls{Agent} to produce an \gls{MTConnectStreams Response Document} containing the \gls{Observations Information Model} for a set of timestamped \glspl{observation} made by \glspl{Component}.},
	plural={Sample Requests}
}

\newglossaryentry{Sample}
{
    name={Sample},
	description={The collection of one or more pieces of information.  
},
	plural={Samples}
}

\newglossaryentry{schema}
{
    name={schema},
	description={The definition of the structure, rules, and vocabularies used to define the information published in an electronic document.},
	plural={schemas}
}

\newglossaryentry{semantic data model}
{
    name={semantic data model},
	description={A methodology for defining the structure and meaning for data in a specific logical way. It provides the rules for encoding electronic information such that it can be interpreted by a software system. },
	plural={semantic data models}
}

\newglossaryentry{sequence number}
{
    name={sequence number},
	description={The primary key identifier used to manage and locate a specific piece of \gls{Streaming Data} in an \gls{Agent}.},
	plural={sequence numbers}
}

\newglossaryentry{Standard}
{
    name={Standard},
	description={A document established by consensus that provides rules, guidelines, or characteristics for activities or their results.. \textit{ISO/IEC Guide 2:2004}},
	plural={Standards}
}

\newglossaryentry{Streaming Data}
{
    name={Streaming Data},
	description={The \glspl{observation} published by a piece of equipment defined by the \gls{Equipment Metadata}.},
	plural={Streaming Datas}
}

\newglossaryentry{Observations Information Model}
{
    name={Observations Information Model},
	description={An \gls{Information Model} that describes the \gls{Streaming Data} reported by a piece of equipment.},
	plural={Observations Information Models}
}

\newglossaryentry{Structural Element}
{
    name={Structural Element},
	description={An \gls{Element} that organizes information that represents the physical and logical parts and sub-parts of a piece of equipment.},
	plural={Structural Elements}
}

\newglossaryentry{subtype}
{
    name={subtype},
	description={A secondary or subordinate type of categorization or classification of information.},
	plural={subtypes}
}

\newglossaryentry{time stamp}
{
    name={time stamp},
	description={The best available estimate of the time that the \glspl{observation} was measured or determined.},
	plural={time stamps}
}

\newglossaryentry{Top Level}
{
    name={Top Level},
	description={\glspl{Structural Element} that represent the most significant physical or logical functions of a piece of equipment.},
	plural={Top Levels}
}

\newglossaryentry{type}
{
    name={type},
	description={A classification or categorization of information.},
	plural={types}
}

\newglossaryentry{URI}
{
    name={URI},
	description={Stands for Universal Resource Identifier. \textit{IETF RFC3986}
},
	plural={URIs}
}

\newglossaryentry{URN}
{
    name={URN},
	description={Stands for Uniform Resource Name. \textit{IETF RFC3986}
},
	plural={URNs}
}

\newglossaryentry{UTC/GMT}
{
    name={UTC/GMT},
	description={Stands for Coordinated Universal Time/Greenwich Mean Time.  
Note 1 to entry: The \gls{time stamp} for all information reported in an \gls{MTConnect Response Document} is provided in UTC/GMT format.},
	plural={UTC/GMTs}
}

\newglossaryentry{UUID}
{
    name={UUID},
	description={Stands for Universally Unique Identifier.  \textit{IETF RFC4122}},
	plural={UUIDs}
}

\newglossaryentry{Valid Data Value}
{
    name={Valid Data Value},
	description={One or more acceptable values or constrained values that can be reported for a \gls{Data Entity}.},
	plural={Valid Data Values}
}

\newglossaryentry{W3C}
{
    name={W3C},
	description={The World Wide Web Consortium (W3C) is an international community that develops open standards to ensure the long-term growth of the Web. See \textit{https://www.w3.org/}},
	plural={W3Cs}
}

\newglossaryentry{WARNING}
{
    name={WARNING},
	description={A statement or action that indicates a possible danger, problem, or other unexpected situation.
Note 1 to entry: Used to indicate that specific content in an \gls{MTConnect Document} may be changed in a future release of the standard.},
	plural={WARNINGs}
}

\newglossaryentry{XML}
{
    name={XML},
	description={Stands for eXtensible Markup Language. \textit{http://www.w3.org/XML}},
	plural={XMLs}
}

\newglossaryentry{XML Container}
{
    name={XML Container},
	description={An XML container is an XML element that \glspl{organize} other XML elements that are logically related to each other. },
	plural={XML Containers}
}

\newglossaryentry{XML Document}
{
    name={XML Document},
	description={A \gls{Document} encoded using XML.
},
	plural={XML Documents}
}

\newglossaryentry{XML Schema}
{
    name={XML Schema},
	description={A \gls{schema} defining a specific document encoded in XML.
},
	plural={XML Schemas}
}

\newglossaryentry{XPath}
{
    name={XPath},
	description={\gls{XPath} is a command structure that describes a way for a software system to locate information in an \gls{XML Document}. },
	plural={XPaths}
}

\newglossaryentry{Application}
{
    name={Application},
	description={Software or a program that is specific to the solution of an application problem.
\textit{ISO/IEC 20944-1:2013}},
	plural={Applications}
}

\newglossaryentry{observation}
{
    name={observation},
	description={The observed value of a property at a point in time.},
	plural={observations}
}

\newglossaryentry{Version}
{
    name={Version},
	description={unique identifier of the administered item. \textit{ISO/IEC 11179-:2015}},
	plural={Versions}
}

\newglossaryentry{observe}
{
    name={observe},
	description={The act of measuring or determining the value of a property at a point in time.},
	plural={observes}
}

\newglossaryentry{Asset}
{
    name={Asset},
	description={Item, thing or entity that has potential or actual value to an organization. \textit{ISO 55000:2014}
\newline Note 1 to entry: Value can be tangible or intangible, financial or non-financial, and includes consideration of risks and liabilities. It can be positive or negative at different stages of the asset life.
\newline Note 2 to entry: Physical assets usually refer to equipment, inventory and properties owned by the organization. Physical assets are the opposite of intangible assets, which are non-physical assets such as leases, brands, digital assets, use rights, licences, intellectual property rights, reputation or agreements.
\newline Note 3 to entry: A grouping of assets referred to as an asset system could also be considered as an asset.
},
	plural={Assets}
}

\newglossaryentry{engineering units}
{
    name={engineering units},
	description={A quantity, dimension, or magnitude used in engineering adopted as a standard in terms of which the magnitude of other quantities of the same kind can be expressed or calculated.},
	plural={engineering units}
}

\newglossaryentry{organizer}
{
    name={organizer},
	description={An element that contains and owns one or more elements.},
	plural={organizers}
}

\newglossaryentry{observable}
{
    name={observable},
	description={A quality, property, or characteristic that can be observed.},
	plural={observables}
}

\newglossaryentry{organize}
{
    name={organize},
	description={The act of containing and owning one or more elements.},
	plural={organizes}
}

\newglossaryentry{electric current}
{
    name={electric current},
	description={The rate of flow of electric charge.},
	plural={electric currents}
}

\newglossaryentry{QName}
{
    name={QName},
	description={A \gls{QName}, or qualified name, is the fully qualified name of an element, attribute, or identifier in an XML document.},
	plural={QNames}
}

\newglossaryentry{MTConnect Interface}
{
    name={MTConnect Interface},
	description={An \gls{Interaction Model} for interoperability between pieces of equipment.},
	plural={MTConnect Interfaces}
}

\newglossaryentry{HTTP Message}
{
    name={HTTP Message},
	description={HTTP messages consist of requests from client to server and responses from server to client. \textit{IETF:RFC-2616}
Note to Entry 1: In MTConnect Standard, it describes the information that is exchanged between an \gls{Agent} and a \gls{Client}.},
	plural={HTTP Messages}
}

\newglossaryentry{Table}
{
    name={Table},
	description={A two dimensional set of values given by a set of \glspl{key-value pair} \glspl{Table Entry}. },
	plural={Tables}
}

\newglossaryentry{key}
{
    name={key},
	description={A unique identifier in a \gls{key-value pair} association.},
	plural={keies}
}

\newglossaryentry{Table Entry}
{
    name={Table Entry},
	description={A subdivision of a \gls{Table} containing a set of \glspl{key-value pair} representing \glspl{Table Cell}.},
	plural={Table Entries}
}

\newglossaryentry{Table Cell}
{
    name={Table Cell},
	description={A subdivision of a \gls{Table Entry} representing a singular value.},
	plural={Table Cells}
}

\newglossaryentry{Condition State}
{
    name={Condition State},
	description={A \gls{Condition State} indicates the reported status of \gls{Condition} for a \gls{Structural Element}.},
	plural={Condition States}
}

\newglossaryentry{alarm limit}
{
    name={alarm limit},
	description={A limit used to trigger warning or alarm indicators.},
	plural={alarm limits}
}

\newglossaryentry{lower limit}
{
    name={lower limit},
	description={The lower conformance boundary for a variable.
Note to Entry: immediate concern or action may be required},
	plural={lower limits}
}

\newglossaryentry{control limit}
{
    name={control limit},
	description={A limit used to indicate whether a process variable is stable and in control.},
	plural={control limits}
}

\newglossaryentry{upper limit}
{
    name={upper limit},
	description={The upper conformance boundary for a variable.
Note to Entry: immediate concern or action may be required.},
	plural={upper limits}
}

\newglossaryentry{Spindle}
{
    name={Spindle},
	description={A mechanism that provides rotational capabilities to a piece of equipment. 
Note to Entry: Typically used for either work holding, materials or cutting tools.},
	plural={Spindles}
}

\newglossaryentry{Attachment}
{
    name={Attachment},
	description={the connection by which one thing is associated with another.},
	plural={Attachments}
}

\newglossaryentry{nominal}
{
    name={nominal},
	description={The ideal or desired value for a variable.},
	plural={nominals}
}

\newglossaryentry{Sensor Configuration}
{
    name={Sensor Configuration},
	description={Data in the \gls{MTConnectDevices Response Document} that provides the information required for maintenance and support of the \gls{sensor unit}.},
	plural={Sensor Configurations}
}

\newglossaryentry{upper warning}
{
    name={upper warning},
	description={The upper boundary indicating increased concern and supervision may be required.},
	plural={upper warnings}
}

\newglossaryentry{specification limit}
{
    name={specification limit},
	description={A limit defining a range of values designating acceptable performance for a variable.},
	plural={specification limits}
}

\newglossaryentry{lower warning}
{
    name={lower warning},
	description={he lower boundary indicating increased concern and supervision may be required.},
	plural={lower warnings}
}

\newglossaryentry{Sensor Data}
{
    name={Sensor Data},
	description={The value of a physical quantity reported by a measuring instrument or controller as an \gls{observation}.},
	plural={Sensor Datas}
}

\newglossaryentry{Force}
{
    name={Force},
	description={A push or pull on a mass which results in an acceleration.},
	plural={Forces}
}

\newglossaryentry{maximum}
{
    name={maximum},
	description={A numeric upper constraint.},
	plural={maximums}
}

\newglossaryentry{minimum}
{
    name={minimum},
	description={A numeric lower constraint.},
	plural={minimums}
}

\newglossaryentry{MTConnect Device}
{
    name={MTConnect Device},
	description={An \gls{MTConnect Device} is a piece of equipment or a manufacturing system that produces \glspl{observation} about itself and/or publishes data using the \gls{MTConnect Information Model}.},
	plural={MTConnect Devices}
}

\newglossaryentry{MTConnect Event}
{
    name={MTConnect Event},
	description={An \gls{MTConnect Event} is an \gls{observation} of either a state or discrete value of the \gls{Component}. \gls{Component} states \textbf{SHOULD} have a controlled vocabulary.},
	plural={MTConnect Events}
}

\newglossaryentry{URL}
{
    name={URL},
	description={Stands for Uniform Resource Locator. \textit{IETF RFC3986}
},
	plural={URLs}
}
