
\section{Observations Information Model}
\label{sec:Observations Information Model}
The {term:Streams Information Model} provides a representation of the data reported by a piece of equipment used for a manufacturing process, or used for any other purpose.  Additional descriptive information associated with the reported data is defined in the {block:MTConnectDevices} document, which is described in \citetitle{MTCPart2}.

Information defined in the {term:Streams Information Model} allows a software application to (1) determine the value for {term:Data Entities} returned from a piece of equipment and (2) interpret the data associated with those {term:Data Entities} with the same meaning, value, and context that it had at its original source.  To do this, the software application issues one of two HTTP requests to an {term:Agent} associated with a piece of equipment.  They are:


\begin{itemize}
\item {block:sample}:  Returns a designated number of time stamped {term:Data Entities} from an {term:Agent} associated with a piece of equipment; subject to any HTTP filtering associated with the request.  See {cite:Section 8.3.3} of \citetitle{MTCPart1} of the MTConnect Standard for details on the {block:sample} HTTP request.

\item {block:current}:  Returns a snapshot of either the most recent values or the values at a given sequence number for all {term:Data Entities} associated with a piece of equipment from an {term:Agent}; subject to any HTTP filtering associated with the request.  See {cite:Section 8.3.2} of \citetitle{MTCPart1} of the MTConnect Standard for details on the {block:current} HTTP request.
\end{itemize}

An {term:Agent} responds to either the {block:sample} or {block:current} HTTP request with an \linebreak{block:MTConnectStreams} {term:normalfont XML} document.  This document contains information describing {term:Data Entities} reported by an {term:Agent} associated with a piece of equipment.   A client software application may correlate the information provided in the {block:MTConnectStreams} {term:normalfont XML} document with the physical and logical structure for that piece of equipment defined in the {block:MTConnectDevices} document to form a clear and unambiguous understanding of the information provided.  (See details on the structure for a piece of equipment described in \citetitle{MTCPart2}).

The {block:MTConnectStreams} {term:normalfont XML} document is comprised of two sections: {block:Header} and {block:Streams}.

The {block:Header} section contains protocol related information as defined in {cite:Section 6.5} of \citetitle{MTCPart1} of the MTConnect Standard.

The {block:Streams} section of the {block:MTConnectStreams} document contains a \linebreak{block:DeviceStream} {term:normalfont XML} container for each piece of equipment represented in the document.  Each {block:DeviceStream} container is comprised of two primary types of {term:normalfont XML} elements – {term:Structural Elements} and {term:Data Entities}.  The contents of the {block:DeviceStream} container are described in detail in this document, \citetitle{MTCPart3} of the MTConnect Standard.

{term:Structural Elements} are defined for both the {block:MTConnectDevices} and the {block:MTConnectStreams} {term:normalfont XML} documents.  These {term:Structural Elements} are used to provide a logical organization of the information provided in each document.  While used for a similar purpose, the {term:Structural Elements} in the {block:MTConnectStreams} document are specifically designed to be distinctly different from those in the {block:MTConnectDevices} document:  

\begin{itemize}

\item {block:MTConnectDevices} document: {term:Structural Elements} organize information that represents the physical and logical parts and sub-parts of a piece of equipment.  (See \citetitle{MTCPart2}, Section 4 of the MTConnect Standard for more details on {term:Structural Elements} used in the {block:MTConnectDevices} document).  

\item {block:MTConnectStreams} document: {term:Structural Elements} provide the structure to organize the data returned from a piece of equipment and establishes the proper context for that data.  The {term:Structural Elements} specifically defined for use in the {block:MTConnectStreams} document are {block:DeviceStream} (see {ref:DeviceStream}) and {block:ComponentStream} (see {ref:ComponentStream}).   

{block:DeviceStream} and {block:ComponentStream} elements have a direct correlation to each of the {term:Structural Elements} defined in the {block:MTConnectDevices} document.
\end{itemize}

{term:Data Entities} that describe data reported by a piece of equipment are also defined for both the {block:MTConnectDevices} and the {block:MTConnectStreams} {term:normalfont XML} documents.  The {term:Data Entities} provided in both documents directly relate to each other.  However, {term:Data Entities} are used for different purposes in each document:

\begin{itemize}
\item {block:MTConnectDevices} document: {term:Data Entity} elements define the data that may be returned from a piece of equipment.  \citetitle{MTCPart2}, {cite:Sections 7 and 8} lists the possible {term:Data Entity} {term:normalfont XML} elements that can be returned in a {block:MTConnectDevices} document.  

\item {block:MTConnectStreams} document: {term:Data Entity} elements provide the data reported by a piece of equipment.  This data is organized in separate {block:ComponentStream} {term:normalfont XML} containers for each of the {term:Structural Elements} defined in the {block:MTConnectDevices} document associated with the data that is reported by a piece of equipment.  
\end{itemize}

Within each {block:ComponentStream} {term:normalfont XML} container in the {block:MTConnectStreams} document, {term:Data Entities} are organized into three types of {term:normalfont XML} container elements - \glspl{sample}, \glspl{event}, and \glspl{condition}.  (See {ref:Data Entities} and {ref:Listing of Data Entities} for more information on these elements.)


\section{Observations}
\label{sec:Observations}

\input model-sections/Observations.tex
\input model-sections/Representation.tex

\section{Observation Types}
\label{sec:Observation Types}
{term:observation} elements are represented by {block:Sample}, {block:Event} or {block:Condition} elements based upon the {property:category} and {property:type} attributes defined for the corresponding {block:DataItem}.
\input model-sections/ConditionTypes.tex
\input model-sections/EventTypes.tex
\input model-sections/SampleTypes.tex
