
\tabulinesep = 5pt
\begin{longtabu} to \textwidth {
    |l|X[3l]|X[0.75l]|}
\caption{Attributes for  Sample} \label{table:attributes-for-sample} \\

\hline
Attribute & Description & Occurrence \\
\hline
\endfirsthead

\hline
\multicolumn{3}{|c|}{Continuation of Table \ref{table:attributes-for-sample}}\\
\hline
Attribute & Description & Occurrence \\
\hline
\endhead
 
\gls{sequence} 
&
A number representing the sequential position of an occurrence of the
\gls{sample} in the data buffer of an \gls{agent}.
\newline \gls{sequence} is a required attribute.
\newline \gls{sequence} \MUST have a value represented as an unsigned 64-bit
value from 1 to $2^{64}-1$.
&
1 \\
\hline

\gls{subtype} 
&
The \gls{subtype} of the \gls{data entity}.
\newline \gls{subtype} is an optional attribute.
\newline \gls{subtype} \MUST match the \gls{subtype} attribute of the \gls{dataitem} element as defined in the \gls{mtconnectdevices} document that the
\gls{sample} element represents. 
&
0..1 \\
\hline

\gls{timestamp} 
&
The most accurate time available to a piece of equipment that represents
the point in time that the data reported for the \gls{sample} was measured.
\newline When the \gls{sample} element represents a \gls{dataitem} element defined in the \gls{mtconnectdevices} document with a \gls{representation} or
\gls{statistic} attribute, \gls{timestamp} \MUST represent the time that the
data collection was completed.
\newline \gls{timestamp} is a required attribute.
&
1 \\
\hline

\gls{name} 
&
The name of the \gls{sample} element.
\newline \gls{name}  is an optional attribute.
\newline \gls{name}  \MUST match the \gls{name}  attribute of the \gls{dataitem} element defined in the \gls{mtconnectdevices} document that the \gls{sample}
element represents.
\newline An \gls{nmtoken} XML type. 
&
0..1 \\
\hline

\gls{dataitemid} 
&
The unique identifier for the \gls{sample} element.
\newline \gls{dataitemid} is a required attribute.
\newline \gls{dataitemid} \MUST match the id attribute of the \gls{dataitem}
element defined in the \gls{mtconnectdevices} document that the
\gls{sample} element represents. 
&
1 \\
\hline

\gls{samplerate} 
&
The rate at which successive samples of the value of a data item are
recorded. \gls{samplerate} is expressed in terms of samples per second.
\newline \gls{samplerate} is an optional attribute.
\newline If the \gls{samplerate} is smaller than one, the number can be represented as a decimal type floating-point number. For example, a rate of 1 per 10 seconds would be 0.1
\newline \gls{samplerate} \MUST be provided when the representation
attribute of the \gls{dataitem} element defined in the
\gls{mtconnectdevices} document that this \gls{sample} element represents
is \gls{timeseries representation}.
\newline For \gls{dataitem} elements where the representation attribute
defined in the \gls{mtconnectdevices} document that this \gls{sample}
element represents is not \gls{timeseries representation}, it \MUST be assumed that the
data reported is represented by a single value and \gls{samplerate} \MUSTNOT be reported in the \gls{mtconnectstreams} document.
&
0..1 \\
\hline

\gls{statistic}
&
The type of statistical calculation defined by the \gls{statistic} attribute
of the \gls{dataitem} element defined in the \gls{mtconnectdevices}
document that this \gls{sample} element represents.
\newline \gls{statistic} is an optional attribute.
&
0..1 \\
\hline

\gls{duration}
&
The time-period over which the data was collected.
\newline \gls{duration} is an optional attribute.
\newline \gls{duration} \MUST be provided when the\gls{statistic} attribute of the \gls{dataitem} element is defined in the \gls{mtconnectdevices} document
that this \gls{sample} element represents.
&
0..1 \\
\hline

\gls{resettriggered}
&
For those \gls{dataitem} elements that report data that may be periodically
reset to an initial value, \gls{resettriggered} identifies when a reported
value has been reset and what has caused that reset to occur.
\newline \gls{resettriggered} is an optional attribute.
\newline \gls{resettriggered} \MUST only be provided for the specific
occurrence of a \gls{data entity} reported in the \gls{mtconnectstreams}
document when the reset occurred and \MUSTNOT be provided for any
other occurrence of the \gls{data entity} reported in a
\gls{mtconnectstreams} document.
&
0..1 \\
\hline

\gls{compositionid}
&
The identifier of the \gls{composition} element defined in the
\gls{mtconnectdevices} document associated with the data reported for
the \gls{sample} element.
\newline \gls{compositionid} is an optional attribute.
&
0..1 \\
\hline

\end{longtabu}