
\tabulinesep = 5pt
\begin{longtabu} to \textwidth {
    |l|X[3l]|X[0.75l]|}
\caption{Attributes for ComponentStream} \label{table:attributes-for-componentstream} \\

\hline
Attribute & Description & Occurrence \\
\hline
\endfirsthead

\hline
\multicolumn{3}{|c|}{Continuation of Table \ref{table:attributes-for-componentstream}}\\
\hline
Attribute & Description & Occurrence \\
\hline
\endhead
 
\gls{componentid} 
&
The identifier of the \gls{structural element} (\gls{device} element, \gls{top level} \gls{component} element, or \gls{lower level} \gls{component} element) as defined by the \gls{id} attribute of the corresponding \gls{structural element} in the \gls{mtconnectdevices} XML document.
\newline \gls{componentid} is a required attribute.
\newline The identifier \MUST be the same as that defined in the \gls{mtconnectdevices} document to associate the data reported in the \gls{componentstream} container with the \gls{structural element} identified
in the \gls{mtconnectdevices} document.
&
1 \\
\hline


\gls{name}
&
The name of the \gls{componentstream} element.
\newline \gls{name} is an optional attribute.
\newline If \gls{name} is not defined for a specific \gls{structural element} in the
\gls{mtconnectdevices} document, it \MUSTNOT be provided for the corresponding \gls{componentstream} element in the \gls{mtconnectstreams} document.
\newline If \gls{name} is defined for a specific \gls{structural element} in the \gls{mtconnectdevices} document, it \MAY be provided for the corresponding \gls{componentstream} element in the \gls{mtconnectstreams} document.
\newline If provided, the value reported for name \MUST be the same as the
value defined for the name attribute of the corresponding \gls{structural element} (\gls{device} element, \gls{top level} \gls{component} element, or \gls{lower level} \gls{component} element) defined in the \gls{mtconnectdevices} XML document.
\newline An \gls{nmtoken} XML type.
&
0..1 \\
\hline

\gls{nativename}
&
\gls{nativename} identifies the common name normally associated with
the \gls{componentstream} element.
\newline \gls{nativename} is an optional attribute.
\newline If \gls{nativename} is not defined for a specific \gls{structural element} in the \gls{mtconnectdevices} document, it \MUSTNOT be provided for the
corresponding \gls{componentstream} element in the
\gls{mtconnectstreams} document.
\newline If \gls{nativename} is defined for a specific \gls{structural element} in the
\gls{mtconnectdevices} document, it \MAY be provided for the
corresponding \gls{componentstream} element in the
\gls{mtconnectstreams} document.
\newline If provided, the value reported for \gls{nativename} \MUST be the same as the value defined for the \gls{nativename} attribute of the corresponding
\gls{structural element} (\gls{device} element, \gls{top level} \gls{component} element,
or \gls{lower level} \gls{component} element) defined in the
\gls{mtconnectdevices} XML document.
&
0..1 \\
\hline

\gls{component componentstream}
&
\gls{component componentstream} identifies the \gls{structural element} (\gls{device}, \gls{top level} \gls{component}, or \gls{lower level} \gls{component}) associated with the
\gls{componentstream} element.
\newline \gls{component componentstream} is a required attribute.
\newline The value reported for component \MUST be the same as the value
defined for the Element Name of the XML container representing the
corresponding \gls{structural element} (\gls{device} element, \gls{top level}
\gls{component} element, or \gls{lower level} \gls{component} element) defined in
the \gls{mtconnectdevices} XML document.
\newline Examples of \gls{component} are \gls{device}, \gls{axes}, \gls{controller},
\gls{linear}, \gls{electric} and \gls{loader}.
&
1 \\
\hline

\gls{uuid}
&
\gls{uuid} of the \gls{componentstream} element.
\newline \gls{uuid} is an optional attribute.
\newline If \gls{uuid} is not defined for a specific \gls{structural element} in the
\gls{mtconnectdevices} document, it \MUSTNOT be provided for the
corresponding \gls{componentstream} element in the
\gls{mtconnectstreams} document.
\newline If \gls{uuid} is defined for a specific \gls{structural element} in the
\gls{mtconnectdevices} document, it \MAY be provided for the
corresponding \gls{componentstream} element in the
\gls{mtconnectstreams} document, but it is not required.
\newline If provided, the value reported for \gls{uuid} \MUST be the same as the
value defined for the \gls{uuid} attribute of the corresponding \gls{structural element} (\gls{device} element, \gls{top level} \gls{component} element, or \gls{lower level} \gls{component} element) defined in the \gls{mtconnectdevices}
XML document.
&
0..1 \\
\hline


\end{longtabu}