
\tabulinesep = 5pt
\begin{longtabu} to \textwidth {
    |l|X[3l]|X[0.75l]|}
\caption{Attributes for Condition} \label{table:attributes-for-condition} \\

\hline
Attribute & Description & Occurrence \\
\hline
\endfirsthead

\hline
\multicolumn{3}{|c|}{Continuation of Table \ref{table:attributes-for-condition}}\\
\hline
Attribute & Description & Occurrence \\
\hline
\endhead
 
\gls{sequence} 
&
A number representing the sequential position of an occurrence of the
\gls{condition} in the data buffer of an MTConnect Agent.
\newline \gls{sequence} is a required attribute.
\newline \gls{sequence} \MUST have a value represented as an unsigned 64-bit value from 1 to $2^{64}-1$.
&
1 \\
\hline

\gls{timestamp} 
&
The most accurate time available to a piece of equipment that represents the point in time that the data reported for the \gls{condition} was measured.
\newline \gls{timestamp} is a required attribute.
&
1 \\
\hline

\gls{name} 
&
The name of the \gls{condition} element.
\newline \gls{name}  is an optional attribute.
\newline \gls{name}  \MUST match the \gls{name}  attribute of the \gls{dataitem} element defined in the \gls{mtconnectdevices} document that the \gls{condition}
element represents.
\newline An \gls{nmtoken} XML type. 
&
0..1 \\
\hline

\gls{dataitemid} 
&
The unique identifier for the\gls{condition} element.
\newline \gls{dataitemid} is a required attribute.
\newline \gls{dataitemid} \MUST match the id attribute of the \gls{dataitem}
element defined in the \gls{mtconnectdevices} document that the
\gls{condition} element represents. 
&
1 \\
\hline

\gls{type} 
&
An identifier of the \gls{type} of fault represented by the \gls{condition} element.
\newline \gls{type} is a required attribute.
\newline \gls{type} \MUST match the \gls{type} attribute of the \gls{dataitem} element defined in the \gls{mtconnectdevices} document that this \gls{condition} element represents. 
&
1 \\
\hline

\gls{nativecode}
&
The native code (usually an alpha-numeric value) generated by the
controller of a piece of equipment providing a reference identifier for a \gls{condition}.
\newline \gls{nativecode} is an optional attribute.
\newline This is the same information an operator or maintenance personnel may see as a reference code designating a specific fault code provided by the piece of equipment. 
&
0..1 \\
\hline

\gls{nativeseverity}
&
If the piece of equipment designates a severity level to a fault,
\gls{nativeseverity} reports that severity information to a client
software application.
\newline \gls{nativeseverity} is an optional attribute.
&
0..1 \\
\hline

\gls{qualifier}
&
\gls{qualifier} provides additional information regarding a \gls{fault state} associated with the measured value of a process variable.
\newline \gls{qualifier} is an optional attribute.
\newline \gls{qualifier} defines whether the \gls{fault state} represented by the \gls{condition} indicates a measured value that is above or below an expected value of a process variable.
\newline If the \gls{fault state} represents a measured value that is greater than the expected value for the process variable, \gls{qualifier} \MUST report a value of \gls{high}.
\newline If the \gls{fault state} represents a measured value that is less than the expected value for the process variable, \gls{qualifier} \MUST report a value of \gls{low}. 
&
0..1 \\
\hline

\gls{statistic}
&
\gls{statistic} provides additional information describing the meaning of the \gls{condition} element.
\newline \gls{statistic} is an optional attribute.
\newline \gls{statistic} \MUST match the \gls{statistic} attribute of the \gls{dataitem} element defined in the \gls{mtconnectdevices} document that this \gls{condition} element represents. 
&
0..1 \\
\hline

\gls{subtype} 
&
\gls{subtype} provides additional information describing the meaning of the \gls{condition} element.
\newline \gls{subtype} is an optional attribute.
\newline \gls{subtype} \MUST match the \gls{subtype} attribute of the \gls{dataitem} element defined in the \gls{mtconnectdevices} document that this \gls{condition} element represents. 
&
0..1 \\
\hline

\gls{compositionid}
&
The identifier of the \gls{composition} element defined in the
\gls{mtconnectdevices} document associated with the data reported for the \gls{condition} element.
\newline \gls{compositionid} is an optional attribute.
&
0..1 \\
\hline

\gls{xs:lang} 
&
An optional attribute that specifies the language of the \gls{cdata} returned for the \gls{condition}.
\newline Refer to IETF RFC 4646 (http://www.ietf.org/rfc/rfc4646.txt) or successor for a full definition of the values for this attribute.
\newline \gls{xs:lang} does not appear in the schema diagram.
&
0..1 \\
\hline

\end{longtabu}