
\tabulinesep = 5pt
\begin{longtabu} to \textwidth {
    |l|X[3l]|X[0.75l]|}
\caption{Attributes for Event} \label{table:attributes-for-event} \\

\hline
Attribute & Description & Occurrence \\
\hline
\endfirsthead

\hline
\multicolumn{3}{|c|}{Continuation of Table \ref{table:attributes-for-event}}\\
\hline
Attribute & Description & Occurrence \\
\hline
\endhead
 
\gls{sequence} 
&
A number representing the sequential position of an occurrence of the
\gls{event} in the data buffer of an \gls{agent}.
\newline \gls{sequence} is a required attribute.
\newline \gls{sequence} \MUST have a value represented as an unsigned 64-bit
value from 1 to $2^{64}-1$.
&
1 \\
\hline

\gls{subtype} 
&
The \gls{subtype} of the \gls{data entity}.
\newline \gls{subtype} is an optional attribute.
\newline \gls{subtype} \MUST match the \gls{subtype} attribute of the \gls{dataitem} element as defined in the \gls{mtconnectdevices} document that the
\gls{event} element represents. 
&
0..1 \\
\hline

\gls{timestamp} 
&
The most accurate time available to a piece of equipment that represents
the point in time that the data reported for the \gls{event} was measured.
\newline \gls{timestamp} is a required attribute.
&
1 \\
\hline

\gls{name} 
&
The name of the \gls{event} element.
\newline \gls{name}  is an optional attribute.
\newline \gls{name}  \MUST match the \gls{name}  attribute of the \gls{dataitem} element defined in the \gls{mtconnectdevices} document that the \gls{event}
element represents.
\newline An \gls{nmtoken} XML type. 
&
0..1 \\
\hline

\gls{dataitemid} 
&
The unique identifier for the\gls{event} element.
\newline \gls{dataitemid} is a required attribute.
\newline \gls{dataitemid} \MUST match the id attribute of the \gls{dataitem}
element defined in the \gls{mtconnectdevices} document that the
\gls{event} element represents. 
&
1 \\
\hline

\gls{resettriggered}
&
For those \gls{dataitem} elements that report data that may be periodically
reset to an initial value, \gls{resettriggered} identifies when a reported
value has been reset and what has caused that reset to occur.
\newline \gls{resettriggered} is an optional attribute.
\newline \gls{resettriggered} \MUST only be provided for the specific
occurrence of a \gls{data entity} reported in the \gls{mtconnectstreams}
document when the reset occurred and \MUSTNOT be provided for any
other occurrence of the \gls{data entity} reported in a
\gls{mtconnectstreams} document.
&
0..1 \\
\hline

\gls{compositionid}
&
The identifier of the \gls{composition} element defined in the
\gls{mtconnectdevices} document associated with the data reported for
the \gls{event} element.
\newline \gls{compositionid} is an optional attribute.
&
0..1 \\
\hline

\end{longtabu}